### 2024-07-27 template.tex
first commit!  includes theoretical work from Summer 2024

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{siunitx}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Analytic Askaryan Signals}

\author{Jordan C. Hanson}
\email{jhanson2@whittier.edu}
\affiliation{Department of Physics and Astronomy, Whittier College}
\author{Raymond Hartig}
\affiliation{Department of Physics and Astronomy, Whittier College}
\date{\today}

\begin{abstract}
This is a work in progress.
\end{abstract}

\keywords{Ultra-high energy neutrino; Askaryan radiation; Mathematical physics}

\maketitle

\section{Introduction}

The introduction.

\section{Units, Definitions, and Conventions}
\label{sec:unit}

The units.

\section{Collection of Main Results}
\label{sec:onc}

Here is a list of the basic results and ideas for this paper.

\begin{itemize}
\item Let the signal model $s(t)$ be
\begin{equation}
s(t) = -E_0 t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} \label{eq:s}
\end{equation}
This is the off-cone field equation from \cite{PhysRevD.105.123019}.  The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: the longitudinal length of the UHE-$\nu$-induced cascade, and the angle at which the cascade is observed relative to the Cherenkov angle.  The parameter $E_0$ is the amplitude normalization, and it depends on two parameters: $\sigma_{\rm t}$, and $\omega_{\rm 0}$, the cutoff frequency from the cascade form factor.
\item Let $\widehat{s}(t)$ represent the Hilbert transform of $s(t)$.  The \textit{analytic signal} of $s(t)$ is
\begin{equation}
s_{\rm a}(t) = s(t) + j \widehat{s}(t)
\end{equation}
The magnitude of the analytic signal, $|s_a(t)|$, is the \textit{envelope} of the signal.  The Hilbert transform $\widehat{s}(t)$ is equivalent to the convolution of $s(t)$ and the tempered distribution $h(t) = 1/(\pi t)$.
\item Let $S(f)$ be the Fourier transform of $s(t)$.  The Fourier transform of the analytic signal is
\begin{equation}
\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
\end{equation}
The sign function, $\sgn$ gives $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$.
\item Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
\begin{equation}
s_{\rm a}(t) = 2\int_{0}^{\infty} S(f) e^{2\pi j f t} df \label{eq:sa_2}
\end{equation}
\item The Fourier transform of Eq. \ref{eq:s} is
\begin{equation}
S(f) = E_0 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}
\end{equation}
\item Using the gaussian spectral width $\sigma_{\rm f}$ from \cite{10.1016/j.astropartphys.2017.03.008}, and the guassian width of $s(t)$ from \cite{PhysRevD.105.123019}, it was shown in \cite{PhysRevD.105.123019} that the uncertainty principle holds for off-cone signals:
\begin{equation}
\sigma_{\rm t} \sigma_{\rm f} \geq \frac{1}{2\pi}
\end{equation}
The equality is reached in the limit the far-field parameter limits to zero: $\eta \to 0$.  This makes the signal spectrum
\begin{equation}
S(f) = E_0 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}
\end{equation}
Inserting $S(f)$ into Eq. \ref{eq:sa_1}, $s_{\rm a}(t)$ is
\begin{equation}
s_{\rm a}(t) = \frac{E_0 \sigma_t^2 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}
\end{equation}
\item Let the integral in Eq. \ref{eq:sa_3} be $I$, $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  The real and imaginary parts of $I$ are
\begin{align}
\Re\lbrace I \rbrace &= \frac{\sigma_f}{\sqrt{2}} \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
\Im\lbrace I \rbrace &= \frac{\sigma_f}{\sqrt{2}} \int_0^{\infty} e^{-k^2/4}\sin(kx) dk \\
\end{align}
The real part of $I$ is even, so it can be extended to $(-\infty,\infty)$ if it is multiplied by $1/2$.  The result is
\begin{equation}
\Re\lbrace I \rbrace = \sqrt{\frac{\pi}{2}} \sigma_f e^{-\frac{1}{2}\left(t/\sigma_t\right)^2}
\end{equation}
The imaginary part of $I$ is proportional to $D(x)$, known as \textit{Dawson's integral:}
\begin{equation}
\Im{I} = \sqrt{2}\sigma_f D(x)
\end{equation}
\item The overal analytic signal, $s_a(t)$, is
\begin{equation}
s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}
\end{equation}
The signal envelope is $|s_a(t)|$:
\begin{equation}
\mathcal{E}_s(t) = E_0 \left(t^2 e^{-\left(t/\sigma_t\right)^2} + \frac{\sigma_t^2}{2\pi} \left(\frac{dD(x)}{dx}\right)^2\right)
\end{equation}
It is important to note that, though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.  Note that $s_a(0) \neq 0$, since $D(x) = 1 - 2x D(x)$.
\item Signal data in detectors designed to observe Askaryan pulses is equivalent to the convolution of the signal and detector response functions.  Signal models are convolved with measured detector responses to create \textit{signal templates}.  Signal templates are cross-correlated with observed data to identify UHE-$\nu$ signals.  The oscillations of signal templates and observed data can introduce various uncertainties when cross-correlated.  This problem intensifies when the signal-to-noise ratio between Askaryan pulse data and thermal noise decreases.  To reduce these uncertainties, the Hilbert envelope of observed signals is used in cross-correlations instead of the original signals.  We seek an analytic equation for the Hilbert envelope of the data.  That is, we seek the envelope of the convolution of the analytic signal model with a typical detector response.  The RLC damped oscillator is a standard circuit model for the RF dipole antennas used in RNO-G and the proposed IceCube Gen2 \cite{10.1103/PhysRevD.85.062004,10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
\item There are two paths to calculating the final result.  The first option involves three steps.  First, the detector response, $r(t)$ is convolved with $s(t)$.  Second, the analytic signal of the result is found.  Third, the magnitude of the analytic signal is computed, which can be compared to envelopes of observed signals.  The second option involves computing the envelope of the convolution of $r(t)$ with $s(t)$ directly from $s_a(t)$ and $r_a(t)$.
\item Let $x(t) * y(t)$ represent the convolution of two functions $x(t)$ and $y(t)$.  Let the envelope of the convolution be $\mathcal{E}_{x * y}(t)$.  $\mathcal{E}_{x * y}(t)$, $r_a(t)$, and $s_a(t)$ are related by
\begin{equation}
\mathcal{E}_{x * y}(t) = \frac{1}{2}| x_a (t) * y_a(t)| \label{eq:awesome}
\end{equation}
The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are
\begin{align}
r(t) &= R_0 e^{-\gamma t} \cos(2\pi j f_0 t) \\
r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t}
\end{align}
The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.
\item The analytic signal and response convolution inside the magnitude on the right hand side of Eq. \ref{eq:awesome} can be broken into real and imaginary parts of $s_a(t)$:
\begin{align}
r_a (t) * s_a(t) = & \\ 
& r_a(t) * \Re\lbrace s_a(t)\rbrace + \\ 
& j r_a(t) * \Im\lbrace s_a(t)\rbrace
\end{align}
Let $\gamma' = \sqrt{2}\sigma_t \gamma$, $f_0' = \sqrt{2} \sigma_t f_0$, and $z_0 = \gamma' - 2\pi j f_0'$.  The result for $r_a(t) * \Re\lbrace s_a(t)\rbrace$ is
\begin{align}
r_a(t) * \Re\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \\
Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2)
\end{align}
Note that there is an extra factor of $\sqrt{2}\sigma_t$ to account for the measure $dt$ in the convolution upon changing the convolution integral from $dt$ to $dx$.
\item The result for $r_a(t) * \Im\lbrace s_a(t)\rbrace$ is
\begin{equation}
r_a(t) * \Im\lbrace s_a(t)\rbrace = \frac{j}{2}\sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} x e^{-x^2} Q(z_0)
\end{equation}
Note that the complementary error function is an \textit{entire function}, so $dQ/dz_0$ is defined for all $z_0$.
\item The convolution $r_a (t) * s_a(t)$ is therefore
\begin{multline}
r_a (t) * s_a(t) = \sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} \\ \left(e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} - \frac{1}{2} x e^{-x^2} Q(z_0) \right)
\end{multline}
\item The envelope of the convolution of $s(t)$ and $r(t)$ is therefore
\begin{multline}
\mathcal{E}_{r * s}(t) = \sqrt{\frac{\pi}{4}} E_0 R_0 \sigma_t^2 \\ \left|e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} - \frac{1}{2} x e^{-x^2} Q(z_0) \right|
\end{multline}
This result can be further simplified.
\end{itemize}

\section{Conclusion}
\label{sec:conc}

The conclusion.

\appendix

\section{Details}
\label{app:a}

The details.

\bibliography{apssamp}

\end{document}

### 2024-07-30 template.tex
updates: fixed some typos and correcting some units factors, factors of 2
calculated new results given that there was a missing factor of 2 near the Dawson Function

@@
 \begin{equation}
-S(f) = E_0 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}
+S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}
 \end{equation}
@@
 \begin{equation}
-S(f) = E_0 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}
+S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}
 \end{equation}
-Inserting $S(f)$ into Eq. \ref{eq:sa_1}, $s_{\rm a}(t)$ is
+Inserting $S(f)$ into Eq. \ref{eq:sa_2}, $s_{\rm a}(t)$ is
 \begin{equation}
-s_{\rm a}(t) = \frac{E_0 \sigma_t^2 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}
+s_{\rm a}(t) = \frac{E_0 \sigma_t^3 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}
 \end{equation}
-\item Let the integral in Eq. \ref{eq:sa_3} be $I$, $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  The real and imaginary parts of $I$ are
+\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
 \begin{align}
-\Re\lbrace I \rbrace &= \frac{\sigma_f}{\sqrt{2}} \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
-\Im\lbrace I \rbrace &= \frac{\sigma_f}{\sqrt{2}} \int_0^{\infty} e^{-k^2/4}\sin(kx) dk \\
+s_{\rm a}(t) &= \frac{E_0 \sigma_{\rm t}}{\sqrt{2\pi}}\frac{dI}{dx} \\
+\Re\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
+\Im\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\sin(kx) dk
 \end{align}
@@
 \begin{equation}
-\Re\lbrace I \rbrace = \sqrt{\frac{\pi}{2}} \sigma_f e^{-\frac{1}{2}\left(t/\sigma_t\right)^2}
+\Re\lbrace I \rbrace = \sqrt{\pi} e^{-x^2}
 \end{equation}
-The imaginary part of $I$ is proportional to $D(x)$, known as \textit{Dawson's integral:}
+The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$:}
 \begin{equation}
-\Im{I} = \sqrt{2}\sigma_f D(x)
+\Im\lbrace I\rbrace = 2 D(x)
 \end{equation}
@@
 \begin{equation}
-s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}
+s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{2 j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}
 \end{equation}
-The signal envelope is $|s_a(t)|$:
-\begin{equation}
-\mathcal{E}_s(t) = E_0 \left(t^2 e^{-\left(t/\sigma_t\right)^2} + \frac{\sigma_t^2}{2\pi} \left(\frac{dD(x)}{dx}\right)^2\right)
-\end{equation}
+The signal envelope is $|s_a(t)|$.
 It is important to note that, though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.
-Note that $s_a(0) \neq 0$, since $D(x) = 1 - 2x D(x)$.
+Note that $s_a(0) \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.
 \item Signal data in detectors designed to observe Askaryan pulses is equivalent to the convolution of the signal and detector response functions.
@@
 \begin{align}
-r_a(t) * \Re\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \\
-Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2)
+r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 R_0 \sigma_t^2 e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \label{eq:result1} \\
+Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2) \label{eq:result2}
 \end{align}
-Note that there is an extra factor of $\sqrt{2}\sigma_t$ to account for the measure $dt$ in the convolution upon changing the convolution integral from $dt$ to $dx$.
 \item The result for $r_a(t) * \Im\lbrace s_a(t)\rbrace$ is
 \begin{equation}
-r_a(t) * \Im\lbrace s_a(t)\rbrace = \frac{j}{2}\sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} x e^{-x^2} Q(z_0)
+r_a(t) * \Im\lbrace s_a(t)\rbrace = -\sqrt{\frac{\pi}{2}} R_0 E_0 \sigma_t t e^{-\frac{1}{2}(t/\sigma_t)^2} Q(z_0) \label{eq:result3}
 \end{equation}
-Note that the complementary error function is an \textit{entire function}, so $dQ/dz_0$ is defined for all $z_0$.
+Note that the complementary error function and Gaussian functions are \textit{entire functions}, so $dQ/dz_0$ is defined for all $z_0$.
+\item The results in Eqs. \ref{eq:result1}-\ref{eq:result3} may be expressed in terms of $s(t)$ and $r_{\rm a}(t)$:
+\begin{align}
+r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\
+r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)
+\end{align}
 \item The convolution $r_a (t) * s_a(t)$ is therefore
 \begin{multline}
-r_a (t) * s_a(t) = \sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} \\ \left(e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} - \frac{1}{2} x e^{-x^2} Q(z_0) \right)
+r_a (t) * s_a(t) = -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\ + j\sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)
 \end{multline}
 \item The envelope of the convolution of $s(t)$ and $r(t)$ is therefore
-\begin{multline}
-\mathcal{E}_{r * s}(t) = \sqrt{\frac{\pi}{4}} E_0 R_0 \sigma_t^2 \\ \left|e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} - \frac{1}{2} x e^{-x^2} Q(z_0) \right|
-\end{multline}
+\begin{equation}
+\mathcal{E}_{r * s}(t) = \frac{1}{2}|r_{\rm a}(t) * s_{\rm a}(t)|
+\end{equation}
 This result can be further simplified.

### 2025-01-03 template.tex
fixed a key typo
another small typo
fixed a typo in template
big new commit, with new progress on simplifying the final envelope

@@
 \usepackage{mathtools}
-\usepackage{makecell}
+\usepackage{empheq}
 \usepackage{siunitx}
@@
 
-\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Analytic Askaryan Signals}
+\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals}
 
@@
 \end{equation}
-\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
+\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f\right)^2$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
 \begin{align}
@@
 \end{equation}
-\item The overal analytic signal, $s_a(t)$, is
+\item The overall analytic signal, $s_a(t)$, is
 \begin{equation}
@@
 Let the envelope of the convolution be $\mathcal{E}_{x * y}(t)$.
-$\mathcal{E}_{x * y}(t)$, $r_a(t)$, and $s_a(t)$ are related by
+$\mathcal{E}_{x * y}(t)$, $x_a(t)$, and $y_a(t)$ are related by
 \begin{equation}
@@
 \begin{align}
-r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\
-r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)
+r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \label{eq:Re} \\
+r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0) \label{eq:Im}
 \end{align}
@@
 This result can be further simplified.
+There are several intermediate steps that aid in the simplification.
+First, note that $Q(z_0)$ is related to the \textit{Voigt functions} $U(x,t)$ and $V(x,t)$:
+\begin{align}
+U(x,t) &= j V(x,t) = \frac{\pi}{4 t} e^{z^2} \erfc(z) \\
+z &= \frac{1-jx}{2\sqrt{t}} \label{eq:z_def}
+\end{align}
+Note that $t$ and $x$ are real parameters, and that the Voigt functions are also real.  Let $z = \frac{1}{2}z_0$. The parameters are connected to $z_0$ by the following:
+\begin{align}
+\Re \lbrace z_0 \rbrace &= \frac{1}{\sqrt{t}} \\
+\gamma ' &= \frac{1}{\sqrt{t}} \\
+\Im \lbrace z_0 \rbrace &= -\frac{x}{\sqrt{t}} \\
+x &= \frac{2\pi f_0'}{\gamma'} = \frac{2\pi f_0}{\gamma} \label{eq:x}
+\end{align}
+It is significant that $x$ is the ratio of the detector parameters.  Thus, $Q(z_0)$ may be written in terms of $U$ and $V$:
+\begin{equation}
+Q(z_0) = \frac{2}{\gamma'\sqrt{\pi}}\left(U + j V\right)
+\end{equation}
+Equation \ref{eq:Im} simplifies:
+\begin{equation}
+\boxed{r_a(t) * \Im\lbrace s_a(t)\rbrace = \frac{R_0 s(t)}{\gamma} \left(U + j V \right)} \label{eq:int_1}
+\end{equation}
+To simplify Eq. \ref{eq:Re}, we need the derivative of $Q(z_0)$ with respect to $z_0$:
+\begin{equation}
+\frac{dQ}{dz_0} = \frac{1}{2}z_0 Q(z_0) - \frac{1}{\sqrt{\pi}} \label{eq:derivative}
+\end{equation}
+Combining Eqs. \ref{eq:Re}, \ref{eq:z_def}, and \ref{eq:derivative}, we find
+\begin{equation}
+r_a(t) * \Re\lbrace s_a(t)\rbrace = E_0 \sigma_t^2 r_a \left(1 - \frac{z_0}{\gamma'}\left(U + j V \right)\right)
+\end{equation}
+Using the definitions of $z_0$, $\gamma'$, and Eq. \ref{eq:x}, we find
+\begin{equation}
+\boxed{r_a(t) * \Re\lbrace s_a(t)\rbrace = E_0 \sigma_t^2 r_a \left(1 - \left(1 + j x \right)\left(U + j V \right)\right)} \label{eq:int_2}
+\end{equation}
+There are useful limits for Voigt functions:
+\begin{align}
+\lim_{t\to 0} U(x,t) &= \frac{1}{1+x^2} \\
+\lim_{t\to 0} V(x,t) &= \frac{x}{1+x^2}
+\end{align}
+Taking this limit for Eqs. \ref{eq:int_1} and \ref{eq:int_2}, we find, to first-order in $1/\gamma'$, 
+\begin{align}
+r_a(t) * \Im\lbrace s_a(t)\rbrace &\approx \frac{R_0s(t)}{\gamma} \\
+r_a(t) * \Re\lbrace s_a(t)\rbrace &\approx 0
+\end{align}
+\item 
+Using Eq. \ref{eq:awesome}, we find
+\begin{equation}
+\boxed{\mathcal{E}_{r * s}(t) = \frac{R_0|s(t)|}{2\gamma}}
+\end{equation}
+This result appears to have (1) the right units, (2) the right limits, and (3) the right symmetry.
+However, the \textit{width} of this theoretical envelope is limited by the width of $s(t)$.
+The limit that the Voigt parameter $t \to 0$ implies that $\gamma' \gg 1$.
+This is not necessarily a good limit for realistic detectors.
 \end{itemize}

### 2025-01-10 template.tex
updated analytic signal of detector response proof

@@
 \end{equation}
-The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are
+We should include the proof here (I have to track it down in my notebooks).
+\item The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are
 \begin{align}
 r(t) &= R_0 e^{-\gamma t} \cos(2\pi j f_0 t) \\
-r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t}
+r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t} \label{eq:ra}
 \end{align}
@@
 Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.
+The proof of Eq.
+\ref{eq:ra} is as follows:
+\begin{align}
+r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
+R(f) &= \frac{R_0}{2\pi j} \left( \frac{f - \frac{j\gamma}{2\pi}}{(f-z_+)(f-z_-)} \right) \\
+z_+ &= f_0 + \frac{j\gamma}{2\pi} \\
+z_- &= -f_0 + \frac{j\gamma}{2\pi} \\
+\widehat{r}(t) &= \mathcal{F}^{-1}\left \lbrace - j \sgn(f) R(f) \right \rbrace \label{eq:rh} \\ 
+\widehat{r}(t) &= \frac{R_0}{2j}\left( e^{2\pi j f_0 t} - e^{-2\pi j f_0 t} \right) e^{-\gamma t} \\
+\widehat{r}(t) &= R_0 \sin(2\pi f_0 t) e^{-\gamma t} \\
+r_a (t) &= R_0 \left(\cos(2\pi f_0 t) + j\sin(2\pi f_0 t)\right) e^{-\gamma t} \\
+r_a (t) &= R_0 e^{2\pi j f_0 t} e^{-\gamma t}
+\end{align}
+In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.
 \item The analytic signal and response convolution inside the magnitude on the right hand side of Eq. \ref{eq:awesome} can be broken into real and imaginary parts of $s_a(t)$:
@@
 \begin{align}
-U(x,t) &= j V(x,t) = \frac{\pi}{4 t} e^{z^2} \erfc(z) \\
+U(x,t) + j V(x,t) &= \sqrt{\frac{\pi}{4 t}} e^{z^2} \erfc(z) \\
 z &= \frac{1-jx}{2\sqrt{t}} \label{eq:z_def}

### 2025-01-11 template.tex
update all the way to integral 3, trying to conclude the problem

--- 2024-07-30 template.tex
@@
 \usepackage{mathtools}
-\usepackage{makecell}
+\usepackage{empheq}
 \usepackage{siunitx}
 \DeclareMathOperator\erfc{erfc}
+\DeclareMathOperator\erf{erf}
 \DeclareMathOperator{\sgn}{sgn}
@@
 \begin{equation}
-S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}
+S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} \label{eq:spec}
 \end{equation}
@@
 Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.
-\item The analytic signal and response convolution inside the magnitude on the right hand side of Eq. \ref{eq:awesome} can be broken into real and imaginary parts of $s_a(t)$:
+The proof of Eq.
+\ref{eq:ra} is as follows:
 \begin{align}
-r_a (t) * s_a(t) = & \\ 
-& r_a(t) * \Re\lbrace s_a(t)\rbrace + \\ 
-& j r_a(t) * \Im\lbrace s_a(t)\rbrace
+r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
+R(f) &= \frac{R_0}{2\pi j} \left( \frac{f - \frac{j\gamma}{2\pi}}{(f-z_+)(f-z_-)} \right) \\
+z_+ &= f_0 + \frac{j\gamma}{2\pi} \\
+z_- &= -f_0 + \frac{j\gamma}{2\pi} \\
+\widehat{r}(t) &= \mathcal{F}^{-1}\left \lbrace - j \sgn(f) R(f) \right \rbrace \label{eq:rh} \\ 
+\widehat{r}(t) &= \frac{R_0}{2j}\left( e^{2\pi j f_0 t} - e^{-2\pi j f_0 t} \right) e^{-\gamma t} \\
+\widehat{r}(t) &= R_0 \sin(2\pi f_0 t) e^{-\gamma t} \\
+r_a (t) &= R_0 \left(\cos(2\pi f_0 t) + j\sin(2\pi f_0 t)\right) e^{-\gamma t} \\
+r_a (t) &= R_0 e^{2\pi j f_0 t} e^{-\gamma t}
 \end{align}
-Let $\gamma' = \sqrt{2}\sigma_t \gamma$, $f_0' = \sqrt{2} \sigma_t f_0$, and $z_0 = \gamma' - 2\pi j f_0'$.  The result for $r_a(t) * \Re\lbrace s_a(t)\rbrace$ is
+In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.
+\item Equation \ref{eq:awesome} will now be applied, using the definition of $r_a(t)$ and the Fourier transform of $s(t)$, $S(f)$.
+The Fourier transform of $r_a(t) * s_a(t)$ is $R_a(f) S_a(f)$.
+Using the definition of the analytic signal, we have
+\begin{equation}
+R_a(f) S_a(f) = R_a(f)(1 + \sgn(f)) S(f) \label{eq:midway}
+\end{equation}
+The Fourier transform of $r_a(t)$ is
 \begin{align}
-r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 R_0 \sigma_t^2 e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \label{eq:result1} \\
-Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2) \label{eq:result2}
+R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z} \\
+z &= f_0 + \frac{j\gamma}{2\pi}
 \end{align}
-\item The result for $r_a(t) * \Im\lbrace s_a(t)\rbrace$ is
+The Fourier transform $S(f)$ is given by Eq.
+\ref{eq:spec}.
+Inserting the spectra into Eq.
+\ref{eq:midway} and taking the inverse Fourier transform should give $r_a(t) * s_a(t)$.
+Note the inverse transform integral is only over positive frequencies, due to the $1+\sgn(f)$ factor.
+Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.
+The result is
+\begin{multline}
+r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j ft} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df
+\end{multline}
+Completing the square in the exponent, and letting $x = t/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
+\begin{align}
+r_a(t) * s_a(t) &= -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{dI_1}{dt} \\
+I_1 &= e^{-x^2} \int_0^\infty \frac{e^{-(y-j x)^2}}{y-z} dy
+\end{align}
+The time derivative can be switched to a derivative with respect to $x$:
 \begin{equation}
-r_a(t) * \Im\lbrace s_a(t)\rbrace = -\sqrt{\frac{\pi}{2}} R_0 E_0 \sigma_t t e^{-\frac{1}{2}(t/\sigma_t)^2} Q(z_0) \label{eq:result3}
+\boxed{
+r_a(t) * s_a(t) = -j \frac{R_0 E_0 \sigma_t^2}{\sqrt{\pi}} \frac{dI_1}{dx}}
 \end{equation}
-Note that the complementary error function and Gaussian functions are \textit{entire functions}, so $dQ/dz_0$ is defined for all $z_0$.
-\item The results in Eqs. \ref{eq:result1}-\ref{eq:result3} may be expressed in terms of $s(t)$ and $r_{\rm a}(t)$:
+Evaluating the derivative $dI_1/dx$ gives
+\begin{equation}
+\frac{dI_1}{dx} = 2j e^{-x^2} \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z}dy + 2 x I_1 - 2 x I_1
+\end{equation}
+The final two terms cancel, and the result is
 \begin{align}
-r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\
-r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)
+\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I_2(x,z)} \\
+\Aboxed{I_2(x,z) &= \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z} dy}
 \end{align}
-\item The convolution $r_a (t) * s_a(t)$ is therefore
-\begin{multline}
-r_a (t) * s_a(t) = -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\ + j\sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)
-\end{multline}
-\item The envelope of the convolution of $s(t)$ and $r(t)$ is therefore
+\item Note that $I_2(x,0)$ has an exact solution:
+\begin{align}
+I_2(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
+I_2(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
+\end{align}
+However, approximating $I_2(x,z) \approx I_2(x,0)$ drops the dependance on $\gamma$ and $f_0$.  This suggests expanding $I_2(x,z)$ in a Taylor series about $z=0$:
+\begin{align}
+I_2(x,z) &\approx I_2(x,0) + \sum_{n=1}^{\infty} z^n I_3(x,n) \\
+I_3(x,n) &= \int_0^{\infty} y^{-n} e^{-(y-jx)^2} dy \\
+I_3(x,n) &= \int_0^{\infty} y^{-n} e^{(x+jy)^2} dy
+\end{align}
+For example, when the lower limit is restricted from 0 to just $z$, the term $I(0,1)$ is
 \begin{equation}
-\mathcal{E}_{r * s}(t) = \frac{1}{2}|r_{\rm a}(t) * s_{\rm a}(t)|
+I(0,1) = \int_z^{\infty} y^{-1} e^{-y^2} dy = \frac{1}{2}E_1(z)
 \end{equation}
-This result can be further simplified.
 \end{itemize}

### 2025-01-13 template.tex
oof ... trying to solve the final integral

@@
 \begin{equation}
-\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
+mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
 \end{equation}
@@
 \begin{align}
-R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z} \\
-z &= f_0 + \frac{j\gamma}{2\pi}
+R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z_0} \\
+z_0 &= f_0 + \frac{j\gamma}{2\pi}
 \end{align}
@@
 Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.
+Note also that it is prudent to consider the signal $s(t)$ shifted by a $t_0$, to ensure the entire signal is convolved with $r(t)$.
+For time-shifts, the Fourier transform responds like:
+\begin{equation}
+\mathcal{F}\left\lbrace s(t-t_0)\right\rbrace = e^{-2\pi f t_0} S(f)
+\end{equation}
 The result is
 \begin{multline}
-r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j ft} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df
+r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j f(t-t_0)} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df
 \end{multline}
-Completing the square in the exponent, and letting $x = t/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
+Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
+\begin{multline}
+r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right)
+\end{multline}
+Evaluating the derivative gives
 \begin{align}
-r_a(t) * s_a(t) &= -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{dI_1}{dt} \\
-I_1 &= e^{-x^2} \int_0^\infty \frac{e^{-(y-j x)^2}}{y-z} dy
+\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \\
+\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy}
 \end{align}
-The time derivative can be switched to a derivative with respect to $x$:
+\item Note that $I(x,0)$ has exact solutions:
+\begin{align}
+I(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
+I(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
+\end{align}
+However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
+Voigt or Faddeeva functions can be introduced, if only the denominator was even in $y$.
+This suggests rationalizing the denominator:
 \begin{equation}
-\boxed{
-r_a(t) * s_a(t) = -j \frac{R_0 E_0 \sigma_t^2}{\sqrt{\pi}} \frac{dI_1}{dx}}
-\end{equation}
-Evaluating the derivative $dI_1/dx$ gives
-\begin{equation}
-\frac{dI_1}{dx} = 2j e^{-x^2} \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z}dy + 2 x I_1 - 2 x I_1
-\end{equation}
-The final two terms cancel, and the result is
-\begin{align}
-\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I_2(x,z)} \\
-\Aboxed{I_2(x,z) &= \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z} dy}
-\end{align}
-\item Note that $I_2(x,0)$ has an exact solution:
-\begin{align}
-I_2(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
-I_2(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
-\end{align}
-However, approximating $I_2(x,z) \approx I_2(x,0)$ drops the dependance on $\gamma$ and $f_0$.  This suggests expanding $I_2(x,z)$ in a Taylor series about $z=0$:
-\begin{align}
-I_2(x,z) &\approx I_2(x,0) + \sum_{n=1}^{\infty} z^n I_3(x,n) \\
-I_3(x,n) &= \int_0^{\infty} y^{-n} e^{-(y-jx)^2} dy \\
-I_3(x,n) &= \int_0^{\infty} y^{-n} e^{(x+jy)^2} dy
-\end{align}
-For example, when the lower limit is restricted from 0 to just $z$, the term $I(0,1)$ is
-\begin{equation}
-I(0,1) = \int_z^{\infty} y^{-1} e^{-y^2} dy = \frac{1}{2}E_1(z)
+\frac{1}{y-z_0} = \frac{\frac{f-f_0}{\sqrt{2}\sigma_f} - \frac{j\gamma}{2\pi\sqrt{2}\sigma_f}}{\frac{(f-f_0)^2}{2\sigma_f^2} + \frac{\gamma^2}{4\pi^2 2\sigma_f^2}}
 \end{equation}

### 2025-01-29 template.tex
updated the pdf

@@
 \end{multline}
-Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
+Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z_0 \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
 \begin{multline}
@@
 \begin{align}
-\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \\
-\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy}
+\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \label{eq:end1} \\
+\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy} \label{eq:end2}
 \end{align}
@@
 However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
-Voigt or Faddeeva functions can be introduced, if only the denominator was even in $y$.
-This suggests rationalizing the denominator:
-\begin{equation}
-\frac{1}{y-z_0} = \frac{\frac{f-f_0}{\sqrt{2}\sigma_f} - \frac{j\gamma}{2\pi\sqrt{2}\sigma_f}}{\frac{(f-f_0)^2}{2\sigma_f^2} + \frac{\gamma^2}{4\pi^2 2\sigma_f^2}}
-\end{equation}
+\item To solve Eq.
+\ref{eq:end2}, the integral function is expanded in powers of $z_0$.
+This is wise, given that the UHE-$\nu$ signal bandwidth will usually exceed that of a dipole receiver with response $r(t)$ and analytic signal $r_a(t)$.
 \end{itemize}

### 2025-02-01 template.tex
big update, with potential final result

@@
 \usepackage{empheq}
-\usepackage{siunitx}
 \DeclareMathOperator\erfc{erfc}
@@
 \begin{align}
-r(t) &= R_0 e^{-\gamma t} \cos(2\pi j f_0 t) \\
+r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
 r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t} \label{eq:ra}
@@
 \end{align}
-\item Note that $I(x,0)$ has exact solutions:
+\item The solution for $I(x,z_0)$ in Eq. \ref{eq:end2} may be found using contour integration, and comparison with standard results from integral tables.  First, $z$ is substituted for $(x+jy)$:
 \begin{align}
-I(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
-I(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
+z &= x+jy \\
+dz &= j dy \\
+y &= j(x-z)
 \end{align}
-However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
-\item To solve Eq.
-\ref{eq:end2}, the integral function is expanded in powers of $z_0$.
-This is wise, given that the UHE-$\nu$ signal bandwidth will usually exceed that of a dipole receiver with response $r(t)$ and analytic signal $r_a(t)$.
+Let $z_1 = x+jz_0$. The substitution changes $I(x,z_0)$ into
+\begin{equation}
+I(x,z_0) = -j \int_{x}^{x+jR} \frac{(z-x)}{(z-z_1)} e^{z^2} dz
+\end{equation}
+First, assume that $x>0$ and $x>\Im \lbrace z_0\rbrace$ so that the pole is in the first quadrant.
+Define four line integrals to enclose the pole, $I_1$ through $I_4$.
+First, $I_1$ extends from $x$ to $x+jR$, and is equal to $I$:
+\begin{align}
+I_1 &= -j \int_{x}^{x+jR} \frac{(x+jy-x)}{(x+jy-(x+jz_0))} e^{(x+jy)^2} j dy \\
+I_1 &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy = I(x,z_0)
+\end{align}
+Regarding the limits, $z = x$ corresponds to $y=0$, and $z = x+jR$ corresponds to $y=R$, where $R \to \infty$.
+The line integral $I_2$ runs from $x+jR$ to $jR$.
+The numerator goes as $\exp(z^2) \propto \exp(-R^2)$.
+For $R \to \infty$, $I_2$ vanishes.
+The line integral $I_3$ returns from $jR$ to $0$.
+The integrand is parametrized by $z = jy$, $dz = jdy$.
+Along $I_3$, $x = 0$.
+The result is
+\begin{equation}
+I_3 = -\int_0^{R} \frac{ye^{-y^2}dy}{y-z_0}
+\end{equation}
+The line integral $I_4$ finishes the loop, with limits $0$ and $x$.
+However, the numerator of the integrand is proportional to $(z-x)$.
+Since the parameterization is $z=x$, the integrand vanishes.
+Thus, only $I_1$ ane $I_3$ remain in the sum of line integrals, which enclose the pole at $z_1$.
+The contour integral is therefore:
+\begin{equation}
+\oint \frac{-j(z-x)e^{z^2}dz}{(z-z_1)} = I(x,z_0) + I_3
+\end{equation}
+According to the Cauchy integral formula, the left-hand side is $2\pi j$ times the residue at $z_1$:
+\begin{equation}
+\oint \frac{-j(z-x)e^{z^2}dz}{(z-z_1)} = 2\pi j z_0 e^{(x+jz_0)^2}
+\end{equation}
+Solving for $I(x,z_0)$:
+\begin{equation}
+I(x,z_0) = 2\pi j z_0 e^{(x+jz_0)^2} + \int_0^{\infty} \frac{ye^{-y^2}dy}{y-z_0}
+\end{equation}
+The term originating from $I_3$ may be found in standard integral tables.  The result is 
+\begin{equation}
+\boxed{
+I(x,z_0) = 2\pi j z_0 e^{(x+jz_0)^2} + \frac{\pi}{2}e^{z_0^2}\erfc(z_0)}
+\end{equation}
+The final result for $\mathcal{E}_{r * s}$ is
+\begin{equation}
+\mathcal{E}_{r * s} = \frac{1}{2}| r_a(t) * s_a(t)| = R_0 E_0 \sigma_t^2 e^{-x^2} \left|\frac{I(x,z_0)}{\sqrt{\pi}}\right|
+\end{equation}
 \end{itemize}

### 2025-02-09 template.tex
big update on simplification of final results

--- 2025-01-29 template.tex
@@
 \begin{equation}
-mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
+\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
 \end{equation}
@@
 \begin{multline}
-r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right)
+r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right) \label{eq:withI}
 \end{multline}
-Evaluating the derivative gives
+All that remains is to evaluate the integral
+\begin{equation}
+I(z,z_0) = \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy
+\end{equation}
+Let $z = x+jy$, $dy = -jdz$, and $z_1 = x+jz_0$.  The integral becomes, as $R \to \infty$,
+\begin{equation}
+I(x,z_0) = \int_{x}^{x+jR} \frac{e^{z^2}}{z - z_1} dz
+\end{equation}
+$I(x,z_0)$ can be evaluated via contour integration, with a rectangular contour that encloses the pole if $x > \Im\lbrace z_0\rbrace$.
+Let $I_1$ extend from $(x,0)$ to ($x,jR)$.
+Let $I_2$ extend from $(x,jR)$ to $(0,jR)$.
+Let $I_3$ extend from $(0,jR)$ to $(0,0)$.
+Finally, let $I_4$ extend from $(0,0)$ to $(x,0)$.
+Note that $I_1 = I(x,z_0)$.
+For the integral $I_2$, note that the exponential factor is proportional to $\exp(-R^2)$, while the denominator contains another factor of $R$.
+Since $dz = dx$, the integrand goes as $\exp(-R^2)/R$, vanishing as $R \to \infty$.
+For $I_3$, $x=0$.
+Thus, it reduces to
+\begin{equation}
+I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y-z_0} dy
+\end{equation}
+Let $y \to -y$, so that 
+\begin{equation}
+I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y+z_0} dy = -G(z_0)
+\end{equation}
+The function $G(z_0)$ is known as the Goodwin-Staton integral.
+$G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.
+It is commonly used in problems involving diffusion approximations, particularly in media with semi-infinite boundary conditions.
+The final segment of the contour is
+\begin{equation}
+I_4 = \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
+\end{equation}
+The sum of contour segments is $I_1 + I_2 + I_3 + I_4 = I_{\rm C}$, where $I_{\rm C}$ is given by the Cauchy integral formula: $2\pi j e^{z_1^2}$.  Solving for $I(x,z_0)$, we find
+\begin{equation}
+I(x,z_0) = 2\pi j e^{z_1^2} + G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
+\end{equation}
+If $x < \Im\lbrace z_0\rbrace$,
+\begin{equation}
+I(x,z_0) = G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
+\end{equation} \\
+Inserting this result into Eq. \ref{eq:withI},
+\begin{multline}
+r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(\frac{dA(x,z_0)}{dx}-\frac{j}{z_0}\frac{dD(x)}{dx} \right) \label{eq:ra_sa_1}
+\end{multline}
+with
 \begin{align}
-\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \label{eq:end1} \\
-\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy} \label{eq:end2}
+A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} + G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
+A(x,z_0) &= G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
 \end{align}
-\item Note that $I(x,0)$ has exact solutions:
-\begin{align}
-I(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
-I(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
-\end{align}
-However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
-\item To solve Eq.
-\ref{eq:end2}, the integral function is expanded in powers of $z_0$.
-This is wise, given that the UHE-$\nu$ signal bandwidth will usually exceed that of a dipole receiver with response $r(t)$ and analytic signal $r_a(t)$.
+and
+\begin{equation}
+D(x) = e^{-x^2} \int_{0}^{x} e^{x'^2} dx'
+\end{equation}
+What remains is to compute the magnitude of Eq.
+\ref{eq:ra_sa_1}.
+Let the overall scale factor in Eq.
+\ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, and let $x>\Im\lbrace z_0\rbrace$.
+Upon taking the magnitude, the quantity in parentheses generates four terms.
+The first is
+\begin{multline}
+\frac{dA^{*}}{dx}\frac{dA}{dx} = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2x_0^2-2y_0^2} \\ + 4G(z_0)x^2 e^{-2x^2} \\ + 16\pi G(z_0) x e^{-x^2}e^{-\gamma t} e^{-x_0^2+y_0^2} \\ \times \left(x_0\cos(2x_0(x-y_0)) - y_0\sin(2x_0(x-y_0)) \right)
+\end{multline}
+The second is
+\begin{equation}
+\frac{1}{z_0^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{z_0^2}\left(1-4xD(x)+4x^2D^2(x) \right)
+\end{equation}
+The combination of the third and forth terms is
+\begin{multline}
+\frac{dD}{dx}\left\lbrace \frac{j}{z_0^{*}} \frac{dA}{dx} - \frac{j}{z_0} \frac{dA^{*}}{dx}\right\rbrace = \\
+-\frac{2}{|z_0|^2} \frac{dD}{dx}\frac{d}{dx} ( -2\pi y_0 e^{-2xy_0} e^{y_0^2-x_0^2}\sin(2x_0(x-x_0)) \\
++ y_0G(z_0)e^{-x^2} \\
++ 2\pi x_0 e^{-2xy_0} e^{y_0^2-x_0^2}\cos(2x_0(x-x_0)) )
+\end{multline}
 \end{itemize}

### 2025-02-11 template.tex
update to the simplification of the final result

@@
 \begin{equation}
-I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y-z_0} dy
+I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y-z_0} dy = -G(-z_0) = G(z_0)
 \end{equation}
-Let $y \to -y$, so that 
-\begin{equation}
-I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y+z_0} dy = -G(z_0)
-\end{equation}
-The function $G(z_0)$ is known as the Goodwin-Staton integral.
+
+The function $G(z_0)$ is a function with odd-symmetry known as the Goodwin-Staton integral.
 $G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.
@@
 \begin{equation}
-I(x,z_0) = 2\pi j e^{z_1^2} + G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
+I(x,z_0) = 2\pi j e^{z_1^2} - G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
 \end{equation}
@@
 \begin{equation}
-I(x,z_0) = G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
+I(x,z_0) = -G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
 \end{equation} \\
@@
 \begin{align}
-A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} + G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
-A(x,z_0) &= G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
+A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} - G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
+A(x,z_0) &= -G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
 \end{align}
@@
 Let the overall scale factor in Eq.
-\ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, and let $x>\Im\lbrace z_0\rbrace$.
+\ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, and let $x>\Im\lbrace z_0\rbrace$.
 Upon taking the magnitude, the quantity in parentheses generates four terms.
@@
 \begin{multline}
-\frac{dA^{*}}{dx}\frac{dA}{dx} = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2x_0^2-2y_0^2} \\ + 4G(z_0)x^2 e^{-2x^2} \\ + 16\pi G(z_0) x e^{-x^2}e^{-\gamma t} e^{-x_0^2+y_0^2} \\ \times \left(x_0\cos(2x_0(x-y_0)) - y_0\sin(2x_0(x-y_0)) \right)
+\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4G^2(z_0)x^2 e^{-2x^2} \\ - 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right)
 \end{multline}
@@
 \begin{equation}
-\frac{1}{z_0^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{z_0^2}\left(1-4xD(x)+4x^2D^2(x) \right)
+\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right)
 \end{equation}
@@
 \begin{multline}
-\frac{dD}{dx}\left\lbrace \frac{j}{z_0^{*}} \frac{dA}{dx} - \frac{j}{z_0} \frac{dA^{*}}{dx}\right\rbrace = \\
--\frac{2}{|z_0|^2} \frac{dD}{dx}\frac{d}{dx} ( -2\pi y_0 e^{-2xy_0} e^{y_0^2-x_0^2}\sin(2x_0(x-x_0)) \\
-+ y_0G(z_0)e^{-x^2} \\
-+ 2\pi x_0 e^{-2xy_0} e^{y_0^2-x_0^2}\cos(2x_0(x-x_0)) )
+j\frac{dD}{dx}\left\lbrace \frac{1}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{1}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
 \end{multline}

### 2025-02-13 template.tex
reached a milestone, but does it all make sense?  the final expression is there, now we have to check it

@@
 \end{equation}
-The combination of the third and forth terms is
+The combination of the third and fourth terms is
 \begin{multline}
-j\frac{dD}{dx}\left\lbrace \frac{1}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{1}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
+\frac{dD}{dx}\left\lbrace \frac{j}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{j}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
+\frac{1}{|z_0|}\frac{dD}{dx}\left\lbrace e^{j\phi_0+j\pi/2} \left(\frac{dA}{dx}\right) + e^{-j\phi_0-j\pi/2} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\ 
+\frac{1}{|z_0|}\frac{dD}{dx}2\Re\left\lbrace e^{j\phi_0+j\pi/2} \left(\frac{dA}{dx}\right) \right\rbrace \label{eq:cross_terms}
+\end{multline}
+The expression in Eq. \ref{eq:cross_terms} simplifies to
+\begin{multline}
+\frac{1}{|z_0|}\frac{dD}{dx}2\Re\left\lbrace e^{j\phi_0+j\pi/2} \left(\frac{dA}{dx}\right) \right\rbrace = \\
+(8\pi\sin(2x_0(x-y_0)+2\phi_0)e^{-2xy_0}e^{-x_0^2+y_0^2} \\ -2xG(z_0)\sin(\phi_0) e^{-x^2})\frac{dD}{dx}
+\end{multline}
+Finally, we add the results of the four terms generated, and take the square root:
+\begin{multline}
+\frac{1}{2}| x_a (t) * y_a(t)| = \\
+16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} + \\ 4G^2(z_0)x^2 e^{-2x^2} - \\ 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right) + \\
+\frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right) + \\
+\frac{dD}{dx}(8\pi\sin(2x_0(x-y_0)+2\phi_0)e^{-2xy_0}e^{-x_0^2+y_0^2} - \\ 2xG(z_0)\sin(\phi_0) e^{-x^2})
 \end{multline}

### 2025-02-13 result.py

@@ -1,0 +1,16 @@
+import numpy as np
+from scipy.special import dawsn as F
+from scipy.special import expi as Ei
+import matplotlib.pyplot as plt
+
+def gauss(x):
+	return np.exp(-x*x)
+def G(x):
+	return np.sqrt(np.pi)*F(x)-0.5*gauss(x)*Ei(x*x)
+
+x = np.arange(0,5,0.01)
+plt.plot(x,G(x))
+plt.plot(x,np.exp(-x)+0.185)
+plt.show()
+
+#Next: extend to complex arguments

### 2025-02-14 result.py
update: added code to attempt plotting final results for x < Im(z0)

@@ -5,12 +5,41 @@ import matplotlib.pyplot as plt
 
 def gauss(x):
 	return np.exp(-x*x)
+def dDdx(x):
+	return 1-2*x*F(x)
 def G(x):
 	return np.sqrt(np.pi)*F(x)-0.5*gauss(x)*Ei(x*x)
+def plotit(X,Y,Z,title):
+    plt.figure()
+    cs = plt.contour(X,Y,Z,10) # contour() accepts complex values
+    plt.clabel(cs, inline=1, fontsize=10) # add labels to contours
+    plt.title(title)
+    plt.savefig(title+'.png')
+def result(x,z0,R0,E0,sigma_t):
+	term1 = 4*x*x*np.abs(G(z0))*np.abs(G(z0))*np.exp(-2*x*x)
+	term2 = 4*np.abs(G(z0))/np.abs(z0)*dDdx(x)*x*np.exp(-x*x)*np.cos(np.angle(z0)+np.angle(G(z0)))
+	term3 = 1.0/np.abs(z0)/np.abs(z0)*dDdx(x)*dDdx(x)
+	return np.sqrt(term1+term2+term3)
 
-x = np.arange(0,5,0.01)
-plt.plot(x,G(x))
-plt.plot(x,np.exp(-x)+0.185)
+#x = np.arange(0.01,1,0.01)
+#y = np.arange(0.01,1,0.01)
+#X,Y = np.meshgrid(x,y)
+#Z = np.zeros(X.shape)
+#n = len(x)
+#for i in range(n):
+#	for j in range(n):
+#		z = complex(X[i][j],Y[i][j])
+#		Z[i][j] = G(z)
+
+z0 = complex(10,0.1)
+R0 = 1
+E0 = 1
+sigma_t = 0.5
+x = np.arange(0,3,0.001)
+n = len(x)
+res = np.zeros(x.shape)
+for i in range(n):
+	res[i] = result(i,z0,R0,E0,sigma_t)
+
+plt.plot(x,20*np.log10(res))
 plt.show()
-
-#Next: extend to complex arguments

### 2025-02-15 template.tex
update: added code to attempt plotting final results for x < Im(z0)
updates to the final simplification, code to compare things

--- 2025-02-11 template.tex
@@
 Let the overall scale factor in Eq.
-\ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, and let $x>\Im\lbrace z_0\rbrace$.
+\ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, $\tan\phi_G = \Im(G(z_0))/\Re(G(z_0))$, and let $x>\Im\lbrace z_0\rbrace$.
 Upon taking the magnitude, the quantity in parentheses generates four terms.
@@
 \begin{multline}
-\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4G^2(z_0)x^2 e^{-2x^2} \\ - 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right)
+\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4|G(z_0)|^2x^2 e^{-2x^2} \\ - 16\pi |G(z_0)| |z_0| x e^{-x^2}e^{-2xy_0} e^{-(x_0^2-y_0^2)} \\ \times \cos(2 x_0 x - 2 x_0 y_0+\phi_0+\phi_{\rm G})
 \end{multline}
@@
 \begin{equation}
-\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right)
+\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2
 \end{equation}
-The combination of the third and forth terms is
+The cross-terms combine to form
 \begin{multline}
-j\frac{dD}{dx}\left\lbrace \frac{1}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{1}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
+2\frac{dD}{dx} \Re\left\lbrace \frac{j}{z_0^{*}} \frac{dA}{dx}\right\rbrace = \\
+\frac{dD}{dx}(8\pi\sin(2 x_0 x - 2 x_0 y_0+2\phi_0)e^{-2xy_0} e^{-(x_0^2-y_0^2)} \\
+-\frac{2|G(z_0)|}{|z_0|}x e^{-x^2}\sin(\phi_0+\phi_{\rm G})) \label{eq:cross_terms}
 \end{multline}
+Finally, we sum the terms and take the square root, multiply by $\frac{1}{2} R_0 E_0 \sigma_t^2/\sqrt{\pi}$, and we are done.
 \end{itemize}

### 2025-02-15 result.py

@@ -1,4 +1,5 @@
 import numpy as np
+from scipy.signal import convolve
 from scipy.special import dawsn as F
 from scipy.special import expi as Ei
 import matplotlib.pyplot as plt
@@ -15,31 +16,49 @@ def plotit(X,Y,Z,title):
     plt.clabel(cs, inline=1, fontsize=10) # add labels to contours
     plt.title(title)
     plt.savefig(title+'.png')
-def result(x,z0,R0,E0,sigma_t):
-	term1 = 4*x*x*np.abs(G(z0))*np.abs(G(z0))*np.exp(-2*x*x)
-	term2 = 4*np.abs(G(z0))/np.abs(z0)*dDdx(x)*x*np.exp(-x*x)*np.cos(np.angle(z0)+np.angle(G(z0)))
-	term3 = 1.0/np.abs(z0)/np.abs(z0)*dDdx(x)*dDdx(x)
-	return np.sqrt(term1+term2+term3)
+def envelope(x,z0,R0,E0,sigma_t):
+	x0 = z0.real
+	y0 = z0.imag
+	phi0 = np.angle(z0)
+	abs_z_0 = np.abs(z0)
+	abs_z_0_2 = abs_z_0*abs_z_0
+	G0 = G(z0)
+	phiG = np.angle(G0)
+	abs_G_0 = np.abs(G0)
+	abs_G_0_2 = abs_G_0
+	phase1 = -2*x0*y0+phi0+phiG
+	term1a = 16*(np.pi*np.pi)*abs_z_0_2*np.exp(-4*x*y0)*np.exp(-2*(x0*x0-y0*y0))
+	term1b = 4*x*x*abs_G_0_2*np.exp(-2*x*x)
+	term1c = -16*np.pi*abs_G_0*abs_z_0*np.exp(-2*x*y0)*x*np.exp(-x*x)*np.cos(2*x0*x+phase1)
+	term1 = term1a+term1b+term1c
+	term2 = 1/abs_z_0_2*(dDdx(x)*dDdx(x))
+	term3a = dDdx(x)*(8*np.pi*np.sin(2*x*x0-2*x0*y0+2*phi0)*np.exp(-2*x*y0)*np.exp(-2*(x0*x0-y0*y0)))
+	term3b = dDdx(x)*(-2*abs_G_0/abs_z_0*x*np.exp(-x*x)*np.sin(phi0+phiG))
+	term3 = term3a+term3b
[…]

### 2025-03-11 result.py
changes to result.py, following significant reorg of calculations

@@ -1,64 +1,35 @@
 import numpy as np
-from scipy.signal import convolve
+from scipy.signal import convolve,hilbert
 from scipy.special import dawsn as F
 from scipy.special import expi as Ei
+from scipy.special import wofz as w
 import matplotlib.pyplot as plt
 
-def gauss(x):
-	return np.exp(-x*x)
-def dDdx(x):
-	return 1-2*x*F(x)
-def G(x):
-	return np.sqrt(np.pi)*F(x)-0.5*gauss(x)*Ei(x*x)
-def plotit(X,Y,Z,title):
-    plt.figure()
-    cs = plt.contour(X,Y,Z,10) # contour() accepts complex values
-    plt.clabel(cs, inline=1, fontsize=10) # add labels to contours
-    plt.title(title)
-    plt.savefig(title+'.png')
-def envelope(x,z0,R0,E0,sigma_t):
-	x0 = z0.real
-	y0 = z0.imag
-	phi0 = np.angle(z0)
-	abs_z_0 = np.abs(z0)
-	abs_z_0_2 = abs_z_0*abs_z_0
-	G0 = G(z0)
-	phiG = np.angle(G0)
-	abs_G_0 = np.abs(G0)
-	abs_G_0_2 = abs_G_0
-	phase1 = -2*x0*y0+phi0+phiG
-	term1a = 16*(np.pi*np.pi)*abs_z_0_2*np.exp(-4*x*y0)*np.exp(-2*(x0*x0-y0*y0))
-	term1b = 4*x*x*abs_G_0_2*np.exp(-2*x*x)
-	term1c = -16*np.pi*abs_G_0*abs_z_0*np.exp(-2*x*y0)*x*np.exp(-x*x)*np.cos(2*x0*x+phase1)
-	term1 = term1a+term1b+term1c
-	term2 = 1/abs_z_0_2*(dDdx(x)*dDdx(x))
-	term3a = dDdx(x)*(8*np.pi*np.sin(2*x*x0-2*x0*y0+2*phi0)*np.exp(-2*x*y0)*np.exp(-2*(x0*x0-y0*y0)))
-	term3b = dDdx(x)*(-2*abs_G_0/abs_z_0*x*np.exp(-x*x)*np.sin(phi0+phiG))
-	term3 = term3a+term3b
[…]

### 2025-03-12 result.py
Updated calculations in result.py

@@ -5,31 +5,64 @@ from scipy.special import expi as Ei
 from scipy.special import wofz as w
 import matplotlib.pyplot as plt
 
+def G(z0):
+	z0 = np.real(z0)
+	return np.sqrt(np.pi)*F(z0)-0.5*np.exp(-z0*z0)*Ei(z0*z0)
 def s(t,E0,sigma_t):
 	return -E0*t*np.exp(-0.5*(t/sigma_t)*(t/sigma_t))
-def wat(t,E0,R0,sigma_t,f0,gamma):
+def r(t,R0,f0,gamma):
+	return R0*np.cos(2*np.pi*f0*t)*np.exp(-gamma*t)
+def ra(t,R0,f0,gamma):
 	J = complex(0,1)
-	y = t/np.sqrt(2)/sigma_t
-	zp = np.sqrt(2)*sigma_t*complex(gamma,2*np.pi*f0)
-	zm = np.sqrt(2)*sigma_t*complex(gamma,-2*np.pi*f0)
-	c = -J*(y-zp/2)
-	d = -J*(y-zm/2)
-	first_term = np.sqrt(np.pi)/2/np.sqrt(2)*R0*sigma_t*s(t,E0,sigma_t)*(w(c)+w(d))
-	second_term = np.sqrt(2)*R0*E0*sigma_t*sigma_t*np.exp(-y*y)*(1+J*(c*w(c)+d*w(d)))
-	return first_term+second_term
+	return R0*np.exp(2*np.pi*J*f0*t)*np.exp(-gamma*t)
+def math_conv(t,E0,R0,sigma_t,f0,gamma):
+	J = complex(0,1)
+	sigma_f = 1.0/(2*np.pi*sigma_t)
+	p = (t/sigma_t)*(sigma_f/f0) - gamma/(2*np.pi*f0)
+	q = 0.5*(sigma_f/f0)*(sigma_f/f0)
+	z = complex(1.0/(2.0*np.sqrt(q)),-p/(2.0*np.sqrt(q)))
+	U = np.sqrt(np.pi/(4.0*q))*np.real(w(z))
+	dUdp = np.sqrt(np.pi)/(4*q)*(2/np.sqrt(np.pi) + 2*np.real(J*z*w(z)))
+	first_term = np.sqrt(np.pi/2)*sigma_t*R0*s(t,E0,sigma_t)*U
[…]

### 2025-03-12 template.tex
Big update: plotting results, finished envelope math

--- 2025-02-11 template.tex
@@
 \begin{equation}
-\sigma_{\rm t} \sigma_{\rm f} \geq \frac{1}{2\pi}
+\sigma_t \sigma_f \geq \frac{1}{2\pi}
 \end{equation}
@@
 In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.
-\item Equation \ref{eq:awesome} will now be applied, using the definition of $r_a(t)$ and the Fourier transform of $s(t)$, $S(f)$.
-The Fourier transform of $r_a(t) * s_a(t)$ is $R_a(f) S_a(f)$.
-Using the definition of the analytic signal, we have
+\item The goal is now to apply Eq.
+\ref{eq:awesome} by convolving $s_a(t)$ with $r_a(t)$.
+The real part of $s_a(t)$ can be convolved with $r_a(t)$ in the time domain.
+As in Eq.
+\ref{eq:sa_4}, real part of $s_a(t)$ is $s(t)$.
+Since $r_a(t<0)=0$, the convolution is written
 \begin{equation}
-R_a(f) S_a(f) = R_a(f)(1 + \sgn(f)) S(f) \label{eq:midway}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r(\tau) s(t-\tau) d\tau
 \end{equation}
-The Fourier transform of $r_a(t)$ is
+Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z_0 = \sqrt{2}\sigma_t(\gamma-2\pi jf_0)$. The convolution may be organized as follows
+\begin{equation}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = R_0 s(t) I + R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t^2)} \frac{dI}{dt} \label{eq:conv}
+\end{equation}
+with
+\begin{equation}
+I(x,z_0) = \sqrt{2}\sigma_t \int_0^{\infty} e^{-y^2 + (2x-z_0)y} dy
+\end{equation}
+Let $b = x-z_0/2$. Completing the square in the exponent produces
+\begin{equation}
+I(x,z_0) = \sqrt{2}\sigma_t e^{b^2} \int_0^{\infty} e^{-(y-b)^2} dy
+\end{equation}
+The integral may be cast as a complementary error function by substituting $u=y-b$ and letting $b=jz$:
+\begin{equation}
+I(x,z_0) = \sqrt{\frac{\pi}{2}}\sigma_t e^{-z^2}\erfc(-jz)
+\end{equation}
+Thus, the integral is proportional to the \textit{Faddeeva function}, $w(z)$:
+\begin{equation}
+I(x,z_0) = \sqrt{\frac{\pi}{2}} \sigma_t w(z) \label{eq:fadd}
+\end{equation}
+Subsituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces
+\begin{multline}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
+-j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz}
+\end{multline}
+Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq.
+\ref{eq:sa_4} contains $dD(x)/dx$, the derivative of the Dawson function.
+To complete the convolution, the inverse Fourier transform of the product of the Fourier transforms of $r_a(t)$ and $\Im\lbrace s_a(t)\rbrace$ is calculated.
+To complete this step, the Fourier transform of $dD(x)/dx$ is needed:
 \begin{align}
-R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z_0} \\
-z_0 &= f_0 + \frac{j\gamma}{2\pi}
+x &= t/(\sqrt{2}\sigma_t) \\
+f' &= \sqrt{2} \sigma_t f \\
+\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \int_{-\infty}^{\infty} \frac{dD(x)}{dx}e^{-2\pi jft} dt \\
+\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \sqrt{2}\sigma_t(2\pi jf') \int_{-\infty}^{\infty} D(x) e^{-2\pi jf'x} dx \\
+\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= 2\pi^2 \sigma_t^2 f e^{-\frac{1}{2}(f/\sigma_f)^2} \sgn(f)
 \end{align}
-The Fourier transform $S(f)$ is given by Eq.
-\ref{eq:spec}.
-Inserting the spectra into Eq.
-\ref{eq:midway} and taking the inverse Fourier transform should give $r_a(t) * s_a(t)$.
-Note the inverse transform integral is only over positive frequencies, due to the $1+\sgn(f)$ factor.
-Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.
-Note also that it is prudent to consider the signal $s(t)$ shifted by a $t_0$, to ensure the entire signal is convolved with $r(t)$.
-For time-shifts, the Fourier transform responds like:
-\begin{equation}
-\mathcal{F}\left\lbrace s(t-t_0)\right\rbrace = e^{-2\pi f t_0} S(f)
-\end{equation}
-The result is
+Let $z_0 = (\gamma - 2\pi jf_0)$, so that the Fourier transform of $r_a$ is 
+\begin{align}
+\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{-\infty}^{\infty} e^{-zt} e^{-2\pi j ft} dt \\
+\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= \frac{R_0}{z_0+2\pi j f}
+\end{align}
+Let $z_1 = f_0 + j\gamma/(2\pi)$. Multiplying the Fourier transforms, and simplifying, yields
 \begin{multline}
-r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j f(t-t_0)} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df
+\mathcal{F}\left\lbrace r_a(t) * \Im\left\lbrace s_a(t)\right\rbrace \right\rbrace = \\ -j \sqrt{2\pi} R_0 E_0 \sigma^3 \frac{f\sgn(f) e^{-\frac{1}{2}(f/\sigma_f)^2}}{f-z_1}
 \end{multline}
-Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z_0 \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
+The inverse Fourier transform now gives $r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace$:
 \begin{multline}
-r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right) \label{eq:withI}
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+-j\sqrt{2\pi} R_0 E_0 \sigma_t^3 \int_{-\infty}^{\infty} \frac{f\sgn(f)e^{-\frac{1}{2}(f/\sigma_f)^2}e^{2\pi jft}}{f-z_1} df
 \end{multline}
-All that remains is to evaluate the integral
-\begin{equation}
-I(z,z_0) = \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy
-\end{equation}
-Let $z = x+jy$, $dy = -jdz$, and $z_1 = x+jz_0$.  The integral becomes, as $R \to \infty$,
-\begin{equation}
-I(x,z_0) = \int_{x}^{x+jR} \frac{e^{z^2}}{z - z_1} dz
-\end{equation}
-$I(x,z_0)$ can be evaluated via contour integration, with a rectangular contour that encloses the pole if $x > \Im\lbrace z_0\rbrace$.
-Let $I_1$ extend from $(x,0)$ to ($x,jR)$.
-Let $I_2$ extend from $(x,jR)$ to $(0,jR)$.
-Let $I_3$ extend from $(0,jR)$ to $(0,0)$.
-Finally, let $I_4$ extend from $(0,0)$ to $(x,0)$.
-Note that $I_1 = I(x,z_0)$.
-For the integral $I_2$, note that the exponential factor is proportional to $\exp(-R^2)$, while the denominator contains another factor of $R$.
-Since $dz = dx$, the integrand goes as $\exp(-R^2)/R$, vanishing as $R \to \infty$.
-For $I_3$, $x=0$.
-Thus, it reduces to
-\begin{equation}
-I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y-z_0} dy = -G(-z_0) = G(z_0)
-\end{equation}
-
-The function $G(z_0)$ is a function with odd-symmetry known as the Goodwin-Staton integral.
-$G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.
-It is commonly used in problems involving diffusion approximations, particularly in media with semi-infinite boundary conditions.
-The final segment of the contour is
-\begin{equation}
-I_4 = \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
-\end{equation}
-The sum of contour segments is $I_1 + I_2 + I_3 + I_4 = I_{\rm C}$, where $I_{\rm C}$ is given by the Cauchy integral formula: $2\pi j e^{z_1^2}$.  Solving for $I(x,z_0)$, we find
-\begin{equation}
-I(x,z_0) = 2\pi j e^{z_1^2} - G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
-\end{equation}
-If $x < \Im\lbrace z_0\rbrace$,
-\begin{equation}
-I(x,z_0) = -G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
-\end{equation} \\
-Inserting this result into Eq. \ref{eq:withI},
+Let $y = f/(\sqrt{2}\sigma_f)$, $x=t/(\sqrt{2}\sigma_t)$, $\sgn(f) = \sgn(y)$, and $z_1 \to f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.
+The inverse Fourier transform can be organized as:
 \begin{multline}
-r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(\frac{dA(x,z_0)}{dx}-\frac{j}{z_0}\frac{dD(x)}{dx} \right) \label{eq:ra_sa_1}
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+-\frac{R_0E_0\sigma_t^3}{\sqrt{2\pi}}\frac{d}{dt}\int_{-\infty}^{\infty} \frac{\sgn(y) e^{-y^2+2jxy}}{y-z_1} dy
 \end{multline}
-with
-\begin{align}
-A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} - G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
-A(x,z_0) &= -G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
-\end{align}
-and
-\begin{equation}
-D(x) = e^{-x^2} \int_{0}^{x} e^{x'^2} dx'
-\end{equation}
-What remains is to compute the magnitude of Eq.
-\ref{eq:ra_sa_1}.
-Let the overall scale factor in Eq.
-\ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, and let $x>\Im\lbrace z_0\rbrace$.
-Upon taking the magnitude, the quantity in parentheses generates four terms.
-The first is
+Completing the square in the exponent, factoring a unit of $j$ from the exponent, and changing the derivative from $d/dt$ to $d/dx$ gives
 \begin{multline}
-\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4G^2(z_0)x^2 e^{-2x^2} \\ - 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right)
-\end{multline}
-The second is
-\begin{equation}
-\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right)
-\end{equation}
-The combination of the third and forth terms is
-\begin{multline}
-j\frac{dD}{dx}\left\lbrace \frac{1}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{1}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{-\infty}^{\infty} \frac{\sgn(y) e^{(x+jy)^2}}{y-z_1}
 \end{multline}

### 2025-03-12 result.py

@@ -31,38 +31,53 @@ def math_conv(t,E0,R0,sigma_t,f0,gamma):
 		return first_term+second_term
 def math_env(t,E0,R0,sigma_t,f0,gamma):
 	J = complex(0,1)
+	x = t/(sigma_t*np.sqrt(2))
 	sigma_f = 1.0/(2*np.pi*sigma_t)
 	z0 = complex(f0/np.sqrt(2)/sigma_f,gamma/(2*np.pi*np.sqrt(2)*sigma_f))
-	first_term = -E0*sigma_t*sigma_t*ra(t,R0,f0,gamma)*(1-J*np.sqrt(np.pi)*z0*w(-z0))
+	z1 = complex(np.sqrt(2)*np.pi*sigma_t*f0,sigma_t*gamma/np.sqrt(2)-x)
+	first_term = np.sqrt(np.pi/2)*R0*sigma_t*s(t,E0,sigma_t)*w(z1)
+	first_term += R0*E0*sigma_t*sigma_t*np.exp(-x*x)*(1+J*np.sqrt(np.pi)*z1*w(z1))
 	second_term = E0*sigma_t*sigma_t*z0*np.exp(-z0*z0)*np.sqrt(np.pi)*ra(t,R0,f0,gamma)
 	second_term += np.sqrt(2/np.pi)*G(z0)*R0*sigma_t*s(t,E0,sigma_t)
-	if(t<0 or np.isinf(first_term) or np.isinf(second_term) or np.isnan(first_term) or np.isnan(second_term)):
+	if(t<-sigma_t*gamma or np.isinf(first_term) or np.isinf(second_term) or np.isnan(first_term) or np.isnan(second_term)):
 		return 0.0
 	else:
 		return 0.5*np.abs(first_term+J*second_term)
 
-f0 = 0.75 #GHz
-gamma = 0.5 #GHz
-sigma_t = 0.2 #ns
+f0 = 0.2 #GHz
+gamma = 0.2 #GHz
+sigma_t = 0.75 #ns
 R0 = 1
 E0 = 1
-dt = 0.01
-T_min = -20
-T_max = 108
+dt = 0.01 #ns
+T_min = -20 #ns
+T_max = 108 #ns
 
 t = np.arange(T_min,T_max,dt)
 n = len(t)
 result1 = np.zeros(t.shape,dtype=complex)
 result2 = np.zeros(t.shape,dtype=complex)
 for i in range(n):
[…]

### 2025-03-12 template.tex
continuing to dump my mathematics in latex

@@
 \end{multline}
-Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq.
+\item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq.
 \ref{eq:sa_4} contains $dD(x)/dx$, the derivative of the Dawson function.
@@
 r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{-\infty}^{\infty} \frac{\sgn(y) e^{(x+jy)^2}}{y-z_1}
+-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{-\infty}^{\infty} \frac{\sgn(y) e^{(x+jy)^2}}{y-z_1}dy
+\end{multline}
+Let $z = x+jy$, with $y = \Im(z)$.
+In this substitution, $x$ is treated as a constant, so $dz = jy$.
+Let $z_2 = x+j z_1$, while $z_1 = f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.
+The result is
+\begin{multline}
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{x-j\infty}^{x+j\infty} \frac{\sgn(\Im(z)) e^{z^2}}{y-z_2}dz \label{eq:cont_int}
+\end{multline}
+The integral may be finished by extending $z$ to the complex plane and using contour integration.
+The location of the pole is in the first quadrant, unless $t = (\gamma \sigma_t)\sigma_t$.
+In that case, $\Re(z_2)=0$, and the pole is located on the imaginary axis.
+For typical values of $\sigma_t$ and $\gamma$, $t\approx 0.1$ ns.
+Since $r(t)=0$ if $t<0$, the location of $z_2$ is usually in the first quadrant.
+Let the line integrals of the rectangular contour be: $I_1$, $(x,-jR) \to (x,jR)$, $I_2$, $(x,jR) \to (0,jR)$, $I_3$, $(0,jR) \to (0,-jR)$, and $I_4$, $(0,-jR) \to (x,-jR)$.
+$I_2$ and $I_4$ are both proportional to $\exp(-R^2)$, so $I_2 \to 0$ and $I_4 \to 0$ when $R \to \infty$.
+$I_1$ is the integral in Eq.
+\ref{eq:cont_int}.
+Let $w = -y$, so that $I_3$ is
+\begin{equation}
+I_3 = -\int_0^{R} \frac{e^{-y^2}}{y-z_1} dy + \int_0^{R} \frac{e^{-w^2}}{w+z_1} dw
+\end{equation}
+Integrals of the type in $I_3$ are known as \textit{Goodwin-Staton} functions, and are related to the other error functions.
+The Goodwin-Staton function, $G(z_1)$, is odd, so $-G(-z_1) = G(z_1)$.
+The result for $I_3$ is
+\begin{equation}
+I_3 = -G(-z_1) + G(z_1) = 2G(z_1)
+\end{equation}
+The residue of the enclosed contour $I_C = I_1+I_2+I_3+I_4$ is $\exp(z_2^2)$.  With $I_2$, $I_3$, and $I_4$ completed, the solution for $I_1$ is
+\begin{equation}
+I_1 = 2\pi j e^{z_2^2} - 2G(z_1)
+\end{equation}
+Inserting this result into Eq. \ref{eq:cont_int}, and simplifying, gives
+\begin{multline}
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_0 - z_0^2 \right)
 \end{multline}

### 2025-03-13 template.tex
final big update (with figures) before April/March APS 2025

@@
 \usepackage{empheq}
+\usepackage{verbatim}
 \DeclareMathOperator\erfc{erfc}
@@
 \end{multline}
+Finally, the derivative of the Faddeeva function is $dw/dz = 2j/\sqrt{\pi} - 2 zw(z)$.  Substituting for $dw/dz$ gives the final result:
+\begin{multline}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
++ R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) \label{eq:Re_result}
+\end{multline}
 \item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq.
@@
 r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_0 - z_0^2 \right)
+-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_1 - z_1^2} - 2G(z_1) e^{-x^2} \right)
 \end{multline}
+Notice that $2\pi j x z_1 = 2\pi j f_0 t - \gamma t$.  Evaluating the derivative and simplifying gives the final result:
+\begin{multline}
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:Im_result}
+\end{multline}
+\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:
+\begin{multline}
+r_a(t) * s_a(t) = \\
+\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) + \\
+R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) + \\
+j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \\
+j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}
+\end{multline}
+The units of the convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq.\ref{eq:final} has these units.
+The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.
+The units of the second term are $R_0 E_0\sigma_t^2$.
+The third term has units of $E_0\sigma_t^2 r_a(t)$, and $r_a(t)$ has units of $R_0$, so the unit product is $R_0 E_0\sigma_t^2$.
+The fourth term has units of $R_0 \sigma_t s(t)$, like the first term.
+Thus, all units check.
+To check the limits, the parameters $z$ and $z_1$ must be recalled.
+Combining prior definitions, the results are
+\begin{align}
+z &= \sqrt{2}\sigma_t \pi f_0 + j\left(\frac{\sigma_t\gamma}{\sqrt{2}} - x\right) \\
+z_1 &= f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)
+\end{align}
+Recall that $\sigma_t = 1/(2\pi \sigma_f)$, and $x=t/(\sqrt{2}\sigma_t)$.  Substituting this into the definition of $z$ reveals that
+\begin{equation}
+z_1 = z + jx
+\end{equation}
+Thus, when $t=0$, the two poles are equal, since $t=0$ means $x=0$.  Taking the magnitude of Eq. \ref{eq:final}, and multiplying by $1/2$, gives the final result:
+\begin{equation}
+\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) |
+\end{equation}
+\item Two examples of comparisons of Eq. \ref{eq:final} to the convolution of $s(t)$ and $r(t)$ are given in Fig. \ref{fig:fig1} below.
+\begin{figure}[hb]
+\centering
+\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
+\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
+\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
+The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
+The light gray envelope represents Eq.
+\ref{eq:final}.
+(Bottom) Same as top, for different parameter values.}
+\end{figure}
 \end{itemize}
+\clearpage
 

### 2025-03-14 APS_2025/main.tex
big update op APS presentation

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{graphicx}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator\erfc{erfc}
\definecolor{box_background}{RGB}{225,225,225}
\definecolor{box_frame}{RGB}{0,0,0}
\title{Complex analysis of Askaryan radiation: energy and angular reconstruction of ultra-high energy neutrinos}
\author{Jordan C. Hanson and Raymond Hartig}
\institute{Dept. of Physics and Astronomy \\ Whittier College \\ Whittier, CA}

\begin{document}
\titlegraphic{\vspace{6cm}\hspace{6.8cm}\includegraphics[width=4cm,height=2cm]{WhittierImages.pdf}}  
\maketitle

\begin{frame}{Outline: from mathematical physics to UHE-$\nu$ observations}
\begin{columns}[T]
\begin{column}{0.5\textwidth}
\textbf{\alert{Background}}
\begin{itemize}
\item UHE-$\nu$ flux
\item The Askaryan effect
\item RF UHE-$\nu$ detectors
\end{itemize}
\textbf{\alert{The Askaryan signal}}
\begin{itemize}
\item Analytic radiation model
\item Signal \textit{envelopes}
\item Uncertainty principles
\end{itemize}
\textbf{\alert{Event reconstruction}}
\begin{itemize}
\item \textbf{NuRadioMC}: MC software
\item Mathematics $\leftrightarrow$ signals
\item Initial results
\end{itemize}
\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{whittier3.jpeg}
\includegraphics[width=0.9\textwidth]{whittier1.jpeg}
\caption{\small Whittier College.}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\section{Background}

\begin{frame}{Background: in-ice UHE-$\nu$ observations}
\small
\begin{columns}[T]
\begin{column}{0.32\textwidth}
\textbf{\alert{UHE-$\nu$ detection via the Askaryan Effect}}
\begin{itemize}
\item \textbf{E$_{\nu} \geq $10$^{16}$ eV}
\item \textbf{Flux is small}
\item Cascades $\leftrightarrow$ RF
\item Ice is transparent
\item Station arrays
\end{itemize}
\end{column}
\begin{column}{0.68\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{flux.png}
\caption{\footnotesize UHE-$\nu$ flux predictions and upper limits.}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Background: in-ice UHE-$\nu$ observations}
\small
\begin{columns}[T]
\begin{column}{0.32\textwidth}
\textbf{\alert{UHE-$\nu$ detection via the Askaryan Effect}}
\begin{itemize}
\item $E_{\nu} \geq 10^{16}$ eV
\item Flux is small
\item \textbf{Cascades $\leftrightarrow$ RF}
\item Ice is transparent
\item Station arrays
\end{itemize}
\end{column}
\begin{column}{0.68\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{ARIANNA_principle.png}
\includegraphics[width=0.9\textwidth]{icd.png}
\caption{\footnotesize The Askaryan effect.}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Background: in-ice UHE-$\nu$ observations}
\small
\begin{columns}[T]
\begin{column}{0.32\textwidth}
\textbf{\alert{UHE-$\nu$ detection via the Askaryan Effect}}
\begin{itemize}
\item $E_{\nu} \geq 10^{16}$ eV
\item Flux is small
\item Cascades $\leftrightarrow$ RF
\item \textbf{Ice is transparent}
\item Station arrays
\end{itemize}
\end{column}
\begin{column}{0.68\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{moores_atten.png}
\includegraphics[width=0.6\textwidth]{atten_greenland.png}
\caption{\footnotesize RF attenuation lengths in ice.}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Background: in-ice UHE-$\nu$ observations}
\small
\begin{columns}[T]
\begin{column}{0.32\textwidth}
\textbf{\alert{UHE-$\nu$ detection via the Askaryan Effect}}
\begin{itemize}
\item $E_{\nu} \geq 10^{16}$ eV
\item Flux is small
\item Cascades $\leftrightarrow$ RF
\item Ice is transparent
\item \textbf{Station arrays}
\end{itemize}
\end{column}
\begin{column}{0.68\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{RNO-G.png} \hspace{0.5cm}
\includegraphics[width=0.55\textwidth]{ARA.png}
\caption{\footnotesize In-ice UHE-$\nu$ detectors. \textbf{Left:} RNO-G (Greenland). \textbf{Right:} ARA (Antarctica).}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\section{The Askaryan Signal}

\begin{frame}{The Askaryan Signal: equation for $\vec{E}$-field}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Askaryan electric field, $\vec{E}(r,t)$, [V m$^{-1}$]}]
\begin{equation}
r \vec{E}(t,\theta) = -\frac{E_0 \omega_0 \sin(\theta)}{8 \pi p} t_r e^{-\frac{t_r^2}{4p} + p \omega_0^2}\erfc(\sqrt{p}\omega_0)
\end{equation}
\end{tcolorbox}
\footnotesize
\begin{columns}[T]
\begin{column}{0.49\textwidth}
\textbf{Geometric parameters}
\begin{table}
\centering
\begin{tabular}{c|c}
$r$ & vertex distance [m] \\
$E_0$ & E-field amplitude [V GHz$^{-2}$] \\
$t_r$ & Retarded time [ns]\footnote{Definition: $t_{\rm r} = t_{\rm ref} - nR/c$.} \\
$\theta$ & Observation angle [rad] \\
$p$ & $\sigma_t = \sqrt{2p}$ (Eq. \ref{eq:p}) [ns$^2$]
\end{tabular}
\end{table}
\end{column}
\begin{column}{0.49\textwidth}
\textbf{Particle physics parameters}
\begin{table}
\centering
\begin{tabular}{c|c}
$\omega_0$ & Form-factor frequency [GHz] \\
$\theta_{\rm C}$ & Cherenkov angle [rad] \\
$p$ & $\sigma_t = \sqrt{2p}$ (Eq. \ref{eq:p}) [ns$^2$] \\
$a$ & Cascade length (Eq. \ref{eq:p}) [m]
\end{tabular}
\end{table}
\begin{align}
p =& \frac{1}{2}\left(\frac{a}{c}\right)^2 \left(\cos\theta - \cos\theta_C\right)^2 \label{eq:p} \\
\sqrt{2p} \approx & ~(a/c)|\theta - \theta_{\rm C}|\sin\theta_{\rm C} \\
\sigma_t =& \sqrt{2p} \propto ~ a\Delta\theta
\end{align}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{The Askaryan Signal: $\vec{E}$-field time-dependence, analytic signal}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Askaryan electric field, $\vec{E}(r,t)$, [V m$^{-1}$], time-dependence}]
\begin{equation}
s(t) = \vec{E}(t,\theta) = -E_0 t e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2}
\end{equation}
\end{tcolorbox}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Askaryan electric field \textit{analytic signal}}]
\begin{equation}
s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{2 j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right)
\end{equation}
\end{tcolorbox}
\footnotesize
\begin{columns}[T]
\begin{column}{0.49\textwidth}
\textbf{The signal envelope}
\begin{itemize}
\item $s_a(t) = s(t) + j ~ \widehat{s}(t)$
\item $\widehat{s}(t)$, Hilbert transform
\item $|s_a(t)|$, signal \textit{envelope}
\end{itemize}
\end{column}
\begin{column}{0.49\textwidth}
\textbf{Special functions and variables}
\begin{itemize}
\item $D(x)$, Dawson function
\item $x = t/(\sqrt{2}\sigma_t)$, normalized time
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{The Askaryan Signal: detected signals}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Common response function for RF channels $r(t)$, [m ns$^{-1}$]}]
\begin{equation}
r(t) = R_0 \cos(2\pi f_0 t) e^{-\gamma t}
\end{equation}
\end{tcolorbox}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Common analytic signal for RF channels $r_a(t)$, [m ns$^{-1}$]}]
\begin{equation}
r_a(t) = R_0 e^{2\pi j f_0 t-\gamma t}
\end{equation}
\end{tcolorbox}
\footnotesize
\begin{columns}[T]
\begin{column}{0.49\textwidth}
\textbf{The signal envelope}
\begin{itemize}
\item $r_a(t) = r(t) + j ~ \widehat{r}(t)$
\item $\widehat{r}(t)$, Hilbert transform
\item $|r_a(t)|$, signal \textit{envelope}
\end{itemize}
\end{column}
\begin{column}{0.49\textwidth}
\textbf{RF channels: RLC circuits}
\begin{itemize}
\item $|r_a(t)| = R_0\exp(-\gamma t)$
\item $\gamma$, damping coefficient [GHz]
\item $f_0$, resonance frequency [GHz]
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{The Askaryan Signal: detected signals}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Detected signals, $r(t) * s(t)$, [V]}]
\begin{equation}
r(t) * s(t) = \int_{-\infty}^{\infty} r(\tau) s(t-\tau) d\tau \rightarrow \int_{0}^{\infty} r(\tau) s(t-\tau) d\tau
\end{equation}
\end{tcolorbox}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title=Theorem: the envelope of detected signal]
Let $\mathcal{E}_{r * s}(t)$ represent the \textit{envelope} of the convolution of $r(t)$ and $s(t)$.  If $s_a(t)$ and $r_a(t)$ are the analytic signals of $s(t)$ and $r(t)$, respectively, then
\begin{equation}
\mathcal{E}_{r*s}(t) = \frac{1}{2}|r_a(t) * s_a(t)|
\end{equation}
\end{tcolorbox}
\end{frame}

\begin{frame}{The Askaryan Signal: uncertainty principles}
\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Uncertainty principles within Askaryan field}]
Let $\Delta\theta = \theta - \theta_{\rm C}$.  Let $a$ be the cascade length, $c$ be the speed of light, $\sigma_t$ be the pulse width, and $\sigma_f$ be the width of the Fourier spectrum.
\begin{equation}
a\Delta\theta = \frac{c\sigma_t}{\sin\theta_{\rm C}}
\end{equation}
Further, $s(t)$, and $S(f)$ (the Fourier transform), have widths that satisfy
\begin{equation}
\sigma_t \sigma_f = \frac{1}{2\pi}\left(1+\eta^2\right)^{1/2}
\end{equation}
In the far-field, $\eta \to 0$.
\end{tcolorbox}
\end{frame}

\begin{frame}[fragile]{The Askaryan Signal: scanning $a$ and $\Delta\theta$}
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,trim=2cm 9cm 2cm 10cm,clip=true]{example_scan.pdf}
\caption{\label{fig:scan} Scanning Askaryan field equation parameters to fit NuRadioMC output.}
\end{figure}
\textbf{Energy reconstruction potential:} $a^2 \propto \ln(E_{\rm C}/E_{\rm crit})$
\end{frame}

\section{Conclusion}

\begin{frame}{Unit 1.1 Outline}
Unit 1.1 covered:

\end{frame}

\end{document}

### 2025-03-14 result.py

@@ -46,7 +46,7 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 
 f0 = 0.2 #GHz
 gamma = 0.2 #GHz
-sigma_t = 0.75 #ns
+sigma_t = 2 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
@@ -65,7 +65,7 @@ graph2 = np.abs(hilbert(np.real(result1)))*1000
 graph3 = np.real(result2)*1000
 graph3 *= np.max(graph2)/np.max(graph3)
 plt.plot(t,graph1,'-',label="mathematical convolution")
-plt.plot(t,graph2,'-',label="envelope of mathematical convolution")
+plt.plot(t,-graph2,'-',label="envelope of mathematical convolution")
 plt.plot(t,graph3,'-',label="mathematical envelope")
 plt.xlabel("Time [ns]")
 plt.ylabel("Amplitude [mV]")
@@ -74,7 +74,7 @@ plt.yticks()
 plt.legend()
 plt.show()
 
-f = open("results_March12_2.dat","w")
+f = open("results_March12_3.dat","w")
 separator = " "
 for i in range(n):
 	data = [t[i],graph1[i],graph2[i],graph3[i]]

### 2025-03-14 APS_2025/main.tex
finished APS 2025 talk

@@
 \usepackage{hyperref}
+\usepackage{verbatim}
 \DeclareMathOperator\erfc{erfc}
-\definecolor{box_background}{RGB}{225,225,225}
-\definecolor{box_frame}{RGB}{0,0,0}
+\DeclareMathOperator\Ei{Ei}
+\definecolor{box_background}{RGB}{240,240,240}
+\definecolor{box_frame}{RGB}{40,40,40}
 \title{Complex analysis of Askaryan radiation: energy and angular reconstruction of ultra-high energy neutrinos}
@@
 \begin{itemize}
+\item Mathematics $\leftrightarrow$ signals
 \item \textbf{NuRadioMC}: MC software
-\item Mathematics $\leftrightarrow$ signals
 \item Initial results
@@
 \item \textbf{Cascades $\leftrightarrow$ RF}
-\item Ice is transparent
-\item Station arrays
-\end{itemize}
-\end{column}
-\begin{column}{0.68\textwidth}
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{ARIANNA_principle.png}
-\includegraphics[width=0.9\textwidth]{icd.png}
-\caption{\footnotesize The Askaryan effect.}
-\end{figure}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}{Background: in-ice UHE-$\nu$ observations}
-\small
-\begin{columns}[T]
-\begin{column}{0.32\textwidth}
-\textbf{\alert{UHE-$\nu$ detection via the Askaryan Effect}}
-\begin{itemize}
-\item $E_{\nu} \geq 10^{16}$ eV
-\item Flux is small
-\item Cascades $\leftrightarrow$ RF
 \item \textbf{Ice is transparent}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{moores_atten.png}
-\includegraphics[width=0.6\textwidth]{atten_greenland.png}
-\caption{\footnotesize RF attenuation lengths in ice.}
+\includegraphics[width=0.45\textwidth]{ARIANNA_principle.png} \\
+\includegraphics[width=0.55\textwidth]{atten_greenland.png}
+\caption{\footnotesize (Top) Detectors use the Askaryan effect. (Bottom) RF attenuation lengths in ice.}
 \end{figure}
@@
 \includegraphics[width=0.55\textwidth]{ARA.png}
-\caption{\footnotesize In-ice UHE-$\nu$ detectors. \textbf{Left:} RNO-G (Greenland). \textbf{Right:} ARA (Antarctica).}
+\caption{\footnotesize In-ice UHE-$\nu$ detectors. (Left) RNO-G (Greenland). (Right) ARA (Antarctica).}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.75\textwidth,trim=2cm 9cm 2cm 10cm,clip=true]{example_scan.pdf}
-\caption{\label{fig:scan} Scanning Askaryan field equation parameters to fit NuRadioMC output.}
+\includegraphics[width=0.9\textwidth,trim=2cm 9cm 2cm 10cm,clip=true]{example_scan.pdf}
+\caption{\footnotesize \label{fig:scan} Fitting Askaryan field to NuRadioMC output.
+(Left) reconstruction of $a$ and $\Delta\theta$, mathematical $\vec{E}$-field vs.
+MC $\vec{E}$-field.
+Circle: MC true.
+Cross: reconstruction.}
 \end{figure}
@@
 
+\section{Event Reconstruction}
+
+\begin{frame}[fragile]{Event Reconstruction: calculating $\mathcal{E}_{r * s}(t)$}
+\textbf{\alert{Stages of the calculation:}}
+\begin{itemize}
+\item Calculate $r_a(t)$ and $s_a(t)$ (already shown).
+\item Convolve $r_a(t)$ and $\Re\lbrace s_a(t)\rbrace$ (time domain).
+\item Convolve $r_a(t)$ and $\Im\lbrace s_a(t)\rbrace$ (Fourier domain).
+\item Combine results and take the magnitude, multiply by $(1/2)$.
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]{Event Reconstruction: $r_a(t) * \Re\lbrace s_a(t)\rbrace$}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Result for $r_a(t) * \Re\lbrace s_a(t)\rbrace$}]
+\begin{multline}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
++ R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) \label{eq:Re_result}
+\end{multline}
+\end{tcolorbox}
+\small
+\begin{columns}[T]
+\begin{column}{0.49\textwidth}
+\textbf{Complex poles:}
+\begin{itemize}
+\item $z_1 = f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$
+\item $z_1 = z + jx$
+\end{itemize}
+\end{column}
+\begin{column}{0.49\textwidth}
+\textbf{The Faddeeva function}
+\begin{itemize}
+\item $w(z) = e^{-z^2}\erfc(-jz)$
+\item $w(z) = e^{y^2}\erfc(y)$, $z\to jy$
+\end{itemize}
+\end{column}
+\end{columns} \vspace{0.25cm}
+\normalsize
+\textbf{\alert{Combine real and imaginary parts:}} $\mathcal{E}_{r * s}(t) = \frac{1}{2}|r_a(t) * s_a(t)|$
+\end{frame}
+
+\begin{frame}[fragile]{Event Reconstruction: $r_a(t) * \Im\lbrace s_a(t)\rbrace$}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Result for $r_a(t) * \Im\lbrace s_a(t)\rbrace$}]
+\begin{multline}
+r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
+\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:Im_result}
+\end{multline}
+\end{tcolorbox}
+\small
+\begin{columns}[T]
+\begin{column}{0.49\textwidth}
+\textbf{Complex poles:}
+\begin{itemize}
+\item $z_1 = f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$
+\item $z_1 = z + jx$
+\end{itemize}
+\end{column}
+\begin{column}{0.49\textwidth}
+\textbf{The Goodwin-Staton integral}
+\begin{itemize}
+\item $G(z) = \sqrt{\pi}F(z) - \frac{1}{2}e^{-z^2}\Ei(z^2)$
+\item $\Ei(z)$ is an exponential integral
+\end{itemize}
+\end{column}
+\end{columns} \vspace{0.25cm}
+\normalsize
+\textbf{\alert{Combine real and imaginary parts:}} $\mathcal{E}_{r * s}(t) = \frac{1}{2}|r_a(t) * s_a(t)|$
+\end{frame}
+
+\begin{frame}[fragile]{Event Reconstruction: graphs of $\mathcal{E}_{r * s}(t)$}
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{March12_plot1.pdf}
+\caption{\footnotesize \label{fig:fig1} Black line: $s(t) * r(t)$.
+Gold line: the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
+Purple line: $\mathcal{E}_{r * s}(t)$.}
+\end{figure}
+\end{frame}
+
+\begin{frame}[fragile]{Event Reconstruction: graphs of $\mathcal{E}_{r * s}(t)$}
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{March12_plot2.pdf}
+\caption{\footnotesize \label{fig:fig2} Same is Fig. \ref{fig:fig1}, with different parameters.}
+\end{figure}
+\end{frame}
+
+\begin{frame}[fragile]{Event Reconstruction: (prelim.) reconstructed $a$ vs. $\Delta\theta$}
+\begin{figure}
+\centering
+\includegraphics[width=0.55\textwidth,height=0.5\textwidth,trim=0cm 7cm 3cmcm 5cm,clip=true]{March14_plot1.pdf}
+\includegraphics[width=0.4\textwidth]{scan_grab.png}
+\caption{\footnotesize \label{fig:fig3} (Left) Reconstructed $a$ and $\Delta\theta$, from NuRadioMC. (Right) Fig. \ref{fig:scan} (right), for comparison.}
+\end{figure}
+\end{frame}
+
 \section{Conclusion}
 
-\begin{frame}{Unit 1.1 Outline}
-Unit 1.1 covered:
+\begin{frame}{Outline: from mathematical physics to UHE-$\nu$ observations}
+\begin{columns}[T]
+\begin{column}{0.5\textwidth}
+\textbf{\alert{Background}}
+\begin{itemize}
+\item UHE-$\nu$ flux
+\item The Askaryan effect
+\item RF UHE-$\nu$ detectors
+\end{itemize}
+\textbf{\alert{The Askaryan signal}}
+\begin{itemize}
+\item Analytic radiation model
+\item Signal \textit{envelopes}
+\item Uncertainty principles
+\end{itemize}
+\textbf{\alert{Event reconstruction}}
+\begin{itemize}
+\item Mathematics $\leftrightarrow$ signals
+\item \textbf{NuRadioMC}: MC software
+\item Initial results
+\end{itemize}
+\end{column}
+\begin{column}{0.5\textwidth}
+\begin{figure}
+\centering
+\includegraphics[width=0.9\textwidth]{whittier2.jpeg}
+\caption{\small Whittier College.}
+\end{figure}
+\end{column}
+\end{columns}
+\end{frame}
 
+\section{References}
+
+\begin{frame}{References}
+\footnotesize
+\begin{enumerate}
+\item P. Allison et al., Low-threshold ultrahigh-energy neutrino search with the Askaryan Radio Array, Phys Rev D 105, 122006 (2022).
+\item J. A. Aguilar et al., In situ, broadband measurement of the radio frequency attenuation length at Summit Station, Greenland, J. Glaciol. 68, 1234 (2022).
+\item S. Agarwal et al., Instrument design and performance of the first seven stations of RNO-G, arXiv (2024).
+\item \textbf{J. C. Hanson and R. Hartig}, Complex analysis of Askaryan radiation: A fully analytic model in the time domain, Phys Rev D 105, 123019 (2022).
+\item \textbf{J.
+C.
+Hanson and A.
+L.
+Connolly}, Complex analysis of Askaryan radiation: A fully analytic treatment including the LPM effect and Cascade Form Factor, Astroparticle Physics 91, 75 (2017).
+\item C. Glaser et al., NuRadioMC: simulating the radio emission of neutrinos from interaction to detector, European Phys J C 80, 77 (2020).
+\end{enumerate}
+\end{frame}
+
+\section{Bonus Slides}
+
+\begin{frame}[fragile]{Calculate the signal envelope with SciPy}
+\begin{verbatim}
+import numpy as np
+import scipy.signal.hilbert as hilbert
+env_out = np.abs(hilbert(sig_in))
+\end{verbatim}
+\begin{enumerate}
+\item The hilbert function computes the \textit{analytic signal}
+\item The absolute value of the analytic signal is the envelope
+\end{enumerate}
+\end{frame}
+
+\begin{frame}[fragile]{Calculate the envelope of the convolution of two functions}
+\small
+\begin{verbatim}
+import numpy as np
+import scipy.signal.hilbert as hilbert
+env_out = 0.5*np.abs(np.conv(
+    hilbert(sig_in_1),
+    hilbert(sig_in_2),
+    'same'))
+\end{verbatim}
+This is equivalent to:
+\begin{verbatim}
+import numpy as np
+import scipy.signal.hilbert as hilbert
+env_out = np.abs(hilbert(
+    np.conv(sig_in_1,sig_in_2,'same')))
+\end{verbatim}
 \end{frame}

### 2025-04-15 template.tex
big update op APS presentation
update with conv of s and r in time

@@
 Thus, all units check.
-To check the limits, the parameters $z$ and $z_1$ must be recalled.
+To check the limits, the parameters within $z$ and $z_1$ must be recalled.
 Combining prior definitions, the results are
@@
 \end{figure}
+\item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain.  Starting with the definitions of $s(t)$, $r(t)$, and the convolution integral:
+\begin{align}
+s * r &= \int_0^{\infty} r(\tau) s(t-\tau) d\tau \\
+s * r &= -E_0 \int_0^{\infty} r(\tau) (t-\tau) e^{-\frac{1}{2}\left(\frac{t-\tau}{\sigma_t}\right)^2}d\tau \\
+s * r &= \left(s(t) + E_0 \sigma_t^2 e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dt} \right)I(t,\sigma_t) \label{eq:conv_1} \\
+I(t,\sigma_t) &= \int_0^{\infty} r(\tau) e^{(t\tau)/\sigma_t^2} e^{-\frac{1}{2}\left(\frac{\tau}{\sigma_t}\right)^2}d\tau
+\end{align}
+To compute $I(t,\sigma_t)$, let
+\begin{align}
+z &= \gamma - 2\pi j f_0 \\
+z_0 &= \sqrt{2}\sigma_t z\\
+x &= t/(\sqrt{2} \sigma_t) \\
+y &= \tau/(\sqrt{2} \sigma_t) \\
+r(\tau) &= \Re\left\lbrace R_0 e^{-z\tau}\right\rbrace
+\end{align}
+These substitutions simply $I(t,\sigma_t)$ to
+\begin{equation}
+I(t,\sigma_t) = \sqrt{2} \sigma_t R_0 \Re \left\lbrace\int_0^{\infty} e^{(2y-z_0)x} e^{-x^2} dx \right\rbrace
+\end{equation}
+Let $b = y-z_0/2$, Completing the square in the exponent gives
+\begin{equation}
+I(t,\sigma_t) = \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\left\lbrace e^{b^2} \erfc(-b) \right\rbrace
+\end{equation}
+Let $b = jc$, so that
+\begin{align}
+I(t,\sigma_t) &= \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\lbrace e^{-c^2} \erfc(-jc) \rbrace \\
+I(t,\sigma_t) &= \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\lbrace w(c) \rbrace
+\end{align}
+The Faddeeva function $w(z)$ may be broken into real and imaginary parts using the Voigt functions:
+\begin{equation}
+U(p,q) + jV(p,q) = \sqrt{\frac{\pi}{4q}} w(z)
+\end{equation}
+The relationship between $p$, $q$, and $z$ is $z=(1-jp)/(2\sqrt{q})$.  Using this relationship, we find
+\begin{align}
+p &= \left(\frac{t}{\sigma_t}\right)\left(\frac{\sigma_f}{f_0}\right) - \frac{\gamma}{2\pi f_0} \\
+q &= \frac{1}{2}\left(\frac{\sigma_f}{f_0}\right)^2
+\end{align}
+Thus, the integral $I(t,\sigma_t)$ becomes
+\begin{equation}
+I(t,\sigma_t) = \sigma_t R_0 \left(\frac{\sigma_f}{f_0}\right) U(p,q)
+\end{equation}
+Substituting the result for $I(t,\sigma_t)$ in Eq. \ref{eq:conv_1} gives
+\begin{multline}
+s * r = \\
+ R_0\sigma_t \left(\frac{\sigma_f}{f_0}\right) \left(s(t) + E_0 \sigma_t^2 e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dt} \right) U(p,q) \label{eq:conv_2}
+\end{multline}
+Equation \ref{eq:conv_2} can be simplified in two ways.
+First, note that $\sigma_t \sigma_f = 1/(2\pi)$, so $R_0\sigma_t (\sigma_f/f_0) = R_0/(2\pi f_0)$.
+Second, the derivative of the Voigt function may be simplified using the chain rule:
+\begin{equation}
+\frac{dU(p,q)}{dt} = \frac{dU(p,q)}{dp}\frac{dp}{dt} = \frac{dU(p,q)}{dp} \frac{\sigma_f}{\sigma_t f_0}
+\end{equation}
+Thus, Eq. \ref{eq:conv_2} becomes
+\begin{multline}
+s * r = \\
+\frac{R_0}{2\pi f_0}\left(s(t) + E_0 \sigma_t \left(\frac{\sigma_f}{f_0}\right) e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dp}\right)U(p,q) \label{eq:conv_3}
+\end{multline}
+The envelope of Eq. \ref{eq:conv_3} can be computed numerically, which represents an alternative approach to that represented by Eq. \ref{eq:awesome}.
 \end{itemize}
-\clearpage
 

### 2025-06-06 template.tex
added some proofs to the paper, working on Ers(t) imag part

@@
 The second option involves computing the envelope of the convolution of $r(t)$ with $s(t)$ directly from $s_a(t)$ and $r_a(t)$.
-\item Let $x(t) * y(t)$ represent the convolution of two functions $x(t)$ and $y(t)$.
-Let the envelope of the convolution be $\mathcal{E}_{x * y}(t)$.
-$\mathcal{E}_{x * y}(t)$, $x_a(t)$, and $y_a(t)$ are related by
+\item Let $s(t) * r(t)$ represent the convolution of $s(t)$ and $r(t)$.
+Let the envelope of the convolution be $\mathcal{E}_{s * r}(t)$.
+$\mathcal{E}_{s * r}(t)$, $s_a(t)$, and $r_a(t)$ are related by
 \begin{equation}
-\mathcal{E}_{x * y}(t) = \frac{1}{2}| x_a (t) * y_a(t)| \label{eq:awesome}
+\mathcal{E}_{s * r}(t) = \frac{1}{2}| s_a (t) * r_a(t)| \label{eq:awesome}
 \end{equation}
-We should include the proof here (I have to track it down in my notebooks).
-\item The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are
+The proof of Eq.
+\ref{eq:awesome} is based on two ideas.
+First, the Hilbert transform of a function $s(t)$ is equivalent to convolving it with the ``tempered distribution'' $h(t) = 1/(\pi t)$.
+Second, computing the Hilbert transform twice yields the original function, multiplied by $-1$: $h * h * s = -s$.
+Given the definitions of the analytic signal and the Hilbert transform,
 \begin{align}
-r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
-r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t} \label{eq:ra}
+(s * r)_a (t) &= s * r + j ~ \widehat{s*r} \\
+\mathcal{E}_{s * r}(t) &= | s * r + j s * r * h|
 \end{align}
-The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.
-Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.
-The proof of Eq.
-\ref{eq:ra} is as follows:
+However,
 \begin{align}
-r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
-R(f) &= \frac{R_0}{2\pi j} \left( \frac{f - \frac{j\gamma}{2\pi}}{(f-z_+)(f-z_-)} \right) \\
-z_+ &= f_0 + \frac{j\gamma}{2\pi} \\
-z_- &= -f_0 + \frac{j\gamma}{2\pi} \\
-\widehat{r}(t) &= \mathcal{F}^{-1}\left \lbrace - j \sgn(f) R(f) \right \rbrace \label{eq:rh} \\ 
-\widehat{r}(t) &= \frac{R_0}{2j}\left( e^{2\pi j f_0 t} - e^{-2\pi j f_0 t} \right) e^{-\gamma t} \\
-\widehat{r}(t) &= R_0 \sin(2\pi f_0 t) e^{-\gamma t} \\
-r_a (t) &= R_0 \left(\cos(2\pi f_0 t) + j\sin(2\pi f_0 t)\right) e^{-\gamma t} \\
-r_a (t) &= R_0 e^{2\pi j f_0 t} e^{-\gamma t}
+r_a * s_a &= (r + j \hat{r}) * (s + j \hat{s}) \\
+r_a * s_a &= r * s + j r * \hat{s} + j \hat{r} * s - \hat{r} * \hat{s} \\
+r_a * s_a &= r * s - r * h * s * h + 2 j h * r * s \\
+r_a * s_a &= r * s - h * h * r * s + 2 j h * r * s \\
+r_a * s_a &= 2 r * s + 2 j h * r * s
 \end{align}
-In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.
+Multiplying both sides $1/2$ and taking the magnitude completes the proof:
+\begin{equation}
+\frac{1}{2} |r_a * s_a| = |r * s + j h * r * s| = \mathcal{E}_{s * r}(t) \\
+\end{equation}
+\item The RLC damped oscillator impulse response and corresponding analytic signal are
+\begin{align}
+r(t) &= R_0 e^{-2 \pi \gamma_f t} \cos(2\pi f_0 t) \label{eq:r} \\
+r_a(t) &= R_0 e^{-2 \pi \gamma_f t} e^{2\pi j f_0 t} \label{eq:ra}
+\end{align}
+The parameters $\gamma_f$ and $f_0$ are the \textit{decay constant} that corresponds to the \textit{fall time} of the output signal, and the resonance frequency.
+Note that the envelope of $r(t)$, $|r_a(t)|$, is $R_0 \exp(-2 \pi \gamma_f t)$, as expected.
+To prove Eq.
+\ref{eq:ra}, first compute the Fourier transform of $r(t)$:
+\begin{align}
+R(f) &= \frac{R_0}{4\pi j} \left( \frac{1}{f - z_{+}} + \frac{1}{1- z_{-}} \right) \\
+z_{+} &= f_0 + j \gamma_f \\
+z_{-} &= -f_0 + j \gamma_f
+\end{align}
+Given Eq.
+\ref{eq:sa_2}, the procedure to find $r_a(t)$ is to multiply the \textit{negative} frequency components by 0 and the \textit{positive} frequency components by 2, and take the inverse Fourier transform.
+The inverse Fourier transform may be completed by extension to the complex plane using the upper infinite semi-circle as a contour, and applying Jordan's lemma.
+The residue from the pole at $z_{+}$ drives the final result.
+%\item The behavior of the RLC oscillator can be extended to the charging state, and the decaying state, via the time-reversal of Eq.
+\ref{eq:r}.
+Times with $t\leq 0$ correspond to the charging state, $t=0$ corresponds to peak response, and $t\geq 0$ corresponds to the decaying state.
+For the charging state:
+%\begin{align}
+%r(t) &= R_0 e^{2 \pi \gamma_r t} \cos(2\pi f_0 t) \label{eq:rc} \\
+%r_a(t) &= R_0 e^{2 \pi \gamma_r t} e^{2\pi j f_0 t} \label{eq:rac}
+%\end{align}
+%The resonance frequency remains the same as the decaying state, and $\gamma_r$ corresponds to the \textit{rise time} in the same way that $\gamma_f$ corresponds to the \textit{fall time.}  In general, the rise and fall times do not have to be equal.
 \item The goal is now to apply Eq.
@@
 \begin{equation}
-r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r(\tau) s(t-\tau) d\tau
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r_a(\tau) s(t-\tau) d\tau
 \end{equation}
@@
 \end{equation}
-Subsituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces
+Substituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces
 \begin{multline}
 r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
--j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz}
-\end{multline}
-Finally, the derivative of the Faddeeva function is $dw/dz = 2j/\sqrt{\pi} - 2 zw(z)$.  Substituting for $dw/dz$ gives the final result:
-\begin{multline}
-r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
-+ R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) \label{eq:Re_result}
+-j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} \label{eq:Re_result}
 \end{multline}
@@
 \begin{align}
-\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{-\infty}^{\infty} e^{-zt} e^{-2\pi j ft} dt \\
+\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{0}^{\infty} e^{-z_0 t} e^{-2\pi j ft} dt \\
 \mathcal{F}\left\lbrace r_a(t)\right\rbrace &= \frac{R_0}{z_0+2\pi j f}
@@
 r_a(t) * s_a(t) = \\
-\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) + \\
-R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) + \\
-j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \\
-j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}
+\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) - j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} + \\
+j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}
 \end{multline}
-The units of the convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq.\ref{eq:final} has these units.
+The units of convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq.
+\ref{eq:final} has these units.
 The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.

### 2025-06-06 result.py

@@ -32,40 +32,40 @@ def math_conv(t,E0,R0,sigma_t,f0,gamma):
 def math_env(t,E0,R0,sigma_t,f0,gamma):
 	J = complex(0,1)
 	x = t/(sigma_t*np.sqrt(2))
-	sigma_f = 1.0/(2*np.pi*sigma_t)
-	z0 = complex(f0/np.sqrt(2)/sigma_f,gamma/(2*np.pi*np.sqrt(2)*sigma_f))
-	z1 = complex(np.sqrt(2)*np.pi*sigma_t*f0,sigma_t*gamma/np.sqrt(2)-x)
-	first_term = np.sqrt(np.pi/2)*R0*sigma_t*s(t,E0,sigma_t)*w(z1)
-	first_term += R0*E0*sigma_t*sigma_t*np.exp(-x*x)*(1+J*np.sqrt(np.pi)*z1*w(z1))
-	second_term = E0*sigma_t*sigma_t*z0*np.exp(-z0*z0)*np.sqrt(np.pi)*ra(t,R0,f0,gamma)
-	second_term += np.sqrt(2/np.pi)*G(z0)*R0*sigma_t*s(t,E0,sigma_t)
-	if(t<-sigma_t*gamma or np.isinf(first_term) or np.isinf(second_term) or np.isnan(first_term) or np.isnan(second_term)):
-		return 0.0
+	z = 2*np.pi*J*f0*np.sqrt(2)*sigma_t-2*np.pi*gamma*np.sqrt(2)*sigma_t
+	k = 2*x+z
+	I = np.sqrt(np.pi)/2.0*w(-J*k/2)
+	dIdk = 0.5+0.25*np.sqrt(np.pi)*w(-J*k/2)
+	first_term = -2*R0*E0*sigma_t*sigma_t*(x*np.exp(-x*x)*I-np.exp(-x*x)*dIdk)
+	second_term = 2/np.sqrt(np.pi)*R0*E0*sigma_t*sigma_t*(F(x)-z*F(x))
+	result = first_term+J*second_term
+	if(np.isinf(result) or np.isnan(result)):
+		return 0
 	else:
-		return 0.5*np.abs(first_term+J*second_term)
+		return 0.5*np.abs(result)
 
-f0 = 0.2 #GHz
-gamma = 0.2 #GHz
-sigma_t = 2 #ns
+f0 = 0.5 #GHz
+gamma = 0.9 #GHz
[…]

### 2025-06-19 template.tex
updated calculations for convolution in time domain

@@
 \end{equation}
-\item The RLC damped oscillator impulse response and corresponding analytic signal are
+\item Assume that a signal arrives in an RLC damped oscillator at $t=0$.  For $t\geq 0$, the impulse response and corresponding analytic signal are
 \begin{align}
@@
 \ref{eq:awesome} by convolving $s_a(t)$ with $r_a(t)$.
-The real part of $s_a(t)$ can be convolved with $r_a(t)$ in the time domain.
-As in Eq.
-\ref{eq:sa_4}, real part of $s_a(t)$ is $s(t)$.
-Since $r_a(t<0)=0$, the convolution is written
+The calculation may be split into two parts: $r_a(t) * \Re\lbrace s_a(t) \rbrace$, and $r_a(t) * \Im\lbrace s_a(t) \rbrace$.
+Let $u(t)$ represent the Heaviside step function.
+Starting with $r_a(t) * \Re\lbrace s_a(t) \rbrace$:
+\begin{multline}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ R_0 e^{2\pi j f_0 t} e^{-2\pi\gamma t} u(t) * \left(-E_0 t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2}\right)
+\end{multline}
+Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z = (2\pi j f_0 - 2\pi\gamma)\sqrt{2}\sigma_t$.
+Changing variables while accounting for the relationship between $u(t)$, $x$, and $y$, gives
+\begin{multline}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ -2R_0 E_0 \sigma_t^2 \int_{-\infty}^{x} e^{z(x-y)} y e^{-y^2} dy
+\end{multline}
+Note that the units for the convolution of $r(t)$ and $s(t)$ correspond to $R_0 E_0 \sigma_t^2$.  Let $u = x-y$, so that $du = -dy$. The result is
 \begin{equation}
-r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r_a(\tau) s(t-\tau) d\tau
+r_a(t) * \Re\lbrace s_a(t) \rbrace = 2R_0 E_0 \sigma_t^2\left(\frac{dI(x,z)}{dz}-xI(x,z)\right)
 \end{equation}
-Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z_0 = \sqrt{2}\sigma_t(\gamma-2\pi jf_0)$. The convolution may be organized as follows
+where
 \begin{equation}
-r_a(t) * \Re\lbrace s_a(t) \rbrace = R_0 s(t) I + R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t^2)} \frac{dI}{dt} \label{eq:conv}
+I(x,z) = \int_0^{\infty} e^{zu} e^{-(u-x)^2} du
 \end{equation}
-with
+Let $b = x+\frac{1}{2} z$. Completing the square in the exponent and substituting $k = u-b$ gives
+\begin{multline}
+I(x,z) = e^{-x^2} e^{b^2} \int_{-b}^{\infty} e^{-k^2} dk \\ = \frac{\sqrt{\pi}}{2} e^{-x^2} e^{b^2} \erfc(-b)
+\end{multline}
+Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function}.  The integral becomes
 \begin{equation}
-I(x,z_0) = \sqrt{2}\sigma_t \int_0^{\infty} e^{-y^2 + (2x-z_0)y} dy
+I(x,z) = \frac{\sqrt{\pi}}{2} e^{-x^2} w(q)
 \end{equation}
-Let $b = x-z_0/2$. Completing the square in the exponent produces
+The chain rule is required to find $dI/dz$:
 \begin{equation}
-I(x,z_0) = \sqrt{2}\sigma_t e^{b^2} \int_0^{\infty} e^{-(y-b)^2} dy
+\frac{dI}{dz} = \frac{dI}{dq}\frac{dq}{dz} = -\left(\frac{j}{2}\right)\frac{dI}{dq}
 \end{equation}
-The integral may be cast as a complementary error function by substituting $u=y-b$ and letting $b=jz$:
-\begin{equation}
-I(x,z_0) = \sqrt{\frac{\pi}{2}}\sigma_t e^{-z^2}\erfc(-jz)
-\end{equation}
-Thus, the integral is proportional to the \textit{Faddeeva function}, $w(z)$:
-\begin{equation}
-I(x,z_0) = \sqrt{\frac{\pi}{2}} \sigma_t w(z) \label{eq:fadd}
-\end{equation}
-Substituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces
+The final result is
 \begin{multline}
-r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
--j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} \label{eq:Re_result}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ -\sqrt{\pi} R_0 E_0 \sigma_t^2 \left(x e^{-x^2} w(q) + \left(\frac{j}{2}\right) e^{-x^2} \frac{dw(q)}{dq} \right) \label{eq:Re_result}
 \end{multline}
-\item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq.
-\ref{eq:sa_4} contains $dD(x)/dx$, the derivative of the Dawson function.
-To complete the convolution, the inverse Fourier transform of the product of the Fourier transforms of $r_a(t)$ and $\Im\lbrace s_a(t)\rbrace$ is calculated.
-To complete this step, the Fourier transform of $dD(x)/dx$ is needed:
-\begin{align}
-x &= t/(\sqrt{2}\sigma_t) \\
-f' &= \sqrt{2} \sigma_t f \\
-\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \int_{-\infty}^{\infty} \frac{dD(x)}{dx}e^{-2\pi jft} dt \\
-\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \sqrt{2}\sigma_t(2\pi jf') \int_{-\infty}^{\infty} D(x) e^{-2\pi jf'x} dx \\
-\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= 2\pi^2 \sigma_t^2 f e^{-\frac{1}{2}(f/\sigma_f)^2} \sgn(f)
-\end{align}
-Let $z_0 = (\gamma - 2\pi jf_0)$, so that the Fourier transform of $r_a$ is 
-\begin{align}
-\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{0}^{\infty} e^{-z_0 t} e^{-2\pi j ft} dt \\
-\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= \frac{R_0}{z_0+2\pi j f}
-\end{align}
-Let $z_1 = f_0 + j\gamma/(2\pi)$. Multiplying the Fourier transforms, and simplifying, yields
+\item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$,
 \begin{multline}
-\mathcal{F}\left\lbrace r_a(t) * \Im\left\lbrace s_a(t)\right\rbrace \right\rbrace = \\ -j \sqrt{2\pi} R_0 E_0 \sigma^3 \frac{f\sgn(f) e^{-\frac{1}{2}(f/\sigma_f)^2}}{f-z_1}
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \left(R_0 e^{2\pi j f_0 t} e^{-2\pi \gamma t} u(t)\right) * \left(\frac{2 E_0 \sigma_t^2}{\sqrt{\pi}}\frac{dD(t/\sqrt{2}\sigma_t)}{dt} \right)
 \end{multline}
-The inverse Fourier transform now gives $r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace$:
+Note that $f'(t) * g(t) = f(t) * g'(t) = (f(t) * g(t))'$.  Thus,
 \begin{multline}
-r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--j\sqrt{2\pi} R_0 E_0 \sigma_t^3 \int_{-\infty}^{\infty} \frac{f\sgn(f)e^{-\frac{1}{2}(f/\sigma_f)^2}e^{2\pi jft}}{f-z_1} df
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dt}\left(e^{2\pi j f_0 t}e^{-2\pi\gamma t} u(t) * D(t/\sqrt{2}\sigma_t) \right)
 \end{multline}
-Let $y = f/(\sqrt{2}\sigma_f)$, $x=t/(\sqrt{2}\sigma_t)$, $\sgn(f) = \sgn(y)$, and $z_1 \to f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.
-The inverse Fourier transform can be organized as:
+Accounting for the step function in the convolution gives
 \begin{multline}
-r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--\frac{R_0E_0\sigma_t^3}{\sqrt{2\pi}}\frac{d}{dt}\int_{-\infty}^{\infty} \frac{\sgn(y) e^{-y^2+2jxy}}{y-z_1} dy
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dt} \int_{-\infty}^{t} e^{(2\pi j f_0 - 2\pi\gamma)(t-\tau)}D(\tau/\sqrt{2}\sigma_t)d\tau
 \end{multline}
-Completing the square in the exponent, factoring a unit of $j$ from the exponent, and changing the derivative from $d/dt$ to $d/dx$ gives
+Adopting the earlier definitions of $x$, $y$, and $z$ gives
 \begin{multline}
-r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{-\infty}^{\infty} \frac{\sgn(y) e^{(x+jy)^2}}{y-z_1}dy
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \int_{-\infty}^{x} e^{z(x-y)} D(y) dy
 \end{multline}
-Let $z = x+jy$, with $y = \Im(z)$.
-In this substitution, $x$ is treated as a constant, so $dz = jy$.
-Let $z_2 = x+j z_1$, while $z_1 = f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.
-The result is
+Using the fundamental theorem of calculus, 
 \begin{multline}
-r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{x-j\infty}^{x+j\infty} \frac{\sgn(\Im(z)) e^{z^2}}{y-z_2}dz \label{eq:cont_int}
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + z\int_{-\infty}^{x} e^{z(x-y)} D(y) dy \right)
 \end{multline}
-The integral may be finished by extending $z$ to the complex plane and using contour integration.
-The location of the pole is in the first quadrant, unless $t = (\gamma \sigma_t)\sigma_t$.
-In that case, $\Re(z_2)=0$, and the pole is located on the imaginary axis.
-For typical values of $\sigma_t$ and $\gamma$, $t\approx 0.1$ ns.
-Since $r(t)=0$ if $t<0$, the location of $z_2$ is usually in the first quadrant.
-Let the line integrals of the rectangular contour be: $I_1$, $(x,-jR) \to (x,jR)$, $I_2$, $(x,jR) \to (0,jR)$, $I_3$, $(0,jR) \to (0,-jR)$, and $I_4$, $(0,-jR) \to (x,-jR)$.
-$I_2$ and $I_4$ are both proportional to $\exp(-R^2)$, so $I_2 \to 0$ and $I_4 \to 0$ when $R \to \infty$.
-$I_1$ is the integral in Eq.
-\ref{eq:cont_int}.
-Let $w = -y$, so that $I_3$ is
-\begin{equation}
-I_3 = -\int_0^{R} \frac{e^{-y^2}}{y-z_1} dy + \int_0^{R} \frac{e^{-w^2}}{w+z_1} dw
-\end{equation}
-Integrals of the type in $I_3$ are known as \textit{Goodwin-Staton} functions, and are related to the other error functions.
-The Goodwin-Staton function, $G(z_1)$, is odd, so $-G(-z_1) = G(z_1)$.
-The result for $I_3$ is
-\begin{equation}
-I_3 = -G(-z_1) + G(z_1) = 2G(z_1)
-\end{equation}
-The residue of the enclosed contour $I_C = I_1+I_2+I_3+I_4$ is $\exp(z_2^2)$.  With $I_2$, $I_3$, and $I_4$ completed, the solution for $I_1$ is
-\begin{equation}
-I_1 = 2\pi j e^{z_2^2} - 2G(z_1)
-\end{equation}
-Inserting this result into Eq. \ref{eq:cont_int}, and simplifying, gives
+Let $u = x-y$, so that $du = -dy$ and note that $D(x)$ is an odd function.  The substitution gives
 \begin{multline}
-r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
--\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_1 - z_1^2} - 2G(z_1) e^{-x^2} \right)
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) - z\int_{0}^{\infty} e^{zu} D(u-x) du \right)
 \end{multline}
-Notice that $2\pi j x z_1 = 2\pi j f_0 t - \gamma t$.  Evaluating the derivative and simplifying gives the final result:
-\begin{multline}
-r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:Im_result}
-\end{multline}
+The integral is the Laplace transform of the shifted Dawson function, evaluated at $-z$.
 \item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:

### 2025-06-19 result.py

@@ -1,20 +1,17 @@
 import numpy as np
 from scipy.signal import convolve,hilbert
-from scipy.special import dawsn as F
-from scipy.special import expi as Ei
+from scipy.special import dawsn as D
 from scipy.special import wofz as w
+from scipy.special import erfc
 import matplotlib.pyplot as plt
 
-def G(z0):
-	z0 = np.real(z0)
-	return np.sqrt(np.pi)*F(z0)-0.5*np.exp(-z0*z0)*Ei(z0*z0)
-def s(t,E0,sigma_t):
-	return -E0*t*np.exp(-0.5*(t/sigma_t)*(t/sigma_t))
-def r(t,R0,f0,gamma):
-	return R0*np.cos(2*np.pi*f0*t)*np.exp(-gamma*t)
-def ra(t,R0,f0,gamma):
+def dwdq(q):
 	J = complex(0,1)
-	return R0*np.exp(2*np.pi*J*f0*t)*np.exp(-gamma*t)
+	return 2*J/np.sqrt(np.pi)-2*q*w(q)
+
+def s(t,E0,sigma_t):
+	return -E0*t*np.exp(-0.5*t*t/sigma_t/sigma_t)
+
 def math_conv(t,E0,R0,sigma_t,f0,gamma):
 	J = complex(0,1)
 	sigma_f = 1.0/(2*np.pi*sigma_t)
@@ -29,32 +26,37 @@ def math_conv(t,E0,R0,sigma_t,f0,gamma):
 		return 0.0
 	else:
 		return first_term+second_term
+
 def math_env(t,E0,R0,sigma_t,f0,gamma):
+	units = R0*E0*sigma_t*sigma_t
 	J = complex(0,1)
 	x = t/(sigma_t*np.sqrt(2))
-	z = 2*np.pi*J*f0*np.sqrt(2)*sigma_t-2*np.pi*gamma*np.sqrt(2)*sigma_t
-	k = 2*x+z
-	I = np.sqrt(np.pi)/2.0*w(-J*k/2)
-	dIdk = 0.5+0.25*np.sqrt(np.pi)*w(-J*k/2)
-	first_term = -2*R0*E0*sigma_t*sigma_t*(x*np.exp(-x*x)*I-np.exp(-x*x)*dIdk)
-	second_term = 2/np.sqrt(np.pi)*R0*E0*sigma_t*sigma_t*(F(x)-z*F(x))
-	result = first_term+J*second_term
[…]

### 2025-06-20 template.tex
just trudging along not getting the Laplacian of the Dawson

@@
 \end{multline}
-Let $u = x-y$, so that $du = -dy$ and note that $D(x)$ is an odd function.  The substitution gives
+Let $u = x-y$, $z=-k$, and note that $D(x)$ is an odd function.  These substitutions give
 \begin{multline}
-r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) - z\int_{0}^{\infty} e^{zu} D(u-x) du \right)
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\int_{0}^{\infty} e^{-ku} D(u-x) du \right)
 \end{multline}
-The integral is the Laplace transform of the shifted Dawson function, evaluated at $-z$.
+The integral is the Laplace transform of the shifted Dawson function, with respect to $k$.  Let $v = u-x$, so that
+\begin{multline}
+k\int_{0}^{\infty} e^{-ku} D(u-x) du = \\ k e^{-kx} \left( \mathcal{L}\lbrace D(v) \rbrace_k - \int_0^{x} e^{kv} D(v) dv\right)
+\end{multline}
 \item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:

### 2025-06-20 result.py

@@ -2,7 +2,7 @@ import numpy as np
 from scipy.signal import convolve,hilbert
 from scipy.special import dawsn as D
 from scipy.special import wofz as w
-from scipy.special import erfc
+from scipy.special import erf
 import matplotlib.pyplot as plt
 
 def dwdq(q):
@@ -11,6 +11,12 @@ def dwdq(q):
 
 def s(t,E0,sigma_t):
 	return -E0*t*np.exp(-0.5*t*t/sigma_t/sigma_t)
+
+def r(t,R0,f0,gamma):
+	if(t>=0):
+		return R0*np.cos(2*np.pi*f0*t)*np.exp(-2*np.pi*gamma*t)
+	else:
+		return 0
 
 def math_conv(t,E0,R0,sigma_t,f0,gamma):
 	J = complex(0,1)
@@ -34,21 +40,21 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 	z = (2*np.pi*J*f0-2*np.pi*gamma)*np.sqrt(2)*sigma_t
 	q = -J*(x+z/2)
 	first_term = -np.sqrt(np.pi)*units*(x*np.exp(-x*x)*w(q)+0.5*J*np.exp(-x*x)*dwdq(q))
-	second_term = 2/np.sqrt(np.pi)*units
-	result = first_term+J*0
+	second_term = 0
+	result = first_term+J*second_term
 	if(np.isinf(result) or np.isnan(result)):
 		return 0
 	else:
 		return 0.5*np.abs(result)
 
-f0 = 0.2 #GHz
-gamma = 0.15 #GHz
-sigma_t = 2 #ns
+f0 = 0.33 #GHz
+gamma = 0.04 #GHz
+sigma_t = 1 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
-T_min = -10 #ns
-T_max = 40 #ns
+T_min = -50 #ns
+T_max = 50 #ns
 t = np.arange(T_min,T_max,dt)
 n = len(t)
 
@@ -56,18 +62,20 @@ J = complex(0,1)
 x = t/(sigma_t*np.sqrt(2))
 z = (2*np.pi*J*f0-2*np.pi*gamma)*np.sqrt(2)*sigma_t
 q = -J*(x+z/2)
+a=4
 
 result1 = np.zeros(t.shape,dtype=complex)
 result2 = np.zeros(t.shape,dtype=complex)
 for i in range(n):
[…]

### 2025-06-26 template.tex
updating math_env function, paper with inc gamma func for ra Im(sa)

@@
 \end{multline}
-The integral is the Laplace transform of the shifted Dawson function, with respect to $k$.  Let $v = u-x$, so that
-\begin{multline}
-k\int_{0}^{\infty} e^{-ku} D(u-x) du = \\ k e^{-kx} \left( \mathcal{L}\lbrace D(v) \rbrace_k - \int_0^{x} e^{kv} D(v) dv\right)
-\end{multline}
+The remaining integral may be expressed in terms of the Laplace transform of the shifted Dawson function.
+Obtaining a closed form, however, is difficult.
+A more practical approach is to let the upper limit be $T \gg x$, and expand $D(u-x)$ in its Taylor series:
+\begin{align}
+I(x,k) &= k\int_{0}^{T} e^{-ku} D(u-x) du \\
+D(u-x) &= \sum_{n=0}^{\infty} \frac{(-1)^n 2^n(u-x)^{2n+1}}{(2n+1)!!}
+\end{align}
+Let $t = u-x$, and $a_n = (-1)^n 2^n / (2n+1)!!$.  Substituting the power series for the Dawson function gives:
+\begin{equation}
+I(x,k) = k e^{-k x} \sum_{n=0}^{\infty} a_n \int_{-x}^{T-x} e^{-kt} t^{2n+1} dt
+\end{equation}
+Since $T\gg x$, the upper limit $T-x\gg 0$, and the lower limit $-x <0$.
+The exponential $\exp(-kx)$ is decaying in the right half-plane (since $\Re(k)>0$).
+Hence, for moderate x,the contribution of the integral over $t>0$, and
+\begin{equation}
+\int_{-x}^{T-x} e^{-kt} t^{2n+1} dt \approx \int_{0}^{T-x} e^{-kt} t^{2n+1} dt
+\end{equation}
+The right-hand side is known as a \textit{lower incomplete gamma-function, $\gamma(2n+2,k(T-x))$.} Thus, the solution is 
+\begin{equation}
+I(x,k) = e^{-k x} \sum_{n=0}^{\infty} a_n \frac{\gamma(2n+2,k(T-x))}{k^{2n+1}}
+\end{equation}
+Requiring that $T$ be much larger than $x$, but finite, is similar to the \textit{symmetric approximation} made in the derivation of $s(t)$ \cite{PhysRevD.105.123019}.
 \item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:

### 2025-06-26 result.py

@@ -2,7 +2,8 @@ import numpy as np
 from scipy.signal import convolve,hilbert
 from scipy.special import dawsn as D
 from scipy.special import wofz as w
-from scipy.special import erf
+from scipy.special import gamma as gamma_f
+from scipy.special import gammainc,factorial2
 import matplotlib.pyplot as plt
 
 def dwdq(q):
@@ -40,7 +41,13 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 	z = (2*np.pi*J*f0-2*np.pi*gamma)*np.sqrt(2)*sigma_t
 	q = -J*(x+z/2)
 	first_term = -np.sqrt(np.pi)*units*(x*np.exp(-x*x)*w(q)+0.5*J*np.exp(-x*x)*dwdq(q))
+	T = 10*x
+	N = 10
+	k = -z
 	second_term = 0
+	for n in range(N):
+		an = np.power(-1,n)*np.power(2,n)/factorial2(2*n+1)
+		second_term+=an*gamma_f(2*n+2)*gammainc(2*n+2,k*(T-x))*np.exp(-k*x)/np.power(k,2*n+2)
 	result = first_term+J*second_term
 	if(np.isinf(result) or np.isnan(result)):
 		return 0
@@ -48,8 +55,8 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 		return 0.5*np.abs(result)
 
 f0 = 0.33 #GHz
-gamma = 0.04 #GHz
-sigma_t = 1 #ns
+gamma = 0.06 #GHz
+sigma_t = 0.5 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
@@ -69,11 +76,9 @@ result2 = np.zeros(t.shape,dtype=complex)
 for i in range(n):
 	u = t[i]
 	result1[i] = math_conv(u,E0,R0,sigma_t,f0,2*np.pi*gamma)
-	u = u+0.5
-	u*=0.2
-	result2[i] = 2*np.exp(-0.5*u*u)*(0.5*(1+erf(a*u/np.sqrt(2))))/1.6
+	result2[i] = math_env(u,E0,R0,sigma_t,f0,gamma)
 graph1 = np.abs(hilbert(np.real(result1)))*1000
-graph2 = np.real(result2)*1000
+graph2 = np.real(result2)*1000*2
 plt.plot(t,graph1,'-',label="env of math conv")
 plt.plot(t,graph2,'-',label="math env")
 plt.xlabel("Time [ns]")

### 2025-06-27 template.tex
introduced numerical integration for Laplace transform and BOOM

--- 2025-06-20 template.tex
@@
 \end{multline}
-Using the fundamental theorem of calculus, 
+Using the fundamental theorem of calculus, and the limiting cases of $D(x)$, 
 \begin{multline}
@@
 \end{multline}
-The integral is the Laplace transform of the shifted Dawson function, with respect to $k$.  Let $v = u-x$, so that
-\begin{multline}
-k\int_{0}^{\infty} e^{-ku} D(u-x) du = \\ k e^{-kx} \left( \mathcal{L}\lbrace D(v) \rbrace_k - \int_0^{x} e^{kv} D(v) dv\right)
-\end{multline}
+The remaining integral is the Laplace transform of the shifted Dawson function, $\mathcal{L}\lbrace D(u-x)\rbrace_k$.  The final result is
+\begin{equation}
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right)
+\end{equation}
+%A more practical approach is to let the upper limit be $T \gg x$, and expand $D(u-x)$ in its Taylor series:
+%\begin{align}
+%I(x,k) &= k\int_{0}^{T} e^{-ku} D(u-x) du \\
+%D(u-x) &= \sum_{n=0}^{\infty} \frac{(-1)^n 2^n(u-x)^{2n+1}}{(2n+1)!!}
+%\end{align}
+%Let $t = u-x$, and $a_n = (-1)^n 2^n / (2n+1)!!$.  Substituting the power series for the Dawson function gives:
+%\begin{equation}
+%I(x,k) = k e^{-k x} \sum_{n=0}^{\infty} a_n \int_{-x}^{T-x} e^{-kt} t^{2n+1} dt
+%\end{equation}
+%Since $T\gg x$, the upper limit $T-x\gg 0$, and the lower limit $-x <0$. The exponential $\exp(-kx)$ is decaying in the right half-plane (since $\Re(k)>0$).  The integral may be approximated
+%\begin{equation}
+%\int_{-x}^{T-x} e^{-kt} t^{2n+1} dt \approx \int_{0}^{T-x} e^{-kt} t^{2n+1} dt
+%\end{equation}
+%The right-hand side is known as a \textit{lower incomplete gamma-function, $\gamma(2n+2,k(T-x))$.} Thus, the solution is 
+%\begin{equation}
+%I(x,k) = e^{-k x} \sum_{n=0}^{\infty} a_n \frac{\gamma(2n+2,k(T-x))}{k^{2n+1}}
+%\end{equation}
+%Requiring that $T$ be much larger than $x$, but finite, is similar to the \textit{symmetric approximation} made in the derivation of $s(t)$ \cite{PhysRevD.105.123019}.
+
 \item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:

### 2025-06-27 result.py

@@ -2,9 +2,16 @@ import numpy as np
 from scipy.signal import convolve,hilbert
 from scipy.special import dawsn as D
 from scipy.special import wofz as w
-from scipy.special import gamma as gamma_f
-from scipy.special import gammainc,factorial2
+from scipy.special import factorial2
+from mpmath import gamma as gammaFunction
+from mpmath import gammainc
 import matplotlib.pyplot as plt
+from scipy.integrate import quad
+
+def shifted_laplace_transform(f,s,t0,t_max=1000):
+    real_integral = quad(lambda t: np.exp(-s.real*t)*np.cos(s.imag*t)*f(t-t0),0,t_max)[0]
+    imag_integral = quad(lambda t: np.exp(-s.real*t)*np.sin(s.imag*t)*f(t-t0),0,t_max)[0]
+    return complex(real_integral,-imag_integral)
 
 def dwdq(q):
 	J = complex(0,1)
@@ -39,37 +46,26 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 	J = complex(0,1)
 	x = t/(sigma_t*np.sqrt(2))
 	z = (2*np.pi*J*f0-2*np.pi*gamma)*np.sqrt(2)*sigma_t
+	k=-z
 	q = -J*(x+z/2)
 	first_term = -np.sqrt(np.pi)*units*(x*np.exp(-x*x)*w(q)+0.5*J*np.exp(-x*x)*dwdq(q))
-	T = 10*x
-	N = 10
-	k = -z
-	second_term = 0
-	for n in range(N):
-		an = np.power(-1,n)*np.power(2,n)/factorial2(2*n+1)
-		second_term+=an*gamma_f(2*n+2)*gammainc(2*n+2,k*(T-x))*np.exp(-k*x)/np.power(k,2*n+2)
-	result = first_term+J*second_term
-	if(np.isinf(result) or np.isnan(result)):
-		return 0
+	second_term = 2/np.sqrt(np.pi)*units*(D(x) + k*shifted_laplace_transform(D,k,x))
+	if(np.isinf(first_term) or np.isinf(second_term) or np.isnan(first_term) or np.isnan(second_term)):
+		return 0.0
 	else:
-		return 0.5*np.abs(result)
+		result = first_term+J*second_term
[…]

### 2025-07-02 template.tex
pushing hard to the finish line (of theory bit)

--- 2025-06-20 template.tex
@@
 \usepackage{mathtools}
-\usepackage{empheq}
+%\usepackage{empheq}
 \usepackage{verbatim}
@@
 The residue from the pole at $z_{+}$ drives the final result.
-%\item The behavior of the RLC oscillator can be extended to the charging state, and the decaying state, via the time-reversal of Eq.
-\ref{eq:r}.
-Times with $t\leq 0$ correspond to the charging state, $t=0$ corresponds to peak response, and $t\geq 0$ corresponds to the decaying state.
-For the charging state:
-%\begin{align}
-%r(t) &= R_0 e^{2 \pi \gamma_r t} \cos(2\pi f_0 t) \label{eq:rc} \\
-%r_a(t) &= R_0 e^{2 \pi \gamma_r t} e^{2\pi j f_0 t} \label{eq:rac}
-%\end{align}
-%The resonance frequency remains the same as the decaying state, and $\gamma_r$ corresponds to the \textit{rise time} in the same way that $\gamma_f$ corresponds to the \textit{fall time.}  In general, the rise and fall times do not have to be equal.
 \item The goal is now to apply Eq.
@@
 \end{multline}
-The integral is the Laplace transform of the shifted Dawson function, with respect to $k$.  Let $v = u-x$, so that
+The remaining integral is the Laplace transform of the shifted Dawson function, $\mathcal{L}\lbrace D(u-x)\rbrace_k$.  The final result is
+\begin{equation}
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right) \label{eq:Im_result}
+\end{equation}
+Though a closed analytic form for $\mathcal{L}\lbrace D(u-x)\rbrace_k$ is elusive, finishing this calculation through numerical integration is straightforward.
+\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$, since
+\begin{equation}
+r_a(t) * s_a(t) = r_a(t) * \Re\lbrace s_a(t)\rbrace + j r_a(t) * \Im\lbrace s_a(t)\rbrace
+\end{equation}
+which yields
 \begin{multline}
-k\int_{0}^{\infty} e^{-ku} D(u-x) du = \\ k e^{-kx} \left( \mathcal{L}\lbrace D(v) \rbrace_k - \int_0^{x} e^{kv} D(v) dv\right)
+r_a(t) * s_a(t) = \\ -\sqrt{\pi} R_0 E_0 \sigma_t^2 \left(x e^{-x^2} w(q) + \left(\frac{j}{2}\right) e^{-x^2} \frac{dw(q)}{dq} \right) + \\ \frac{2j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right) \label{eq:final}
 \end{multline}
-\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:
-\begin{multline}
-r_a(t) * s_a(t) = \\
-\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) - j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} + \\
-j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}
-\end{multline}
-The units of convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq.
-\ref{eq:final} has these units.
-The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.
-The units of the second term are $R_0 E_0\sigma_t^2$.
-The third term has units of $E_0\sigma_t^2 r_a(t)$, and $r_a(t)$ has units of $R_0$, so the unit product is $R_0 E_0\sigma_t^2$.
-The fourth term has units of $R_0 \sigma_t s(t)$, like the first term.
-Thus, all units check.
-To check the limits, the parameters within $z$ and $z_1$ must be recalled.
-Combining prior definitions, the results are
-\begin{align}
-z &= \sqrt{2}\sigma_t \pi f_0 + j\left(\frac{\sigma_t\gamma}{\sqrt{2}} - x\right) \\
-z_1 &= f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)
-\end{align}
-Recall that $\sigma_t = 1/(2\pi \sigma_f)$, and $x=t/(\sqrt{2}\sigma_t)$.  Substituting this into the definition of $z$ reveals that
+The units of convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq. \ref{eq:final} has these units.  Remember that the relationship between $q$ and $x$ is given by
 \begin{equation}
-z_1 = z + jx
+q = -jb = -j\left(x + \frac{z}{2}\right) \\
 \end{equation}
-Thus, when $t=0$, the two poles are equal, since $t=0$ means $x=0$.  Taking the magnitude of Eq. \ref{eq:final}, and multiplying by $1/2$, gives the final result:
+Taking the magnitude of Eq. \ref{eq:final}, and multiplying by $1/2$, yields the \textbf{Hilbert envelope of the convolution of $s(t)$ with $r(t)$:}
 \begin{equation}
@@
 \end{figure}
-\item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain.  Starting with the definitions of $s(t)$, $r(t)$, and the convolution integral:
+\clearpage
+\item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
+\begin{equation}
+s * r = \int_{-\infty}^{\infty} s(t-\tau) r(\tau) d\tau 
+\end{equation}
+Inserting the definitions of $s(t)$ and $r(t)$,
+\begin{multline}
+s * r = \\ -E_0 R_0 \int_{-\infty}^{\infty} (t-\tau) e^{-\frac{1}{2}\left(\frac{t-\tau}{\sigma_t}\right)^2} \Re\left\lbrace e^{2\pi j f_0 \tau} e^{-2\pi\gamma \tau} \right\rbrace u(\tau) d\tau
+\end{multline}
+Using the previous definitions of $x$, $y$, and $z$ gives
+\begin{equation}
+s * r = -2R_0 E_0 \sigma_t^2 \int_{0}^{\infty} (x-y) e^{-(x-y)^2} \Re\left\lbrace e^{zy} \right\rbrace dy
+\end{equation}
+Note that the $\Re\lbrace \rbrace$ operator can encompass the whole integral, since $s(t)$ is real.  Splitting the integral and employing differentiation under the equals sign yields
+\begin{multline}
+s * r = \\ -2R_0 E_0 \sigma_t^2 \Re\left\lbrace xe^{-x^2}I(x,z) - \frac{1}{2}e^{-x^2} \frac{dI(x,z)}{dx} \right\rbrace \label{eq:conv_sr}
+\end{multline}
+with
+\begin{equation}
+I(x,z) = \int_0^{\infty} e^{-y^2 + (2x + z)y}dy
+\end{equation}
+Let $b=x+\frac{1}{2}z$, and $a = -jb$.  Completing the square in the exponent of $I(x,z)$ gives
+\begin{equation}
+I(x,z) = \frac{\sqrt{\pi}}{2} w(a)
+\end{equation}
+where $w(a)$ is the Faddeeva function.
+Note that the Faddeeva function is \textit{entire}, meaning the $\Re\lbrace \rbrace$ operator and differentiation commute.
+Inserting this result into Eq.
+\ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives
+\begin{multline}
+s * r = \\ -\sqrt{\pi}R_0 E_0 \sigma_t^2 \left(xe^{-x^2} \Re\left\lbrace w(a)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(a)\rbrace}{dx} \right)
+\end{multline}
+The Faddeeva function may be split into real and imaginary parts via the \textit{Voigt functions}:
 \begin{align}
-s * r &= \int_0^{\infty} r(\tau) s(t-\tau) d\tau \\
-s * r &= -E_0 \int_0^{\infty} r(\tau) (t-\tau) e^{-\frac{1}{2}\left(\frac{t-\tau}{\sigma_t}\right)^2}d\tau \\
-s * r &= \left(s(t) + E_0 \sigma_t^2 e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dt} \right)I(t,\sigma_t) \label{eq:conv_1} \\
-I(t,\sigma_t) &= \int_0^{\infty} r(\tau) e^{(t\tau)/\sigma_t^2} e^{-\frac{1}{2}\left(\frac{\tau}{\sigma_t}\right)^2}d\tau
+w(a) &= U(p,q) + jV(p,q) \\
+p &= 
 \end{align}
-To compute $I(t,\sigma_t)$, let
-\begin{align}
-z &= \gamma - 2\pi j f_0 \\
-z_0 &= \sqrt{2}\sigma_t z\\
-x &= t/(\sqrt{2} \sigma_t) \\
-y &= \tau/(\sqrt{2} \sigma_t) \\
-r(\tau) &= \Re\left\lbrace R_0 e^{-z\tau}\right\rbrace
-\end{align}
-These substitutions simply $I(t,\sigma_t)$ to
-\begin{equation}
-I(t,\sigma_t) = \sqrt{2} \sigma_t R_0 \Re \left\lbrace\int_0^{\infty} e^{(2y-z_0)x} e^{-x^2} dx \right\rbrace
-\end{equation}
-Let $b = y-z_0/2$, Completing the square in the exponent gives
-\begin{equation}
-I(t,\sigma_t) = \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\left\lbrace e^{b^2} \erfc(-b) \right\rbrace
-\end{equation}
-Let $b = jc$, so that
-\begin{align}
-I(t,\sigma_t) &= \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\lbrace e^{-c^2} \erfc(-jc) \rbrace \\
-I(t,\sigma_t) &= \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\lbrace w(c) \rbrace
-\end{align}
-The Faddeeva function $w(z)$ may be broken into real and imaginary parts using the Voigt functions:
-\begin{equation}
-U(p,q) + jV(p,q) = \sqrt{\frac{\pi}{4q}} w(z)
-\end{equation}
-The relationship between $p$, $q$, and $z$ is $z=(1-jp)/(2\sqrt{q})$.  Using this relationship, we find
-\begin{align}
-p &= \left(\frac{t}{\sigma_t}\right)\left(\frac{\sigma_f}{f_0}\right) - \frac{\gamma}{2\pi f_0} \\
-q &= \frac{1}{2}\left(\frac{\sigma_f}{f_0}\right)^2
-\end{align}
-Thus, the integral $I(t,\sigma_t)$ becomes
-\begin{equation}
-I(t,\sigma_t) = \sigma_t R_0 \left(\frac{\sigma_f}{f_0}\right) U(p,q)
-\end{equation}
-Substituting the result for $I(t,\sigma_t)$ in Eq. \ref{eq:conv_1} gives
-\begin{multline}
-s * r = \\
- R_0\sigma_t \left(\frac{\sigma_f}{f_0}\right) \left(s(t) + E_0 \sigma_t^2 e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dt} \right) U(p,q) \label{eq:conv_2}
-\end{multline}
-Equation \ref{eq:conv_2} can be simplified in two ways.
-First, note that $\sigma_t \sigma_f = 1/(2\pi)$, so $R_0\sigma_t (\sigma_f/f_0) = R_0/(2\pi f_0)$.
-Second, the derivative of the Voigt function may be simplified using the chain rule:
-\begin{equation}
-\frac{dU(p,q)}{dt} = \frac{dU(p,q)}{dp}\frac{dp}{dt} = \frac{dU(p,q)}{dp} \frac{\sigma_f}{\sigma_t f_0}
-\end{equation}
-Thus, Eq. \ref{eq:conv_2} becomes
-\begin{multline}
-s * r = \\
-\frac{R_0}{2\pi f_0}\left(s(t) + E_0 \sigma_t \left(\frac{\sigma_f}{f_0}\right) e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dp}\right)U(p,q) \label{eq:conv_3}
-\end{multline}
-The envelope of Eq. \ref{eq:conv_3} can be computed numerically, which represents an alternative approach to that represented by Eq. \ref{eq:awesome}.
 \end{itemize}

### 2025-07-02 result.py

@@ -57,13 +57,13 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 	return 0.5*np.abs(result)
 
 f0 = 0.25 #GHz
-gamma = 0.075 #GHz
+gamma = 0.05 #GHz
 sigma_t = 0.5 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
 T_min = -20 #ns
-T_max = 50 #ns
+T_max = 100 #ns
 t = np.arange(T_min,T_max,dt)
 n = len(t)
 
@@ -76,7 +76,14 @@ for i in range(n):
 graph1 = np.abs(hilbert(np.real(result1)))*1000
 graph2 = np.real(result2)*1000
 graph3 = np.real(result1)*1000
-plt.plot(t,graph1,'-',label="env of math conv")
+
+with open("results_June27th.dat","w") as file:
+	for i in range(n):
+		writeString = str(t[i])+" "+str(graph3[i])+" "+str(graph1[i])+" "+str(graph2[i])+"\n"
+		file.write(writeString)
+file.close()
+
+'''plt.plot(t,graph1,'-',label="env of math conv")
 plt.plot(t,graph2,'-',label="math env")
 plt.plot(t,graph3,'-',label="math conv")
 plt.xlabel("Time [ns]")
@@ -84,4 +91,4 @@ plt.ylabel("Amplitude [mV]")
 plt.xticks()
 plt.yticks()
 plt.legend()
-plt.show()
+plt.show()'''

### 2025-07-03 result.py
Add files via upload

@@ -2,9 +2,6 @@ import numpy as np
 from scipy.signal import convolve,hilbert
 from scipy.special import dawsn as D
 from scipy.special import wofz as w
-from scipy.special import factorial2
-from mpmath import gamma as gammaFunction
-from mpmath import gammainc
 import matplotlib.pyplot as plt
 from scipy.integrate import quad
 
@@ -25,21 +22,20 @@ def r(t,R0,f0,gamma):
 		return R0*np.cos(2*np.pi*f0*t)*np.exp(-2*np.pi*gamma*t)
 	else:
 		return 0
-
+        
 def math_conv(t,E0,R0,sigma_t,f0,gamma):
-	J = complex(0,1)
-	sigma_f = 1.0/(2*np.pi*sigma_t)
-	p = (t/sigma_t)*(sigma_f/f0) - gamma/(2*np.pi*f0)
-	q = 0.5*(sigma_f/f0)*(sigma_f/f0)
-	z = complex(1.0/(2.0*np.sqrt(q)),-p/(2.0*np.sqrt(q)))
-	U = np.sqrt(np.pi/(4.0*q))*np.real(w(z))
-	dUdp = np.sqrt(np.pi)/(4*q)*(2/np.sqrt(np.pi) + 2*np.real(J*z*w(z)))
-	first_term = np.sqrt(np.pi/2)*sigma_t*R0*s(t,E0,sigma_t)*U
-	second_term = np.sqrt(np.pi/2)*E0*R0*sigma_t*sigma_t*(sigma_f/f0)*np.exp(-0.5*(t/sigma_t)*(t/sigma_t))*dUdp
-	if(np.isinf(first_term) or np.isinf(second_term) or np.isnan(first_term) or np.isnan(second_term)):
-		return 0.0
-	else:
-		return first_term+second_term
+    J = complex(0,1)
+    units = R0*E0*sigma_t*sigma_t
+    x = t/(sigma_t*np.sqrt(2))
+    z = (2*np.pi*J*f0-2*np.pi*gamma)*np.sqrt(2)*sigma_t
+    q = -J*(x+0.5*z)
+    Re_wq = np.real(w(q))
+    Re_dwdx = np.real(-J*dwdq(q))
+    result = -np.sqrt(np.pi)*units*(x*np.exp(-x*x)*Re_wq-0.5*np.exp(-x*x)*Re_dwdx)
+    if(np.isinf(result) or np.isnan(result)):
+        return 0.0
+    else:
[…]

### 2025-07-03 template.tex
made updates to manuscript reflecting changes in s * r

@@
 \end{equation}
-The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$:}
+The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$} \cite{NIST:DLMF}:
 \begin{equation}
@@
 \end{multline}
-Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function}.  The integral becomes
+Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function} \cite{NIST:DLMF}.  The integral becomes
 \begin{equation}
@@
 \begin{equation}
-\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) |
+\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) | \label{eq:final2}
 \end{equation}
-\item Two examples of comparisons of Eq. \ref{eq:final} to the convolution of $s(t)$ and $r(t)$ are given in Fig. \ref{fig:fig1} below.
-\begin{figure}[hb]
-\centering
-\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
-\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
-\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
-The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
-The light gray envelope represents Eq.
-\ref{eq:final}.
-(Bottom) Same as top, for different parameter values.}
-\end{figure}
-\clearpage
 \item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
@@
 \end{equation}
-Let $b=x+\frac{1}{2}z$, and $a = -jb$.  Completing the square in the exponent of $I(x,z)$ gives
+As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re\lbrace s_a(t)\rbrace$, the result for $I(x,z)$ is
 \begin{equation}
-I(x,z) = \frac{\sqrt{\pi}}{2} w(a)
+I(x,z) = \frac{\sqrt{\pi}}{2} w(q)
 \end{equation}
-where $w(a)$ is the Faddeeva function.
+where $w(q)$ is the Faddeeva function.
 Note that the Faddeeva function is \textit{entire}, meaning the $\Re\lbrace \rbrace$ operator and differentiation commute.
@@
 \begin{multline}
-s * r = \\ -\sqrt{\pi}R_0 E_0 \sigma_t^2 \left(xe^{-x^2} \Re\left\lbrace w(a)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(a)\rbrace}{dx} \right)
+s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dx} \right)
 \end{multline}
-The Faddeeva function may be split into real and imaginary parts via the \textit{Voigt functions}:
-\begin{align}
-w(a) &= U(p,q) + jV(p,q) \\
-p &= 
-\end{align}
+From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$, and $dw(q)/dq = -2qw(q)+2j/\sqrt{\pi}$ \cite{NIST:DLMF}.
+The final result is left in terms of the real part of the Faddeeva function, which may be computed using the \textit{Voigt function} $U(x,t)$ \cite{NIST:DLMF,PhysRevD.105.123019}.
+\begin{multline}
+s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + j\frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
+\end{multline}
+\item To illustrate the accuracy and efficiency of the model, Eq. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
+\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
+\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
+The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
+The light gray envelope represents Eq.
+\ref{eq:final}.
+(Bottom) Same as top, for different parameter values.}
+\end{figure}
 \end{itemize}

### 2025-07-07 template.tex
new plots comparing envelopes

@@
 \centering
-\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
-\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
+\includegraphics[width=0.5\textwidth]{July3rd_plot1.pdf}
+\includegraphics[width=0.5\textwidth]{July3rd_plot2.pdf}
 \caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
-The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
-The light gray envelope represents Eq.
-\ref{eq:final}.
+The light gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
+The dark gray envelope represents Eq.
+\ref{eq:final}-\ref{eq:final2}.
 (Bottom) Same as top, for different parameter values.}

### 2025-07-07 result.py

@@ -52,9 +52,9 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 		result = first_term+J*second_term
 	return 0.5*np.abs(result)
 
-f0 = 0.3 #GHz
-gamma = 0.05 #GHz
-sigma_t = 0.5 #ns
+f0 = 0.15 #GHz
+gamma = 0.033 #GHz
+sigma_t = 1.0 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
@@ -69,11 +69,11 @@ for i in range(n):
     u = t[i]
     result1[i] = math_conv(u,E0,R0,sigma_t,f0,gamma)
     result2[i] = math_env(u,E0,R0,sigma_t,f0,gamma)
-graph1 = np.abs(hilbert(np.real(result1)))*1000
-graph2 = np.real(result2)*1000
-graph3 = np.real(result1)*1000
+graph1 = np.real(result1)*1000
+graph2 = np.abs(hilbert(np.real(result1)))*1000
+graph3 = np.real(result2)*1000
 
-plt.plot(t,graph1,'-',label="env of math conv")
+'''plt.plot(t,graph1,'-',label="env of math conv")
 plt.plot(t,graph2,'-',label="math env")
 plt.plot(t,graph3,'-',label="math conv")
 plt.xlabel("Time [ns]")
@@ -81,4 +81,10 @@ plt.ylabel("Amplitude [mV]")
 plt.xticks()
 plt.yticks()
 plt.legend()
-plt.show()
+plt.show()'''
+
+with(open('results_July3rd.dat','w') as file):
+	for i in range(n):
+		write_string = str(t[i])+" "+str(graph1[i])+" "+str(graph2[i])+" "+str(graph3[i])+"\n"
+		file.write(write_string)
+file.close()

### 2025-07-08 template.tex
added comparison figures for s * r

@@
 \usepackage{mathtools}
-%\usepackage{empheq}
 \usepackage{verbatim}
@@
 \caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
-The light gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
+The light gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 SciPy function scipy.special.hilbert.
 The dark gray envelope represents Eq.
 \ref{eq:final}-\ref{eq:final2}.
+(Bottom) Same as top, for different parameter values.}
+\end{figure}
+\item To demonstrate that \textit{numerical convolution} of $s(t)$ and $r(t)$ produces the same results as the \textit{mathematical convolution} of $s(t)$ and $r(t)$ (Eq.
+\ref{eq:final3}), the corresponding waveforms are shown in Fig.
+\ref{fig:fig2}.
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{July7th_plot1.pdf}
+\includegraphics[width=0.5\textwidth]{July7th_plot2.pdf}
+\caption{\label{fig:fig2} (Top) The thin black line represents $s(t) * r(t)$, produced using the Python3 SciPy function scipy.signal.convolve.
+The dark gray line represents Eq.
+\ref{eq:final3}.
 (Bottom) Same as top, for different parameter values.}

### 2025-07-08 result.py

@@ -52,26 +52,46 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 		result = first_term+J*second_term
 	return 0.5*np.abs(result)
 
-f0 = 0.15 #GHz
-gamma = 0.033 #GHz
-sigma_t = 1.0 #ns
+f0 = 0.3 #GHz
+gamma = 0.05 #GHz
+sigma_t = 0.5 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
-T_min = -10 #ns
+T_min = -100 #ns
 T_max = 100 #ns
 t = np.arange(T_min,T_max,dt)
 n = len(t)
 
 result1 = np.zeros(t.shape,dtype=complex)
 result2 = np.zeros(t.shape,dtype=complex)
+signal = np.zeros(t.shape,dtype=float)
+response = np.zeros(t.shape,dtype=float)
 for i in range(n):
     u = t[i]
+    signal[i] = s(u,E0,sigma_t)
+    response[i] = r(u,R0,f0,gamma)
     result1[i] = math_conv(u,E0,R0,sigma_t,f0,gamma)
     result2[i] = math_env(u,E0,R0,sigma_t,f0,gamma)
 graph1 = np.real(result1)*1000
 graph2 = np.abs(hilbert(np.real(result1)))*1000
 graph3 = np.real(result2)*1000
+graph4 = convolve(signal,response,"same")*dt*1000
+
+'''plt.plot(t,graph4,'-',label="numerical convolution")
+plt.plot(t,graph1,'-',label="math conv")
+plt.xlabel("Time [ns]")
+plt.ylabel("Amplitude [mV]")
+plt.xticks()
+plt.yticks()
+plt.legend()
+plt.show()'''
+
+with(open('results_July7th.dat','w') as file):
+	for i in range(n):
+		write_string = str(t[i])+" "+str(graph4[i])+" "+str(graph1[i])+"\n"
+		file.write(write_string)
+file.close()
 
 '''plt.plot(t,graph1,'-',label="env of math conv")
 plt.plot(t,graph2,'-',label="math env")
@@ -83,8 +103,8 @@ plt.yticks()
 plt.legend()
 plt.show()'''
 
-with(open('results_July3rd.dat','w') as file):
+'''with(open('results_July3rd.dat','w') as file):
 	for i in range(n):
[…]

### 2025-07-11 template.tex
trying to add the connection between sigma_t and energy

@@
 The parameter $E_0$ is the amplitude normalization, and it depends on two parameters: $\sigma_{\rm t}$, and $\omega_{\rm 0}$, the cutoff frequency from the cascade form factor.
+In Sec.
+\ref{sec:onc}, $E_0$ and $\sigma_t$ will be treated as constants, since neither depends on time.
+In Sec.
+\ref{sec:amp}, the implications of these dependencies will be explored.
 \item Let $\widehat{s}(t)$ represent the Hilbert transform of $s(t)$.  The \textit{analytic signal} of $s(t)$ is
@@
 \begin{multline}
-s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + j\frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
+s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + \left(\frac{j}{2}\right)e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
 \end{multline}
@@
 \centering
+\includegraphics[width=0.5\textwidth]{July7th_plot2.pdf}
 \includegraphics[width=0.5\textwidth]{July7th_plot1.pdf}
-\includegraphics[width=0.5\textwidth]{July7th_plot2.pdf}
 \caption{\label{fig:fig2} (Top) The thin black line represents $s(t) * r(t)$, produced using the Python3 SciPy function scipy.signal.convolve.
@@
 \end{figure}
+\end{itemize}
+
+\section{The Amplitude of The Signal Model, $s(t)$}
+\label{sec:amp}
+
+\begin{itemize}
+\item The result for $\mathcal{E}_{r*s}(t)$, Eqs.
+\ref{eq:final} and \ref{eq:final2}, depends on the model for $s(t)$, Eq.
+\ref{eq:s}.
+The parameters $E_0$ and $\sigma_t$ in Eq.
+\ref{eq:s} were held constant in Sec.
+\ref{sec:onc}, because neither depends on time.
+The full expression for $s(t)$ was first derived by the authors of \cite{PhysRevD.105.123019}:
+\begin{equation}
+s(t) = -\frac{E_0\omega_0 \sin(\theta)}{8\pi p}te^{-\frac{t^2}{4p}+p\omega_0^2}\erfc(\sqrt{p}\omega_0) \label{eq:s_full}
+\end{equation}
+The parameters of Eq. \ref{eq:s_full} are defined in Tab. \ref{tab:param}.
+\begin{table*}
+\small
+\begin{tabular}{| c | c | c | c |} \hline
+\textbf{Variable} & \textbf{Definition} & \textbf{Units} & \textbf{Typical Value}\\ \hline
+$c$ & speed of light & meter GHz & 0.299792458 \\ 
+$\theta_{\rm C}$ & Cherenkov angle & radians & 0.9739 \\ 
+$\theta$ & viewing angle from cascade axis & radians & $|\theta-\theta_{\rm C}| = \mathcal{O}(1)$ degree \\ 
+$a$ & longitudinal length of cascade (see \cite{10.1103/physrevd.65.016003}) & meter & $\approx 4.2$ at $\approx 10^{16}$ eV \\ 
+$n_{max}$ & peak excess charged cascade particles (see \cite{10.1103/physrevd.65.016003})  & none & $\mathcal{O}(10^6)$ at $\approx 10^{16}$ eV \\
+$E_{\rm 0}$ & $\propto n_{\rm max}a$ (see \cite{10.1103/physrevd.65.016003}) & V m$^{-1}$ GHz$^{-2}$ & $\approx 1.2$ at $\approx 10^{16}$ eV \\
+$p$ & $\frac{1}{2}(a/c)^2 \left(\cos\theta - \cos\theta_C\right)^2$ (see \cite{PhysRevD.105.123019}) & ns$^2$ & depends on $\theta$, $\sqrt{2 p} \approx$ 1 ns \\ 
+$\omega_{\rm 0}$ & $\sqrt{\frac{2}{3}} (c\sqrt{2\pi}\rho_{\rm 0})/(n\sin\theta)$ (see \cite{10.1016/j.astropartphys.2017.03.008}) & GHz & depends on $\theta$, $\omega_0/(2\pi)$ is $\mathcal{O}(1)$ GHz \\
+$\sqrt{2\pi}\rho_{\rm 0}$ & lateral ICD width (see \cite{10.1016/j.astropartphys.2017.03.008}) & m$^{-1}$ & $\approx 20$ m$^{-1}$ at $\approx 10^{17}$ eV \\
+$n$ & index of refraction, ice & none & $1.778 \pm 0.006$ for RF bandwidth \\ \hline
+\end{tabular}
+\caption{\label{tab:param} things.}
+\end{table*}
+There is a deep connection between $s(t)$, Eqs.
+\ref{eq:final}-\ref{eq:final2}, and the natural logarithm of the UHE-$\nu$ cascade energy, $\ln(E_{\rm C}/E_{\rm crit})$.
+The authors of \cite{PhysRevD.105.123019} have shown that
+\begin{equation}
+a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}}
+\end{equation}
 \end{itemize}

### 2025-07-13 template.tex
Updates from Overleaf

--- 2025-07-07 template.tex
@@
 \end{equation}
-The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$} \cite{NIST:DLMF}:
+The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$:}
 \begin{equation}
@@
 \end{multline}
-Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function} \cite{NIST:DLMF}.  The integral becomes
+Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function}.  The integral becomes
 \begin{equation}
@@
 \begin{equation}
-\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) | \label{eq:final2}
+\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) |
 \end{equation}
+\item Two examples of comparisons of Eq. \ref{eq:final} to the convolution of $s(t)$ and $r(t)$ are given in Fig. \ref{fig:fig1} below.
+\begin{figure}[hb]
+\centering
+\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
+\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
+\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
+The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
+The light gray envelope represents Eq.
+\ref{eq:final}.
+(Bottom) Same as top, for different parameter values.}
+\end{figure}
+\clearpage
 \item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
@@
 \end{equation}
-As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re\lbrace s_a(t)\rbrace$, the result for $I(x,z)$ is
+As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re{s_a(t)}$, the result for $I(x,z)$ is
 \begin{equation}
@@
 \end{multline}
-From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$, and $dw(q)/dq = -2qw(q)+2j/\sqrt{\pi}$ \cite{NIST:DLMF}.
-The final result is left in terms of the real part of the Faddeeva function, which may be computed using the \textit{Voigt function} $U(x,t)$ \cite{NIST:DLMF,PhysRevD.105.123019}.
-\begin{multline}
-s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + j\frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
-\end{multline}
-\item To illustrate the accuracy and efficiency of the model, Eq. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{July3rd_plot1.pdf}
-\includegraphics[width=0.5\textwidth]{July3rd_plot2.pdf}
-\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
-The light gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert.
-The dark gray envelope represents Eq.
-\ref{eq:final}-\ref{eq:final2}.
-(Bottom) Same as top, for different parameter values.}
-\end{figure}
+Because the Faddeeva function is \textit{entire}, the derivative commutes with the $\Re\lbrace\rbrace$ operator.
+From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$.
+The complex derivative
 \end{itemize}

### 2025-07-18 template.tex
trying to update the section about amplitude parameters

--- 2025-07-08 template.tex
@@
 \end{figure}
+\end{itemize}
+
+\section{The Amplitude of The Signal Model, $s(t)$}
+\label{sec:amp}
+
+\begin{itemize}
+\item The result for $\mathcal{E}_{r*s}(t)$, Eqs.
+\ref{eq:final} and \ref{eq:final2}, depends on the model for $s(t)$, Eq.
+\ref{eq:s}.
+The parameters $E_0$ and $\sigma_t$ in Eq.
+\ref{eq:s} were held constant in Sec.
+\ref{sec:onc}, because neither depends on time.
+The full expression for $s(t)$ was first derived by the authors of \cite{PhysRevD.105.123019}:
+\begin{equation}
+r\vec{E}(t_{\rm r},\theta) = -\frac{E_0\omega_0 \sin(\theta)}{8\pi p}t_{\rm r}e^{-\frac{t_{\rm r}^2}{4p}+p\omega_0^2}\erfc(\sqrt{p}\omega_0) \label{eq:s_full}
+\end{equation}
+The parameters of Eq. \ref{eq:s_full} are defined in Tab. \ref{tab:param}.
+\begin{table}
+\small
+\begin{tabular}{| c | c | c |} \hline
+\textbf{Variable} & \textbf{Definition} & \textbf{Units}\\ \hline
+$c$ & speed of light in medium & m ns$^{-1}$ \\ 
+$r$ & distance to cascade peak & m \\
+$t_{\rm r}$ & $t-r/c$ & ns \\
+$\theta_{\rm C}$ & Cherenkov angle & radians \\ 
+$\theta$ & viewing angle from cascade axis & radians \\ 
+$a$ & longitudinal cascade length (see \cite{10.1103/physrevd.65.016003}) & m \\ 
+$n_{max}$ & max excess cascade particles (see \cite{10.1103/physrevd.65.016003})  & none \\
+$E_{\rm 0}$ & $\propto n_{\rm max}a$ (see \cite{10.1103/physrevd.65.016003}) & V GHz$^{-2}$ \\
+$p$ & $\frac{1}{2}(a/c)^2 \left(\cos\theta - \cos\theta_C\right)^2$ (see \cite{PhysRevD.105.123019}) & ns$^2$ \\ 
+$\omega_{\rm 0}$ & $\sqrt{\frac{2}{3}} (c\sqrt{2\pi}\rho_{\rm 0})/(\sin\theta)$ (see \cite{10.1016/j.astropartphys.2017.03.008}) & GHz \\
+$\sqrt{2\pi}\rho_{\rm 0}$ & lateral ICD width (see \cite{10.1016/j.astropartphys.2017.03.008}) & m$^{-1}$ \\ \hline
+\end{tabular}
+\caption{\label{tab:param} things.}
+\end{table}
+Though the authors of \cite{10.1103/physrevd.65.016003} use $c$ for the vaccuum value of the speed of light, the formulae for $r \vec{E}$ presented in \cite{10.1103/physrevd.65.016003} typically refer to the wavenumber $k$ in the medium, which is proptional to the index of refraction.
+Thus, the use of $c$ in this work refers to the speed of light in the medium.
+For example, a phase factor of $\exp(j k r)$ could also be written $\exp(j r \omega/c)$, if $c$ refers to the value in the medium.
+From the ``acceleration argument'' in \cite{10.1103/physrevd.65.016003}, $r$ is the distance to ...
+The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, typically quoted as 55.8 degrees in the RF bandwidth.
+The authors of \cite{10.1103/physrevd.65.016003} define the longitudinal cascade length, $a$, relative to the length over which the Askaryan ra
+
+There is a deep connection between $s(t)$, Eqs.
+\ref{eq:final}-\ref{eq:final2}, and the natural logarithm of the UHE-$\nu$ cascade energy, $\ln(E_{\rm C}/E_{\rm crit})$.
+The authors of \cite{PhysRevD.105.123019} have shown that
+\begin{equation}
+a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}}
+\end{equation}
 \end{itemize}

### 2025-07-21 template.tex
update to further writing of paper

@@
 \end{equation}
-The parameters of Eq. \ref{eq:s_full} are defined in Tab. \ref{tab:param}.
 \begin{table}
@@
 \end{table}
-Though the authors of \cite{10.1103/physrevd.65.016003} use $c$ for the vaccuum value of the speed of light, the formulae for $r \vec{E}$ presented in \cite{10.1103/physrevd.65.016003} typically refer to the wavenumber $k$ in the medium, which is proptional to the index of refraction.
+
+The parameters of Eq.
+\ref{eq:s_full} are shown in Tab.
+\ref{tab:param}.
+Though Ralston and Buniy (RB) \cite{10.1103/physrevd.65.016003} used $c$ for the vaccuum value of the speed of light, the formulae for $r \vec{E}$ presented in \cite{10.1103/physrevd.65.016003} refer to the wavenumber $k$ in the medium, which is proptional to the index of refraction.
 Thus, the use of $c$ in this work refers to the speed of light in the medium.
 For example, a phase factor of $\exp(j k r)$ could also be written $\exp(j r \omega/c)$, if $c$ refers to the value in the medium.
-From the ``acceleration argument'' in \cite{10.1103/physrevd.65.016003}, $r$ is the distance to ...
-The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, typically quoted as 55.8 degrees in the RF bandwidth.
-The authors of \cite{10.1103/physrevd.65.016003} define the longitudinal cascade length, $a$, relative to the length over which the Askaryan ra
+The distance $r$ is between the observer and the radiating charge at the cascade peak.
+The longitudinal length over which $\Delta r < \lambda$, the RF wavelength in ice, is named the \textit{coherence zone} $\Delta z_{\rm coh}$ in the RB model.
+The $\Delta z_{\rm coh}$ is limited by what RB call the ``acceleration argument,'' that $r(t)$ is accelerating while keeping $\Delta r < \lambda$.
+
+The longitudinal cascade length, $a$, is set by the cascade physics.
+The ratio $\eta = (a/\Delta z_{\rm coh})^2$ corresponds to the far-field limit as $\eta \to 0$, but this is not a requirement of the RB model.
+In fact, the RB equations are valid when $\eta > 1$.
+Hanson and Connolly (JCH+AC) have shown that $\eta$ corresponds to low-pass filter with cutoff $\omega_{\rm C}$ that limits the RF emissions, $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
+JCH+AC also studied $\omega_{\rm C}$ over the frequency and $a$ parameter space, because this parameter space is relevant for the LPM effect.
+
+The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}.
+The delayed time is $t_{\rm r} = t-r/c$.
+The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.
+The value often quoted for the RF bandwidth in ice ($n=1.78$) is 55.8 degrees.
+The viewing angle $\theta$ is measured relative to the cascade axis, and the Askaryan radiation is concentrated when $\theta$ is close to $\theta_{\rm C}$.
+The $n_{\rm max}$ parameter is the maximum excess negative charge in the cascade, and the overall RF amplitude is propotional to $n_{\rm max} a$.
+Hanson and Hartig (HH) have shown that the parameter $p$ is related to the pulse width \cite{PhysRevD.105.123019}:
+
+\begin{equation}
+\sigma_t = \sqrt{2p}
+\end{equation}
 

### 2025-07-22 template.tex
another update ... trying to get energy

@@
 The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.
-The value often quoted for the RF bandwidth in ice ($n=1.78$) is 55.8 degrees.
-The viewing angle $\theta$ is measured relative to the cascade axis, and the Askaryan radiation is concentrated when $\theta$ is close to $\theta_{\rm C}$.
+The value for the RF bandwidth in solid ice ($n=1.78$) is 55.8 degrees.
+More detail on the index of refraction in polar ice is given in \cite{Barwick:2018497,ALLISON201963}.
+The viewing angle $\theta$ is measured relative to the cascade axis, and the Askaryan radiation is concentrated when $\theta \approx \theta_{\rm C}$.
 The $n_{\rm max}$ parameter is the maximum excess negative charge in the cascade, and the overall RF amplitude is propotional to $n_{\rm max} a$.
-Hanson and Hartig (HH) have shown that the parameter $p$ is related to the pulse width \cite{PhysRevD.105.123019}:
+Hanson and Hartig (HH) have shown that the parameter $p$ is related to $\sigma_t$ \cite{PhysRevD.105.123019}:
 
 \begin{equation}
-\sigma_t = \sqrt{2p}
+\sigma_t = \sqrt{2p} \label{eq:pulse_width}
 \end{equation}
 
-There is a deep connection between $s(t)$, Eqs.
-\ref{eq:final}-\ref{eq:final2}, and the natural logarithm of the UHE-$\nu$ cascade energy, $\ln(E_{\rm C}/E_{\rm crit})$.
-The authors of \cite{PhysRevD.105.123019} have shown that
+The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta = (=\theta-\theta_{\rm C}$, $p \propto \Delta\theta^2$ to second order, and
+
 \begin{equation}
@@
 \end{equation}
+
+Qualitatively, this notion was identified by RB in Sec. III of \cite{10.1103/physrevd.65.016003}.  Discuss error prop to lnE
 \end{itemize}

### 2025-07-24 template.tex
trying to grind the paper forward

@@
 
-The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta = (=\theta-\theta_{\rm C}$, $p \propto \Delta\theta^2$ to second order, and
+The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta=(\theta-\theta_{\rm C}$, $p \propto \Delta\theta^2$ to second order, and
 
@@
 
-Qualitatively, this notion was identified by RB in Sec. III of \cite{10.1103/physrevd.65.016003}.  Discuss error prop to lnE
+Qualitatively, this notion was identified by RB in Sec.
+III of \cite{10.1103/physrevd.65.016003}.
+HH provided an analysis of the relationship between $a$, the cascade energy $E_{\rm C}$ and the critical energy $E_{\rm crit}$ \cite{PhysRevD.105.123019}.
+Let $E_{\rm C}/E_{\rm crit} = \Lambda$.
+HH found that
+
+\begin{equation}
+\frac{\sigma_{\ln\Lambda}}{\ln\Lambda} = 2\left(\frac{\sigma_a}{a}\right)
+\end{equation}
 \end{itemize}

### 2025-07-25 template.tex
re-ordered the paper sections to focus on the main goal, definitions in order

--- 2025-07-22 template.tex
@@
 
-The units.
+\begin{itemize}
+\item The result for $\mathcal{E}_{r*s}(t)$, Eqs.
+\ref{eq:final} and \ref{eq:final2}, depends on the model for $s(t)$, Eq.
+\ref{eq:s}.
+Equation \ref{eq:s} is a simplified version of Eq.
+28 in the analysis presented by Hanson and Hartig (HH) \cite{PhysRevD.105.123019}.
+The $E_0$ simply represents all time-independent amplitude factors.
+The full expression for $s(t)$ is
+\begin{equation}
+r\vec{E}(t_{\rm r},\theta) = -\frac{E_0\omega_0 \sin(\theta)}{8\pi p}t_{\rm r}e^{-\frac{t_{\rm r}^2}{4p}+p\omega_0^2}\erfc(\sqrt{p}\omega_0) \label{eq:s_full}
+\end{equation}
+\begin{table}
+\small
+\begin{tabular}{| c | c | c |} \hline
+\textbf{Variable} & \textbf{Definition} & \textbf{Units}\\ \hline
+$c$ & speed of light in medium & m ns$^{-1}$ \\ 
+$r$ & distance to cascade peak & m \\
+$t_{\rm r}$ & $t-r/c$ & ns \\
+$\theta_{\rm C}$ & Cherenkov angle & radians \\ 
+$\theta$ & viewing angle from cascade axis & radians \\ 
+$a$ & longitudinal cascade length (see \cite{10.1103/physrevd.65.016003}) & m \\ 
+$n_{max}$ & max excess cascade particles (see \cite{10.1103/physrevd.65.016003})  & none \\
+$E_{\rm 0}$ & $\propto n_{\rm max}a$ (see \cite{10.1103/physrevd.65.016003}) & V GHz$^{-2}$ \\
+$p$ & $\frac{1}{2}(a/c)^2 \left(\cos\theta - \cos\theta_C\right)^2$ (see \cite{PhysRevD.105.123019}) & ns$^2$ \\ 
+$\omega_{\rm 0}$ & $\sqrt{\frac{2}{3}} (c\sqrt{2\pi}\rho_{\rm 0})/(\sin\theta)$ (see \cite{10.1016/j.astropartphys.2017.03.008}) & GHz \\
+$\sqrt{2\pi}\rho_{\rm 0}$ & lateral ICD width (see \cite{10.1016/j.astropartphys.2017.03.008}) & m$^{-1}$ \\ \hline
+\end{tabular}
+\caption{\label{tab:param} things.}
+\end{table}
+
+The parameters of Eq.
+\ref{eq:s_full} are shown in Tab.
+\ref{tab:param}.
+Though Ralston and Buniy (RB) \cite{10.1103/physrevd.65.016003} used $c$ for the vaccuum value of the speed of light, the formulae for $r \vec{E}$ presented in \cite{10.1103/physrevd.65.016003} refer to the wavenumber $k$ in the medium, which is proptional to the index of refraction.
+Thus, the use of $c$ in this work refers to the speed of light in the medium.
+For example, a phase factor of $\exp(j k r)$ could also be written $\exp(j r \omega/c)$, if $c$ refers to the value in the medium.
+The distance $r$ is between the observer and the radiating charge at the cascade peak.
+The longitudinal length over which $\Delta r < \lambda$, the RF wavelength in ice, is named the \textit{coherence zone} $\Delta z_{\rm coh}$ in the RB model.
+The $\Delta z_{\rm coh}$ is limited by what RB call the ``acceleration argument,'' that $r(t)$ is accelerating while keeping $\Delta r < \lambda$.
+
+The longitudinal cascade length, $a$, is set by the cascade physics.
+The ratio $\eta = (a/\Delta z_{\rm coh})^2$ corresponds to the far-field limit as $\eta \to 0$, but this is not a requirement of the RB model.
+In fact, the RB equations are valid when $\eta > 1$.
+Hanson and Connolly (JCH+AC) have shown that $\eta$ corresponds to low-pass filter with cutoff $\omega_{\rm C}$ that limits the RF emissions, $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
+JCH+AC also studied $\omega_{\rm C}$ over the frequency and $a$ parameter space, because this parameter space is relevant for the LPM effect.
+
+The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}.
+The delayed time is $t_{\rm r} = t-r/c$.
+The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.
+The value for the RF bandwidth in solid ice ($n=1.78$) is 55.8 degrees.
+More detail on the index of refraction in polar ice is given in \cite{Barwick:2018497,ALLISON201963}.
+The viewing angle $\theta$ is measured relative to the cascade axis, and Askaryan radiation is concentrated for $\theta \approx \theta_{\rm C}$.
+The $n_{\rm max}$ parameter is the maximum excess negative cascade charge, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$.
+
+JCH+AC and Hanson and Hartig (HH) demonstrate how the cutoff frequency $\omega_{\rm 0}$ is related to the instantaneous charge distribution (ICD) and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
+Monte Carlo simulations have shown that the lateral dependence of the ICD is, to first order, exponentially distributed \cite{zhs,PhysRevD.105.123019}.
+In JCH+AC, characterizing the lateral component of the ICD as $\exp(-\sqrt{2\pi}\rho_0 \rho)$ led to an elegant expression for the ICD form factor, $\widetilde{F}(\omega)$.
+
+Hanson and Hartig (HH) have shown that the parameter $p$ is related to $\sigma_t$ \cite{PhysRevD.105.123019}:
+
+\begin{equation}
+\sigma_t = \sqrt{2p} \label{eq:pulse_width}
+\end{equation}
+
+The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta=(\theta-\theta_{\rm C})$, $p \propto \Delta\theta^2$ to second order, and
+
+\begin{equation}
+a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}} \label{eq:uncert}
+\end{equation}
+
+Qualitatively, this notion was identified by RB in Sec.
+III of \cite{10.1103/physrevd.65.016003}.
+HH analyzed the relationship between $a$, the cascade energy $E_{\rm C}$ and the critical energy $E_{\rm crit}$ for electromagnetic and hadronic cascades \cite{PhysRevD.105.123019}.
+Let $E_{\rm C}/E_{\rm crit} = \Lambda$.
+Assuming the Greisen and Gaisser-Hillas parameterizaions for electromagnetic and hadronic cascades, respectively, HH found the relationship
+
+\begin{align}
+a &= c_{\rm em} \sqrt{\ln\Lambda} \\
+a &= c_{\rm had} \sqrt{\ln\Lambda}
+\end{align}
+
+\begin{equation}
+\frac{\sigma_{\ln\Lambda}}{\ln\Lambda} = 2\left(\frac{\sigma_a}{a}\right) \label{eq:a_err}
+\end{equation}
+
+Equation \ref{eq:a_err} corresponds to Eq.
+42 in \cite{PhysRevD.105.123019}, and has been corrected for units.
+Equations \ref{eq:pulse_width}-\ref{eq:a_err} imply measurements of $a$ and $\Delta\theta$ lead to a measurement of the logarithm of the cascade energy $\ln\Lambda$, and that the relative error in $\ln\Lambda$ is proportional to the relative error in $a$.
+\end{itemize}
 
@@
 \ref{sec:onc}, $E_0$ and $\sigma_t$ will be treated as constants, since neither depends on time.
-In Sec.
-\ref{sec:amp}, the implications of these dependencies will be explored.
 \item Let $\widehat{s}(t)$ represent the Hilbert transform of $s(t)$.  The \textit{analytic signal} of $s(t)$ is
@@
 
-\section{The Amplitude of The Signal Model, $s(t)$}
-\label{sec:amp}
-
-\begin{itemize}
-\item The result for $\mathcal{E}_{r*s}(t)$, Eqs.
-\ref{eq:final} and \ref{eq:final2}, depends on the model for $s(t)$, Eq.
-\ref{eq:s}.
-The parameters $E_0$ and $\sigma_t$ in Eq.
-\ref{eq:s} were held constant in Sec.
-\ref{sec:onc}, because neither depends on time.
-The full expression for $s(t)$ was first derived by the authors of \cite{PhysRevD.105.123019}:
-\begin{equation}
-r\vec{E}(t_{\rm r},\theta) = -\frac{E_0\omega_0 \sin(\theta)}{8\pi p}t_{\rm r}e^{-\frac{t_{\rm r}^2}{4p}+p\omega_0^2}\erfc(\sqrt{p}\omega_0) \label{eq:s_full}
-\end{equation}
-\begin{table}
-\small
-\begin{tabular}{| c | c | c |} \hline
-\textbf{Variable} & \textbf{Definition} & \textbf{Units}\\ \hline
-$c$ & speed of light in medium & m ns$^{-1}$ \\ 
-$r$ & distance to cascade peak & m \\
-$t_{\rm r}$ & $t-r/c$ & ns \\
-$\theta_{\rm C}$ & Cherenkov angle & radians \\ 
-$\theta$ & viewing angle from cascade axis & radians \\ 
-$a$ & longitudinal cascade length (see \cite{10.1103/physrevd.65.016003}) & m \\ 
-$n_{max}$ & max excess cascade particles (see \cite{10.1103/physrevd.65.016003})  & none \\
-$E_{\rm 0}$ & $\propto n_{\rm max}a$ (see \cite{10.1103/physrevd.65.016003}) & V GHz$^{-2}$ \\
-$p$ & $\frac{1}{2}(a/c)^2 \left(\cos\theta - \cos\theta_C\right)^2$ (see \cite{PhysRevD.105.123019}) & ns$^2$ \\ 
-$\omega_{\rm 0}$ & $\sqrt{\frac{2}{3}} (c\sqrt{2\pi}\rho_{\rm 0})/(\sin\theta)$ (see \cite{10.1016/j.astropartphys.2017.03.008}) & GHz \\
-$\sqrt{2\pi}\rho_{\rm 0}$ & lateral ICD width (see \cite{10.1016/j.astropartphys.2017.03.008}) & m$^{-1}$ \\ \hline
-\end{tabular}
-\caption{\label{tab:param} things.}
-\end{table}
-
-The parameters of Eq.
-\ref{eq:s_full} are shown in Tab.
-\ref{tab:param}.
-Though Ralston and Buniy (RB) \cite{10.1103/physrevd.65.016003} used $c$ for the vaccuum value of the speed of light, the formulae for $r \vec{E}$ presented in \cite{10.1103/physrevd.65.016003} refer to the wavenumber $k$ in the medium, which is proptional to the index of refraction.
-Thus, the use of $c$ in this work refers to the speed of light in the medium.
-For example, a phase factor of $\exp(j k r)$ could also be written $\exp(j r \omega/c)$, if $c$ refers to the value in the medium.
-The distance $r$ is between the observer and the radiating charge at the cascade peak.
-The longitudinal length over which $\Delta r < \lambda$, the RF wavelength in ice, is named the \textit{coherence zone} $\Delta z_{\rm coh}$ in the RB model.
-The $\Delta z_{\rm coh}$ is limited by what RB call the ``acceleration argument,'' that $r(t)$ is accelerating while keeping $\Delta r < \lambda$.
-
-The longitudinal cascade length, $a$, is set by the cascade physics.
-The ratio $\eta = (a/\Delta z_{\rm coh})^2$ corresponds to the far-field limit as $\eta \to 0$, but this is not a requirement of the RB model.
-In fact, the RB equations are valid when $\eta > 1$.
-Hanson and Connolly (JCH+AC) have shown that $\eta$ corresponds to low-pass filter with cutoff $\omega_{\rm C}$ that limits the RF emissions, $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
-JCH+AC also studied $\omega_{\rm C}$ over the frequency and $a$ parameter space, because this parameter space is relevant for the LPM effect.
-
-The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}.
-The delayed time is $t_{\rm r} = t-r/c$.
-The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.
-The value for the RF bandwidth in solid ice ($n=1.78$) is 55.8 degrees.
-More detail on the index of refraction in polar ice is given in \cite{Barwick:2018497,ALLISON201963}.
-The viewing angle $\theta$ is measured relative to the cascade axis, and the Askaryan radiation is concentrated when $\theta \approx \theta_{\rm C}$.
-The $n_{\rm max}$ parameter is the maximum excess negative charge in the cascade, and the overall RF amplitude is propotional to $n_{\rm max} a$.
-Hanson and Hartig (HH) have shown that the parameter $p$ is related to $\sigma_t$ \cite{PhysRevD.105.123019}:
-
-\begin{equation}
-\sigma_t = \sqrt{2p} \label{eq:pulse_width}
-\end{equation}
-
-The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta = (=\theta-\theta_{\rm C}$, $p \propto \Delta\theta^2$ to second order, and
-
-\begin{equation}
-a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}}
-\end{equation}
-
-Qualitatively, this notion was identified by RB in Sec. III of \cite{10.1103/physrevd.65.016003}.  Discuss error prop to lnE
-\end{itemize}
-
 \section{Conclusion}

### 2025-07-25 template.tex
continuing to write abstract, introduction

@@
 
-\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals}
+\title{Complex Analysis of Askaryan Radiation: UHE-$\nu$ Energy Reconstruction via the Hilbert Envelope of Observed Signals}
 
@@
 \begin{abstract}
-This is a work in progress.
+The detection of cosmogenic and astrophysical neutrinos with energies greater than 10 PeV has been a long-time goal of the astroparticle physics community.
+Due to the small flux of such particles, a key strategy has been to deploy autonomous, radio-frequency (RF) detetectors in polar regions that rely on the Askaryan effect for the neutrino signal.
+The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.
+Neutrinos with energies greater than 10 PeV can induce cascades that radiate in the radio-frequency (RF) bandwidth.
+To identify neutrino signals in future data from autonomous RF detectors, mathematical models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.
+In the past, mathematical models have only described the Askaryan electromagnetic field, leaving the effect of the RF detection channels on the observed waveforms to simulation packages (NuRadioMC).
+In this work, we present a fully analytic model that accounts for the effect of an RF detection channel.
+We provide a formula for the observed voltage trace, and a formula for the Hilbert envelope of the trace.
+We compare our models to traces and envelopes recorded from large-scale simulations of Askaryan-class neutrino detectors (NuRadioMC).
+Our equations match NuRadioMC with correlation coefficients greater than 0.95, and power differences of less than 5\%.
 \end{abstract}
@@
 
-The introduction.
+Extrasolar neutrinos with energies between [0.01–1] PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}.
+Previous analyses indicate that the discovery of neutrinos above 5 PeV to 20 EeV will  require large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.
+Neutrinos with energies in the EeV range could potentially reveal the source of ultra-high energy cosmic rays.
+Further, studying electroweak interactions at these energies is virtually impossible on Earth, and Askaryan-class neutrino detectors could provide new data.
+
+%of ultra-high-energy neutrinos (UHE-ν) will require an
+%expansion in detector volume because the flux is expected
+%to decrease with energy [2–6]. The UHE-ν flux could
+%potentially explain the origin of UHE cosmic rays
+%(UHECR), and provides the opportunity to study electro-
+%weak interactions at record-breaking energies [7,8].
+%Utilizing the Askaryan effect expands the effective volume
+%of UHE-ν detector designs, because this effect offers a way
+%to detect UHE-ν with radio pulses that travel more than
+%1 km in sufficiently RF-transparent media such as Antarctic
+%and Greenlandic ice [9–11].
 
@@
 \end{equation}
-\begin{table}
-\small
+\begin{table*}
 \begin{tabular}{| c | c | c |} \hline
@@
 \caption{\label{tab:param} things.}
-\end{table}
+\end{table*}
 

### 2025-08-07 template.tex
minor work on abstract and intro

--- 2025-07-25 template.tex
@@
 \begin{abstract}
-This is a work in progress.
+The detection of neutrinos with energies greater than 10 PeV has been a long-time goal of the astroparticle physics community.
+A key strategy has been to deploy autonomous, radio-frequency (RF) detetectors in polar regions that rely on the Askaryan effect in ice for the neutrino signal.
+The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.
+Neutrinos with energies above 10 PeV can induce cascades that radiate in the radio-frequency (RF) bandwidth above thermal backgrounds.
+To identify neutrino signals in future data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.
+In the past, these models have only described the Askaryan electromagnetic field, leaving the effect of the RF detection channels on the field to simulation packages.
+In this work, we present a fully analytic Askaryan model that accounts for the effect of an RF detection channel.
+We provide formulas for the observed voltage trace, and for the Hilbert envelope of the trace.
+We compare our analytic envelope equation to simulated data computed with NuRadioMC, a key Monte Carlo toolset in high-energy neutrino detection.
+Our equation matches the data with correlation coefficients greater than 0.95.
+Using the analytic envelope technique, we reconstruct key neutrino properties.
 \end{abstract}
@@
 
-The introduction.
+Cosmic neutrinos with energies up to 100 PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}.
+Previous analyses indicate that the discovery of neutrinos above 5 PeV to 20 EeV will  require large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.
+Neutrinos with energies in the EeV range could potentially reveal the source of ultra-high energy cosmic rays.
+Further, studying electroweak interactions at these energies is virtually impossible on Earth, and Askaryan-class neutrino detectors could provide new data.
+
+%of ultra-high-energy neutrinos (UHE-ν) will require an
+%expansion in detector volume because the flux is expected
+%to decrease with energy [2–6]. The UHE-ν flux could
+%potentially explain the origin of UHE cosmic rays
+%(UHECR), and provides the opportunity to study electro-
+%weak interactions at record-breaking energies [7,8].
+%Utilizing the Askaryan effect expands the effective volume
+%of UHE-ν detector designs, because this effect offers a way
+%to detect UHE-ν with radio pulses that travel more than
+%1 km in sufficiently RF-transparent media such as Antarctic
+%and Greenlandic ice [9–11].
 

### 2025-08-08 template.tex
revised the first figure, abstract, and running more code

--- 2025-07-25 template.tex
@@
 
-\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals}
+\title{Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction via the Hilbert Envelope of Observed Signals}
 
@@
 \begin{abstract}
-This is a work in progress.
+The detection of ultra-high energy neutrinos (UHE-$\nu$), with enegies above 10 PeV, has been a long-time goal of the astroparticle physics community.
+A key strategy has been to deploy autonomous, radio-frequency (RF) detetectors in polar regions that rely on the Askaryan effect in ice for the neutrino signal.
+The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.
+UHE-$\nu$ can induce cascades that radiate in the radio-frequency (RF) bandwidth above thermal backgrounds.
+To identify UHE-$\nu$ signals in future data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.
+In the past, these models have only described the Askaryan electromagnetic field, leaving the effect of the RF detection channels on the field to simulation packages.
+In this work, we present a fully analytic Askaryan model that accounts for the effect of an RF detection channel.
+We provide formulas for the observed voltage trace, and for the Hilbert envelope of the trace.
+We match the equations to data computed with NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
+Our analytic model and NuRadioMC match, with correlation coefficients $>0.95$.
+Using this correlation, we demonstrate that RF thermal noise and UHE-$\nu$ signals can be classified to better than xxx.
+Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy using the analytic model, with a precision of yyy.
 \end{abstract}
@@
 
-The introduction.
+Cosmic neutrinos with energies up to 100 PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}.
+Previous analyses indicate that the discovery of neutrinos above 5 PeV to 20 EeV will  require large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.
+Neutrinos with energies in the EeV range could potentially reveal the source of ultra-high energy cosmic rays (see sections 3.1-3.3 of \cite{10.48550/arxiv.2008.04323}).
+Further, studying electroweak interactions at these energies is impossible on Earth, and Askaryan-class neutrino detectors provide new data (see section 3.4 of \cite{10.48550/arxiv.2008.04323}).
+
+This work is the first application of the Hanson and Hartig (HH) model for the purposes of reconstruction.
 
@@
 The residue from the pole at $z_{+}$ drives the final result.
+(Check the sign of time here, to ensure that it is positive).
 \item The goal is now to apply Eq.

### 2025-08-08 result.py

@@ -87,11 +87,11 @@ plt.yticks()
 plt.legend()
 plt.show()'''
 
-with(open('results_July7th.dat','w') as file):
+'''with(open('results_July7th.dat','w') as file):
 	for i in range(n):
 		write_string = str(t[i])+" "+str(graph4[i])+" "+str(graph1[i])+"\n"
 		file.write(write_string)
-file.close()
+file.close()'''
 
 '''plt.plot(t,graph1,'-',label="env of math conv")
 plt.plot(t,graph2,'-',label="math env")
@@ -103,8 +103,8 @@ plt.yticks()
 plt.legend()
 plt.show()'''
 
-'''with(open('results_July3rd.dat','w') as file):
+with(open('results_July3rd.dat','w') as file):
 	for i in range(n):
 		write_string = str(t[i])+" "+str(graph1[i])+" "+str(graph2[i])+" "+str(graph3[i])+"\n"
 		file.write(write_string)
-file.close()'''
+file.close()

### 2025-08-14 template.tex
updated first four plots; trying to gauge efficiency

@@
 A key strategy has been to deploy autonomous, radio-frequency (RF) detetectors in polar regions that rely on the Askaryan effect in ice for the neutrino signal.
-The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.
-UHE-$\nu$ can induce cascades that radiate in the radio-frequency (RF) bandwidth above thermal backgrounds.
+The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium, and UHE-$\nu$ can induce such cascades that radiate in the radio-frequency (RF) bandwidth above thermal backgrounds.
 To identify UHE-$\nu$ signals in future data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.
-In the past, these models have only described the Askaryan electromagnetic field, leaving the effect of the RF detection channels on the field to simulation packages.
+These models have correctly described the Askaryan electromagnetic field, while leaving the effect of the RF detection channels on the field to simulation packages.
 In this work, we present a fully analytic Askaryan model that accounts for the effect of an RF detection channel.
@@
 Our analytic model and NuRadioMC match, with correlation coefficients $>0.95$.
-Using this correlation, we demonstrate that RF thermal noise and UHE-$\nu$ signals can be classified to better than xxx.
-Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy using the analytic model, with a precision of yyy.
+Using this correlation, UHE-$\nu$ signals can be distinguished from RF backgrounds with an efficiency of xxx.
+Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy with a precision of yyy using a single string of RF channels.
 \end{abstract}
@@
 \centering
+\includegraphics[width=0.5\textwidth]{July7th_plot1.pdf}
 \includegraphics[width=0.5\textwidth]{July7th_plot2.pdf}
-\includegraphics[width=0.5\textwidth]{July7th_plot1.pdf}
 \caption{\label{fig:fig2} (Top) The thin black line represents $s(t) * r(t)$, produced using the Python3 SciPy function scipy.signal.convolve.

### 2025-08-14 efficiency.m

@@ -1,0 +1,21 @@
+clear;
+close;
+home;
+results = load('all_results.dat');
+bin_min = 0.0;
+bin_max = 1.0;
+bin_delta = 0.005;
+bins = bin_min:bin_delta:bin_max;
+n = length(bins);
+[y1,x1] = hist(results(:,8),bins);
+[y2,x2] = hist(results(:,5),bins);
+eff = zeros(size(bins));
+for i=1:n
+	if(y1(i)>0)
+		eff(i) = y2(i)/y1(i);
+	endif
+endfor
+plot(eff)
+hold on
+plot(y1)
+plot(y2)

### 2025-08-14 result.py

@@ -52,9 +52,9 @@ def math_env(t,E0,R0,sigma_t,f0,gamma):
 		result = first_term+J*second_term
 	return 0.5*np.abs(result)
 
-f0 = 0.3 #GHz
-gamma = 0.05 #GHz
-sigma_t = 0.5 #ns
+f0 = 0.15 #GHz
+gamma = 0.033 #GHz
+sigma_t = 1.0 #ns
 R0 = 1
 E0 = 1
 dt = 0.01 #ns
@@ -87,11 +87,11 @@ plt.yticks()
 plt.legend()
 plt.show()'''
 
-'''with(open('results_July7th.dat','w') as file):
+with(open('results_July7th_2.dat','w') as file):
 	for i in range(n):
 		write_string = str(t[i])+" "+str(graph4[i])+" "+str(graph1[i])+"\n"
 		file.write(write_string)
-file.close()'''
+file.close()
 
 '''plt.plot(t,graph1,'-',label="env of math conv")
 plt.plot(t,graph2,'-',label="math env")
@@ -103,8 +103,8 @@ plt.yticks()
 plt.legend()
 plt.show()'''
 
-with(open('results_July3rd.dat','w') as file):
+'''with(open('results_July3rd_2.dat','w') as file):
 	for i in range(n):
 		write_string = str(t[i])+" "+str(graph1[i])+" "+str(graph2[i])+" "+str(graph3[i])+"\n"
 		file.write(write_string)
-file.close()
+file.close()'''

### 2025-08-15 efficiency.m
working on cut efficiency plot.

@@ -1,21 +1,27 @@
 clear;
 close;
 home;
+pkg load optim
+
 results = load('all_results.dat');
-bin_min = 0.0;
+bin_min = 0.100;
 bin_max = 1.0;
-bin_delta = 0.005;
+bin_delta = 0.01;
 bins = bin_min:bin_delta:bin_max;
 n = length(bins);
-[y1,x1] = hist(results(:,8),bins);
-[y2,x2] = hist(results(:,5),bins);
-eff = zeros(size(bins));
-for i=1:n
-	if(y1(i)>0)
-		eff(i) = y2(i)/y1(i);
-	endif
-endfor
-plot(eff)
-hold on
-plot(y1)
-plot(y2)
+[y1,x1] = hist(results(:,8),bins,1);
+[y2,x2] = hist(results(:,5),bins,1);
+
+p0 = [0.08,0.05,0.05];
+[p1,~] = lsqcurvefit(@fit_function,p0,x1,y1);
+xfit = linspace(bin_min,bin_max,length(bins)*100);
+yfit = fit_function(p1,xfit);
+figure(1,'position',[0 500 0 500]);
+hold on;
+semilogy(x1,y1,'o','color','black','markersize',8);
+semilogy(xfit,yfit,'-','color','black','linewidth',0.5)
+semilogy(x2,y2,'-','color','black','linewidth',2)
+axis([0 1 3.01e-8 0.301]);
+set(gca(),'fontname','courier','fontsize',20,'box','on');
+xlabel('Correlation coefficient','fontname','courier','fontsize',20,'offset',[0 -0.1]);
+ylabel('Probability density','fontname','courier','fontsize',20,'offset',[-0.1 0]);

### 2025-08-15 fit_function.m

@@ -1,0 +1,4 @@
+function res = fit_function(p0,x)
+	xfit = (x-p0(1))./p0(2);
+	res = p0(3).*xfit.^2.*exp(-0.5*xfit.^2);
+endfunction

### 2025-08-15 efficiency.m
finished efficiency analysis

@@ -2,26 +2,50 @@ clear;
 close;
 home;
 pkg load optim
-
+fontsize = 18;
+markersize = 8;
+signal_linewidth = 3.0;
+noise_linewidth = 1.5;
 results = load('all_results.dat');
-bin_min = 0.100;
+bin_delta = 0.02;
+bin_min = 0.1;
 bin_max = 1.0;
-bin_delta = 0.01;
 bins = bin_min:bin_delta:bin_max;
 n = length(bins);
 [y1,x1] = hist(results(:,8),bins,1);
 [y2,x2] = hist(results(:,5),bins,1);
-
+[~,exp_limit_index] = max(y1);
+exp_limit = x1(exp_limit_index)+7*bin_delta;
+exp_limit_index = find(x1>=exp_limit,1);
 p0 = [0.08,0.05,0.05];
-[p1,~] = lsqcurvefit(@fit_function,p0,x1,y1);
+p1 = [exp_limit,0.012];
+[p2,~] = lsqcurvefit(@fit_function,p0,x1,y1);
+[p3,~] = lsqcurvefit(@fit_function_2,p1,x1(exp_limit_index:end),y1(exp_limit_index:end));
 xfit = linspace(bin_min,bin_max,length(bins)*100);
-yfit = fit_function(p1,xfit);
-figure(1,'position',[0 500 0 500]);
+yfit1 = fit_function(p2,xfit);
+yfit2 = fit_function_2(p3,xfit);
+noise_events = 100;
+cut_limit = 0.4;
+signal_efficiency = 0;
+noise_rate = 1;
+while(noise_events>1)
+	cut_limit += 0.001;
+	sig_ll = find(x2>=cut_limit,1);
+	noise_ll = find(xfit>=cut_limit,1);
+	signal_efficiency = sum(y2(sig_ll:end));
+	noise_events = 5*365*24*60*60*noise_rate*sum(yfit2(noise_ll:end));
+endwhile
+display([cut_limit signal_efficiency noise_events])
+
+figure(1);
 hold on;
-semilogy(x1,y1,'o','color','black','markersize',8);
-semilogy(xfit,yfit,'-','color','black','linewidth',0.5)
-semilogy(x2,y2,'-','color','black','linewidth',2)
-axis([0 1 3.01e-8 0.301]);
-set(gca(),'fontname','courier','fontsize',20,'box','on');
-xlabel('Correlation coefficient','fontname','courier','fontsize',20,'offset',[0 -0.1]);
[…]

### 2025-08-15 fit_function_2.m

@@ -1,0 +1,4 @@
+function res = fit_function_2(p0,x)
+	xfit = (x-p0(1))./p0(2);
+	res = p0(2).*exp(-xfit);
+endfunction

### 2025-08-15 template.tex
added efficiency figure and text

@@
 \end{multline}
-\item To illustrate the accuracy and efficiency of the model, Eq. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
-\begin{figure}
+\item To illustrate the accuracy of the model, Eqs. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
+\begin{figure}[ht]
 \centering
@@
 \ref{fig:fig2}.
-\begin{figure}
+\begin{figure}[ht]
 \centering
@@
 \end{figure}
+\item A Monte Carlo data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume with a depth of 0.65 km and a radius of 0.850 km.
+The UHE-$\nu$ energies ranged from 10-100 PeV, with roughly equal numbers of UHE-$\nu$ in each 10 PeV bin.
+The detector included a single string of 8 RF dipole antennas, a filtered passpand of [80,1000] MHz, and 256 samples per channel at a 1 GHz sampling rate.
+The RF trigger responded when 3 of the 8 voltage traces exceeded $\pm 3$ times the $v_{\rm rms}$ of the thermal noise within 256 ns.
+For each triggered UHE-$\nu$ interaction, the Hilbert envelope of the coherently summed waveform (CSW) was calculated and correlated against Eqs.
+\ref{eq:final}-\ref{eq:final2}.
+A quick optimization over the whole data set yielded 0.15 GHz and 0.025 GHz for the $f_0$ and $\gamma$ parameters, respectively.
+Each individual correlation was maximized by varying the just the $\sigma_t$ parameter, yielding an optimized analytical envelope for each event.
+A thermal noise waveform reflective of the detector properties was also generated using NuRadioMC tools for each UHE-$\nu$ event.
+The noise waveform was also correlated against the optimized analytical envelope.
+The probability distributions for the correlation coefficients are shown in Fig.
+\ref{fig:fig3}.
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{Aug15_plot1.pdf}
+\caption{\label{fig:fig3} (Black circles) Noise distribution.
+(Gray dashed line) Fitting function to noise distribution.
+(Solid black line) Exponential fit to tail of noise distribution.
+(Solid gray line) UHE-$\nu$ signal distribution.
+(Dashed black line) Optimized correlation coefficient threshold value.}
+\end{figure}
+In Fig.
+\ref{fig:fig3}, the black circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and the thermal noise waveform.
+A function of the form $x^2 \exp(-0.5 x^2)$ was fit to the black circles on the interval [0.1,1.0], and is represented by the gray dashed line.
+A function of the form $exp(-x)$ was fit to the noise distribution on the interval [0.28,1] to capture the limiting behavior, and is represented by the solid black line.
+The solid gray line represents the signal distribution, which peaks at a correlation value of 0.96.
+The vertical black dashed line represents a threshold value, 0.438.
+For the simulated UHE-$\nu$ sample, 92\% of CSWs meet or exceed this correlation value when fit to an optimized analytic envelope.
+Assuming the solid black line correctly describes the tail of the probability distribution function for noise correlation, a threshold of 0.438 is equivalent to 0.95 noise events per detector over a period of 5 years, at a noise trigger rate of 1 Hz.
+
+Correlation vs SNR
 \end{itemize}

### 2025-08-15 efficiency.m

@@ -2,7 +2,7 @@ clear;
 close;
 home;
 pkg load optim
-fontsize = 18;
+fontsize = 16;
 markersize = 8;
 signal_linewidth = 3.0;
 noise_linewidth = 1.5;
@@ -14,6 +14,9 @@ bins = bin_min:bin_delta:bin_max;
 n = length(bins);
 [y1,x1] = hist(results(:,8),bins,1);
 [y2,x2] = hist(results(:,5),bins,1);
+[~,pk_index] = max(y2);
+pk_corr = x2(pk_index);
+
 [~,exp_limit_index] = max(y1);
 exp_limit = x1(exp_limit_index)+7*bin_delta;
 exp_limit_index = find(x1>=exp_limit,1);
@@ -35,7 +38,7 @@ while(noise_events>1)
 	signal_efficiency = sum(y2(sig_ll:end));
 	noise_events = 5*365*24*60*60*noise_rate*sum(yfit2(noise_ll:end));
 endwhile
-display([cut_limit signal_efficiency noise_events])
+display([exp_limit pk_corr cut_limit signal_efficiency noise_events])
 
 figure(1);
 hold on;

### 2025-08-16 template.tex
added rho vs. SNR, contour plot needs work

@@
 \end{figure}
+
 \item A Monte Carlo data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume with a depth of 0.65 km and a radius of 0.850 km.
 The UHE-$\nu$ energies ranged from 10-100 PeV, with roughly equal numbers of UHE-$\nu$ in each 10 PeV bin.
-The detector included a single string of 8 RF dipole antennas, a filtered passpand of [80,1000] MHz, and 256 samples per channel at a 1 GHz sampling rate.
+The detector had one string of 8 RF dipole antennas.
+Each RF channel had a filtered, amplified passpand of [80,1000] MHz, with 256 samples per channel at a 1 GHz sampling rate.
 The RF trigger responded when 3 of the 8 voltage traces exceeded $\pm 3$ times the $v_{\rm rms}$ of the thermal noise within 256 ns.
-For each triggered UHE-$\nu$ interaction, the Hilbert envelope of the coherently summed waveform (CSW) was calculated and correlated against Eqs.
+For each signal, the Hilbert envelope of the coherently summed waveform (CSW) was calculated and correlated against Eqs.
 \ref{eq:final}-\ref{eq:final2}.
 A quick optimization over the whole data set yielded 0.15 GHz and 0.025 GHz for the $f_0$ and $\gamma$ parameters, respectively.
-Each individual correlation was maximized by varying the just the $\sigma_t$ parameter, yielding an optimized analytical envelope for each event.
-A thermal noise waveform reflective of the detector properties was also generated using NuRadioMC tools for each UHE-$\nu$ event.
+Each correlation was maximized by varying the just the $\sigma_t$ parameter, yielding an optimized analytical envelope for each event.
+A thermal noise waveform reflective of the channel properties was also generated for each event.
 The noise waveform was also correlated against the optimized analytical envelope.
-The probability distributions for the correlation coefficients are shown in Fig.
+Both correlation distributions are shown in Fig.
 \ref{fig:fig3}.
+
 \begin{figure}
@@
 \end{figure}
+
 In Fig.
 \ref{fig:fig3}, the black circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and the thermal noise waveform.
-A function of the form $x^2 \exp(-0.5 x^2)$ was fit to the black circles on the interval [0.1,1.0], and is represented by the gray dashed line.
-A function of the form $exp(-x)$ was fit to the noise distribution on the interval [0.28,1] to capture the limiting behavior, and is represented by the solid black line.
+Functions of the forms $x^2 \exp(-0.5 x^2)$ and $\exp(-x)$ were fit to the noise distribution on the intervals [0.1,1.0] and [0.28,1], respectively.
+The former is represented by the gray dashed line, and the latter is represented by the solid black line.
 The solid gray line represents the signal distribution, which peaks at a correlation value of 0.96.
-The vertical black dashed line represents a threshold value, 0.438.
-For the simulated UHE-$\nu$ sample, 92\% of CSWs meet or exceed this correlation value when fit to an optimized analytic envelope.
-Assuming the solid black line correctly describes the tail of the probability distribution function for noise correlation, a threshold of 0.438 is equivalent to 0.95 noise events per detector over a period of 5 years, at a noise trigger rate of 1 Hz.
+The vertical black dashed line represents a threshold of 0.438.
+For the simulated UHE-$\nu$, 92\% of correlations between CSWs and optimized analytic envelopes are greater than or equal to this threshold.
+Assuming the solid black line describes the noise distribution tail, with a noise trigger rate of 1 Hz, the threshold is equivalent to 0.95 noise events every 5 years.
 
-Correlation vs SNR
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{Aug15_plot2.png}
+\caption{\label{fig:fig3} Larger font without cutting it off, add noise data}
+\end{figure}
+
 \end{itemize}

### 2025-08-16 rho_vs_snr.m

@@ -1,0 +1,40 @@
+clear;
+close;
+home;
+pkg load statistics
+fontsize = 12;
+markersize = 2;
+signal_linewidth = 3.0;
+noise_linewidth = 1.5;
+results = load('all_results.dat');
+snr = results(:,7);
+rho = results(:,5);
+x_bin_delta = 0.02;
+x_bin_min = 0.0;
+x_bin_max = 5.0;
+y_bin_delta = 0.02;
+y_bin_min = 0.0;
+y_bin_max = 1.0;
+xbins = x_bin_min:x_bin_delta:x_bin_max;
+ybins = y_bin_min:y_bin_delta:y_bin_max;
+contour_min = 0.0;
+contour_max = 0.003;
+contour_delta = 0.0003;
+contours = contour_min:contour_delta:contour_max;
+[h,c] = hist3([snr,rho],{xbins,ybins});
+h/=sum(sum(h));
+
+figure(1);
+contour(c{1}, c{2}, h',contours,'linewidth',signal_linewidth);
+set(gca, 'XScale', 'log');
+axis([1e-1 10 0 1]);
+
+colormap('gray');
+cb = colorbar();
+caxis([contour_min, contour_max]);
+set(cb,'YTick',contours,'fontname','courier','fontsize',fontsize);
+
+set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
+xlabel('Signal to Noise Ratio','fontname','courier','fontsize',fontsize);
+ylabel('Correlation Coefficient','fontname','courier','fontsize',fontsize);
+print('Aug15_plot2.png','-dpng');

### 2025-08-19 template.tex
plot updates, beginning energy recon sec

@@
 \DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\snr}{SNR}
 \begin{document}
@@
 In this work, we present a fully analytic Askaryan model that accounts for the effect of an RF detection channel.
-We provide formulas for the observed voltage trace, and for the Hilbert envelope of the trace.
-We match the equations to data computed with NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
-Our analytic model and NuRadioMC match, with correlation coefficients $>0.95$.
-Using this correlation, UHE-$\nu$ signals can be distinguished from RF backgrounds with an efficiency of xxx.
-Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy with a precision of yyy using a single string of RF channels.
+First, we derive formulas for the observed voltage trace, and for the Hilbert envelope of the trace.
+Second, we match the analytic model to data computed for a detector with a single string of 8 RF detection channels in NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
+Third, we find that a correlation threshold of 0.438 accepts 92\% of UHE-$\nu$ signals, and just 0.95 out of $1.57 \times 10^8$ RF thermal triggers.
+At a thermal trigger rate of 1 Hz, this corresponds to 5 years of continuous operation.
+Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy with a precision of yyy.
 \end{abstract}
@@
 \begin{align}
-a &= c_{\rm em} \sqrt{\ln\Lambda} \\
-a &= c_{\rm had} \sqrt{\ln\Lambda}
+a &= c_{\rm em} \sqrt{\ln\Lambda} \label{eq:em} \\
+a &= c_{\rm had} \sqrt{\ln\Lambda} \label{eq:had}
 \end{align}
@@
 
-\item A Monte Carlo data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume with a depth of 0.65 km and a radius of 0.850 km.
+\item A Monte Carlo data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume with a depth of 0.65 km and a radius of 0.85 km.
 The UHE-$\nu$ energies ranged from 10-100 PeV, with roughly equal numbers of UHE-$\nu$ in each 10 PeV bin.
@@
 In Fig.
-\ref{fig:fig3}, the black circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and the thermal noise waveform.
+\ref{fig:fig3}, the circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and the thermal noise.
 Functions of the forms $x^2 \exp(-0.5 x^2)$ and $\exp(-x)$ were fit to the noise distribution on the intervals [0.1,1.0] and [0.28,1], respectively.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Aug15_plot2.png}
-\caption{\label{fig:fig3} Larger font without cutting it off, add noise data}
+\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{Aug15_plot2.pdf}
+\caption{\label{fig:fig4} The correlation versus SNR (dB) for UHE-$\nu$ signals (upper distribution) and RF thermal noise (lower distribution).
+Color scale: normalized histogram value, with five equally spaced contours between 0.0 and 0.003.}
+\end{figure}
+
+The correlation between the optimized analytical envelope and UHE-$\nu$ signals depends on the signal to noise ratio (SNR).
+Let $v_{\rm pp}$ and $v_{\rm rms}$ represent the peak-to-peak and rms values a voltage traces, respectively.
+The SNR, in decibels, is defined as
+
+\begin{equation}
+\snr_{\rm dB} = 20\log_{10}\left(\frac{1}{2}\frac{v_{\rm pp}}{v_{\rm rms}}\right)
+\end{equation}
+
+In Fig.
+\ref{fig:fig4}, the correlation coefficient is plotted versus the SNR in dB for the data shown in Fig.
+\ref{fig:fig3}.
+The upper distribution corresponds to CSWs from UHE-$\nu$ events, and the flat distribution corresponds to the CSWs from RF thermal noise.
+UHE-$\nu$ events with SNR values $>5$ dB tend to maximize the correlation coefficient, and the correlation coefficient decreases linearly with decreasing SNR (dB).
+As expected, the correlation coefficient for thermal noise does not depend on SNR, since the thermal fluctuations that increase the SNR do not resemble the optimized analytic envelope.
+Note that the SNR of a CSW does not equal the SNR of the individual voltage traces.
+Rather, the individual voltage traces will have SNR values approximately 5-10 dB \textit{lower} than the CSW SNR.
+If $N$ voltage traces contain signal, computing the CSW raises the linear SNR by a factor of $\sqrt{N}$, and adds to the SNR in dB a factor of $20\log_{10}(N)$.
+For an event with 3 of 8 channels containing signal, $20\log_{10}(3)\approx 5$ dB, while $20\log_{10}(8)\approx 9$ dB.
+The exact increase in SNR from traces to CSW depends on how many RF channels contain significant signal.
+
+\item Equations \ref{eq:uncert}-\ref{eq:a_err} are used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy.
+For Eq.
+\ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants, and an assumption must be made for $\Delta\theta$.
+We do not compute $\Delta\theta$ from a single string
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{Aug18_plot1.pdf}
+\caption{\label{fig:fig5} (Black circles) Viewing angle from NuRadioMC.
+(Solid black line) Gaussian fit, with $\mu = 55.6$ deg, and $\sigma = 5.77$ deg.
+(Black dashed line) Cherenkov angle, $\theta_{\rm C}$.}
 \end{figure}

### 2025-08-19 efficiency.m

@@ -50,5 +50,5 @@ plot([cut_limit cut_limit],[1e-9 1],'--','color','#444444','linewidth',signal_li
 axis([0 1 1e-7 1]);
 set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
 xlabel('Correlation coefficient','fontname','courier','fontsize',fontsize);
-ylabel('Probability density','fontname','courier','fontsize',fontsize);
+ylabel('Probability (Normalized)','fontname','courier','fontsize',fontsize);
 print('Aug15_plot1.pdf','-dpdf');

### 2025-08-19 fit_function_3.m

@@ -1,0 +1,4 @@
+function res = fit_function_3(p0,x)
+	xfit = (x-p0(1))./p0(2);
+	res = p0(3).*exp(-0.5*xfit.^2);
+endfunction

### 2025-08-19 rho_vs_snr.m

@@ -2,39 +2,43 @@ clear;
 close;
 home;
 pkg load statistics
-fontsize = 12;
+fontsize = 16;
 markersize = 2;
-signal_linewidth = 3.0;
-noise_linewidth = 1.5;
+signal_linewidth = 4;
+noise_linewidth = 4;
 results = load('all_results.dat');
 snr = results(:,7);
 rho = results(:,5);
+rho_noise = results(:,8);
 x_bin_delta = 0.02;
-x_bin_min = 0.0;
+x_bin_min = 0.02;
 x_bin_max = 5.0;
 y_bin_delta = 0.02;
-y_bin_min = 0.0;
+y_bin_min = 0.02;
 y_bin_max = 1.0;
 xbins = x_bin_min:x_bin_delta:x_bin_max;
 ybins = y_bin_min:y_bin_delta:y_bin_max;
 contour_min = 0.0;
 contour_max = 0.003;
-contour_delta = 0.0003;
+contour_delta = 0.0006;
 contours = contour_min:contour_delta:contour_max;
 [h,c] = hist3([snr,rho],{xbins,ybins});
+[h2,c2] = hist3([snr,rho_noise],{xbins,ybins});
 h/=sum(sum(h));
+h2/=sum(sum(h2));
 
 figure(1);
-contour(c{1}, c{2}, h',contours,'linewidth',signal_linewidth);
-set(gca, 'XScale', 'log');
-axis([1e-1 10 0 1]);
+hold on;
+contour(20*log10(c{1}), c{2}, h',contours,'linewidth',signal_linewidth);
+contour(20*log10(c2{1}), c2{2}, h2',contours,'linewidth',noise_linewidth);
+axis([-5 15 -0.05 1.05]);
 
 colormap('gray');
-cb = colorbar();
+%cb = colorbar();
 caxis([contour_min, contour_max]);
-set(cb,'YTick',contours,'fontname','courier','fontsize',fontsize);
+%set(cb,'YTick',contours,'fontname','courier','fontsize',fontsize,'fontweight','bold');
 
 set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
-xlabel('Signal to Noise Ratio','fontname','courier','fontsize',fontsize);
-ylabel('Correlation Coefficient','fontname','courier','fontsize',fontsize);
-print('Aug15_plot2.png','-dpng');
[…]

### 2025-08-19 viewing_angle.m

@@ -1,0 +1,34 @@
+clear;
+close;
+home;
+pkg load optim
+fontsize = 16;
+markersize = 6;
+linewidth = 1.5;
+results = load('all_results.dat');
+theta = results(:,9)*180.0/pi;
+x_bin_delta = 2.0;
+x_bin_min = 0.0;
+x_bin_max = 90.0;
+xbins = x_bin_min:x_bin_delta:x_bin_max;
+[y1,x1] = hist(theta,xbins,1);
+
+p0 = [60,10,0.33];
+[p1,~] = lsqcurvefit(@fit_function_3,p0,x1,y1);
+xfit = linspace(x_bin_min,x_bin_max,length(xbins)*100);
+yfit = fit_function_3(p1,xfit);
+cAngle = acos(1.0/1.78)*180.0/pi;
+
+figure(1);
+hold on;
+plot(x1,y1,'o','color','black','markersize',markersize);
+plot(xfit,yfit,'-','color','black','linewidth',linewidth);
+axis([-10 90 0.0 0.25]);
+plot([cAngle cAngle],[0 1],'--','color','#444444','linewidth',linewidth)
+legendString = ['\mu: ' num2str(p1(1),3) ' \sigma: ' num2str(p1(2),3)];
+h = legend('NuRadioMC output',legendString,'Cherenkov Angle','location','northwest');
+set(h,'fontname','courier','fontsize',fontsize)
+set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
+xlabel('Viewing Angle (deg)','fontname','courier','fontsize',fontsize);
+ylabel('Probability (Normalized)','fontname','courier','fontsize',fontsize);
+print('Aug18_plot1.pdf','-dpdf');

### 2025-08-19 template.tex
updates on energy derivation

@@
 
-\item Equations \ref{eq:uncert}-\ref{eq:a_err} are used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy.
-For Eq.
-\ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants, and an assumption must be made for $\Delta\theta$.
-We do not compute $\Delta\theta$ from a single string
-
 \begin{figure}
@@
 \end{figure}
+
+\item Equations \ref{eq:uncert}-\ref{eq:a_err} may be used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy, $\ln\Lambda$.
+For Eq.
+\ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants, and an assumption must be made for $\Delta\theta$.
+We will make the assumption that $\Delta\theta \approx \Delta\theta_{\rm rms}$.
+Relying on a single string of RF channels makes calculating $\Delta\theta$ difficult, and geometric event reconstruction usually requires interferometry with multiple strings (cite).
+However, the assumption is justified since the $\Delta\theta$ distribution is Gaussian.
+The MC truth for $\Delta\theta$ in this analysis is shown in Fig.
+\ref{fig:fig5}, with a Gaussian fit ($\mu=55.6$ deg, $\sigma=5.77$ deg).
+The rms and the $\sigma$ parameter are identical for Gaussian distributions, so we assume $\Delta\theta \approx 5.77$ deg.
+The fractional error $\sigma_{\Delta\theta}/\Delta\theta$ is then set to 1.0, reflecting our uncertainty in this parameter.
+Solving Eq.
+\ref{eq:uncert} for $a$ gives
+
+\begin{equation}
+a = \frac{c\sigma_t}{\Delta\theta_{\rm rms} \sin\theta_{\rm C}}
+\end{equation}
+
+The result for the fractional error in $a$ is found by propagating error from $\sigma_t$ and $\Delta\theta$, defined as $\epsilon$ and $\sigma_{\Delta\theta}$, respectively.  The result is
+
+\begin{equation}
+\frac{\sigma_a}{a} = \left(\left(\frac{\epsilon}{\sigma_t}\right)^2 +  \left(\frac{\sigma_{\Delta\theta}}{\Delta\theta}\right)^2\right)^{1/2}
+\end{equation}
+
+The first term is small compared to the second, as it is limited by the scan resolution for $\sigma_t$ in the optimization of the analytic envelope and the number of samples per envelope.
+The scan resolution is set to 50 ps in the optimization, and there are typically $>10$ samples per envelope.
+Thus, the main source of error is $\sigma_{\Delta\theta}$, and
+
+\begin{equation}
+\frac{\sigma_a}{a} = \left|\frac{\sigma_{\Delta\theta}}{\Delta\theta}\right| = \left|\frac{\Delta\theta_{\rm rms}}{\Delta\theta_{\rm rms}}\right|\approx 1
+\end{equation}
+
+Setting the ratio to 1 reflects the idea that the rms is equal to $\sigma$ for a normal distribution.  Inserting this assumption into Eq. \ref{eq:a_err} gives
+
+\begin{equation}
+\frac{\sigma_{\ln\Lambda}}{\ln\Lambda} \approx 2 \label{eq:a_err_2}
+\end{equation}
+
+Using Eqs. \ref{eq:em} and \ref{eq:had}, the logarithm of the energy is
+
+\begin{equation}
+\ln\Lambda = \left( \frac{c\sigma_t}{c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2 \label{eq:lnLambda}
+\end{equation}
+
+The constants $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively, using Eqs.
+10 and 12 from HH (\cite{PhysRevD.105.123019}), at FWHM for the high-energy cascades ($R=0.5$).
+Using Eq.
+\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ CSWs may be used to deduce the UHE-$\nu$ energy distribution.
 

### 2025-08-20 template.tex
updated unit 0 lecture notes, warm ups

@@
 \begin{abstract}
-The detection of ultra-high energy neutrinos (UHE-$\nu$), with enegies above 10 PeV, has been a long-time goal of the astroparticle physics community.
-A key strategy has been to deploy autonomous, radio-frequency (RF) detetectors in polar regions that rely on the Askaryan effect in ice for the neutrino signal.
-The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium, and UHE-$\nu$ can induce such cascades that radiate in the radio-frequency (RF) bandwidth above thermal backgrounds.
+The detection of ultra-high energy neutrinos (UHE-$\nu$), with enegies above 10 PeV, has been a long-time goal in astroparticle physics.
+Autonomous, radio-frequency (RF) UHE-$\nu$ detetectors have been deployed in polar regions.
+These detectors rely on the Askaryan effect in ice for the neutrino signal.
+The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.
+UHE-$\nu$ can induce such cascades that radiate in the RF bandwidth above thermal backgrounds.
 To identify UHE-$\nu$ signals in future data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.
@@
 First, we derive formulas for the observed voltage trace, and for the Hilbert envelope of the trace.
-Second, we match the analytic model to data computed for a detector with a single string of 8 RF detection channels in NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
-Third, we find that a correlation threshold of 0.438 accepts 92\% of UHE-$\nu$ signals, and just 0.95 out of $1.57 \times 10^8$ RF thermal triggers.
+Second, we match the analytic model to data computed for a detector with a single string of eight RF detection channels in NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
+For UHE-$\nu$ signals above RF thermal backgrounds, we find correlation coefficients in excess of $0.95$.
+Third, 92\% of UHE-$\nu$ signals pass a correlation threshold of 0.438, while all but 0.95 out of $1.57 \times 10^8$ RF thermal triggers are rejected.
 At a thermal trigger rate of 1 Hz, this corresponds to 5 years of continuous operation.
-Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy with a precision of yyy.
+Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy.
 \end{abstract}
@@
 
-The constants $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively, using Eqs.
-10 and 12 from HH (\cite{PhysRevD.105.123019}), at FWHM for the high-energy cascades ($R=0.5$).
+Using Eqs.
+10 and 12 from HH (\cite{PhysRevD.105.123019}), $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).
 Using Eq.
 \ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ CSWs may be used to deduce the UHE-$\nu$ energy distribution.
+Two modifications facilitate interpretation.
+First, converting to the base-10 logarithm is more convenient, and this introduces a factor of $\ln(10)$ in the denominator of Eq.
+\ref{eq:lnLambda}.
+Second, $\ln\Lambda = \ln(E_{\rm C}/E_{\rm crit})$, where $E_{\rm C}$ is the energy in the UHE-$\nu$ induced cascade, and $E_{\rm crit}\approx 10^8$ eV is known as the critical energy \cite{PhysRevD.105.123019}.
+Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio simply adds a constant to the right hand side of Eq.
+\ref{eq:lnLambda}.
+The modified form of Eq.
+\ref{eq:lnLambda} is
+
+\begin{equation}
+\log_{10} E_{\rm C} = \frac{\left( \frac{c\sigma_t}{c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2}{\ln 10} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
+\end{equation}
+
+Figure \ref{fig:fig6} contains the $\sigma_t$ distribution, converted into $\log_{10} E_{\rm C}$.
+Note that when applying the change of base formula, factors of $\ln(10)$ cancel in the ratio of Eq.
+\ref{eq:a_err_2}.
+The histogram is spread out over a range much larger than the expected range from NuRadioMC.
+However, the average value of the histogram is $15.7 \pm 4.5$, in agreement with the prediction from NuRadioMC and Eq.
+\ref{eq:a_err_2}: $16.7 \pm 2.0$.
+Thus, the energy reconstruction produces the correct order of magnitude on average, if not the precise value.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 8.25cm,clip=true]{Aug19_plot1.pdf}
+\caption{\label{fig:fig6} Normalized distribution of $\sigma_t$ values, converted to $\log_{10}E_{\rm C}$ via Eq.
+\ref{eq:lnLambda_2}.
+The vertical black line represents the average $\log_{10}E_{\rm C}$ from the NuRadioMC energies, and the shaded region represnts the $1\sigma$ error range using Eq.
+\ref{eq:a_err_2}.}
+\end{figure}
 

### 2025-08-20 energy_distribution.m

@@ -1,0 +1,45 @@
+clear;
+close;
+home;
+fontsize = 16;
+markersize = 6;
+linewidth = 1.5;
+results = load('all_results.dat');
+c = 0.3/1.78;
+sinC = sin(55.8*pi/180.0);
+dTheta = 5.77*pi/180.0;
+sigma = results(:,6);
+cem = 0.825;
+log10E = (c*sigma./cem/dTheta/sinC).^2/log(10.0)+8.0;
+mean_log10E = mean(log10E);
+std_log10E = std(log10E);
+x_bin_delta = 1.0;
+x_bin_min = 8.0;
+x_bin_max = 30.0;
+xbins = x_bin_min:x_bin_delta:x_bin_max;
+[y,x] = hist(log10E,xbins,1);
+
+%Prediction from NuRadioMC, 10, 20, ..., 100 PeV
+m = mean(log10((10:10:100)*10^(15)));
+s = 2;
+shade_delta = x_bin_delta/100.0;
+shade_bins = x_bin_min:shade_delta:x_bin_max;
+region = zeros(size(shade_bins));
+region(find(and(shade_bins>=(m-s),shade_bins<=(m+s)))) = 1;
+
+figure(1);
+hold on;
+bar(x,y,'facecolor','white','edgecolor','black','linewidth',linewidth);
+axis([7 31 0.0 0.25]);
+h = area(shade_bins,region);
+set(h,'facecolor',[0.5 0.5 0.5]);
+set(h,'edgecolor',[0.5 0.5 0.5]);
+set(h,'facealpha',0.2);
+set(h,'edgealpha',0.9);
+plot([m m],[0 1],'-','color','black','linewidth',linewidth);
+labelString = ['mean: ',num2str(mean_log10E,3),' std: ',num2str(std_log10E,3)];
+text(16.0,0.26,labelString,'fontname','courier','fontsize',fontsize)
+set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
+xlabel('log_{10} E_{C}','fontname','courier','fontsize',fontsize);
+ylabel('Probability (Normalized)','fontname','courier','fontsize',fontsize);
+print('Aug19_plot1.pdf','-dpdf');

### 2025-08-28 template.tex
fixed an equation, working on plots

@@
 For UHE-$\nu$ signals above RF thermal backgrounds, we find correlation coefficients in excess of $0.95$.
-Third, 92\% of UHE-$\nu$ signals pass a correlation threshold of 0.438, while all but 0.95 out of $1.57 \times 10^8$ RF thermal triggers are rejected.
+Third, 96.9\% of UHE-$\nu$ signals pass a correlation threshold of 0.386, while all but 0.877 out of $1.57 \times 10^8$ RF thermal triggers are rejected.
 At a thermal trigger rate of 1 Hz, this corresponds to 5 years of continuous operation.
@@
 \end{equation}
-where $w(q)$ is the Faddeeva function.
-Note that the Faddeeva function is \textit{entire}, meaning the $\Re\lbrace \rbrace$ operator and differentiation commute.
-Inserting this result into Eq.
-\ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives
+where $w(q)$ is the Faddeeva function.  Inserting this result into Eq. \ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives
 \begin{multline}
-s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dx} \right)
+s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \Re\left\lbrace xe^{-x^2} w(q) - \frac{1}{2}e^{-x^2} \frac{d w(q)}{dx} \right\rbrace
 \end{multline}
@@
 \begin{multline}
-s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + \left(\frac{j}{2}\right)e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
+s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q) \right\rbrace - \frac{1}{2}e^{-x^2} \Re\left\lbrace -j \frac{d w(q)}{dq} \right\rbrace \right) \label{eq:final3}
 \end{multline}
@@
 The UHE-$\nu$ energies ranged from 10-100 PeV, with roughly equal numbers of UHE-$\nu$ in each 10 PeV bin.
-The detector had one string of 8 RF dipole antennas.
+The detector just a single string of 8 RF dipole antennas.
 Each RF channel had a filtered, amplified passpand of [80,1000] MHz, with 256 samples per channel at a 1 GHz sampling rate.
@@
 (Gray dashed line) Fitting function to noise distribution.
-(Solid black line) Exponential fit to tail of noise distribution.
 (Solid gray line) UHE-$\nu$ signal distribution.
@@
 In Fig.
-\ref{fig:fig3}, the circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and the thermal noise.
-Functions of the forms $x^2 \exp(-0.5 x^2)$ and $\exp(-x)$ were fit to the noise distribution on the intervals [0.1,1.0] and [0.28,1], respectively.
-The former is represented by the gray dashed line, and the latter is represented by the solid black line.
+\ref{fig:fig3}, the circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and thermal noise.
+A fitting function of the form $x^2 \exp(-0.5 x^2)$ was fit to the noise distribution, and is represented by the gray dashed line.
 The solid gray line represents the signal distribution, which peaks at a correlation value of 0.96.
-The vertical black dashed line represents a threshold of 0.438.
-For the simulated UHE-$\nu$, 92\% of correlations between CSWs and optimized analytic envelopes are greater than or equal to this threshold.
-Assuming the solid black line describes the noise distribution tail, with a noise trigger rate of 1 Hz, the threshold is equivalent to 0.95 noise events every 5 years.
+Lower signal correlation values correspond to lower SNR values (Fig.
+\ref{fig:fig4}).
+The vertical black dashed line represents a threshold of 0.386.
+For the simulated UHE-$\nu$, 97\% of correlations between CSWs and optimized analytic envelopes are greater than or equal to this threshold.
+Assuming the gray dashed line describes accurately the noise distribution tail, and assuming a thermal trigger rate of 1 Hz, the correlation threshold is equivalent to 0.88 noise events every 5 years.
 
@@
 \caption{\label{fig:fig4} The correlation versus SNR (dB) for UHE-$\nu$ signals (upper distribution) and RF thermal noise (lower distribution).
-Color scale: normalized histogram value, with five equally spaced contours between 0.0 and 0.003.}
+Color scale: normalized histogram value, with five equally spaced contours between 0.0 and 0.002.}
 \end{figure}
@@
 \ref{fig:fig3}.
-The upper distribution corresponds to CSWs from UHE-$\nu$ events, and the flat distribution corresponds to the CSWs from RF thermal noise.
-UHE-$\nu$ events with SNR values $>5$ dB tend to maximize the correlation coefficient, and the correlation coefficient decreases linearly with decreasing SNR (dB).
-As expected, the correlation coefficient for thermal noise does not depend on SNR, since the thermal fluctuations that increase the SNR do not resemble the optimized analytic envelope.
+The upper and lower distributions correspond to CSWs from UHE-$\nu$ events and thermal noise, respectively.
+A linear relationship between the correlation coefficient for UHE-$\nu$ events and SNR$_{\rm dB}$ is observed, while the correlation coefficient for thermal noise is independent of SNR$_{\rm dB}$.
 Note that the SNR of a CSW does not equal the SNR of the individual voltage traces.

### 2025-08-28 efficiency.m

@@ -6,7 +6,7 @@ fontsize = 16;
 markersize = 8;
 signal_linewidth = 3.0;
 noise_linewidth = 1.5;
-results = load('all_results.dat');
+results = load('all_results_2.dat');
 bin_delta = 0.02;
 bin_min = 0.1;
 bin_max = 1.0;
@@ -18,7 +18,7 @@ n = length(bins);
 pk_corr = x2(pk_index);
 
 [~,exp_limit_index] = max(y1);
-exp_limit = x1(exp_limit_index)+7*bin_delta;
+exp_limit = x1(exp_limit_index)+5*bin_delta;
 exp_limit_index = find(x1>=exp_limit,1);
 p0 = [0.08,0.05,0.05];
 p1 = [exp_limit,0.012];
@@ -28,7 +28,7 @@ xfit = linspace(bin_min,bin_max,length(bins)*100);
 yfit1 = fit_function(p2,xfit);
 yfit2 = fit_function_2(p3,xfit);
 noise_events = 100;
-cut_limit = 0.4;
+cut_limit = 0.25;
 signal_efficiency = 0;
 noise_rate = 1;
 while(noise_events>1)
@@ -36,7 +36,7 @@ while(noise_events>1)
 	sig_ll = find(x2>=cut_limit,1);
 	noise_ll = find(xfit>=cut_limit,1);
 	signal_efficiency = sum(y2(sig_ll:end));
-	noise_events = 5*365*24*60*60*noise_rate*sum(yfit2(noise_ll:end));
+	noise_events = 5*365*24*60*60*noise_rate*sum(yfit1(noise_ll:end));
 endwhile
 display([exp_limit pk_corr cut_limit signal_efficiency noise_events])
 
@@ -44,7 +44,7 @@ figure(1);
 hold on;
 semilogy(x1,y1,'o','color','black','markersize',markersize);
 semilogy(xfit,yfit1,'--','color','#999999','linewidth',noise_linewidth)
-semilogy(xfit,yfit2,'-','color','black','linewidth',noise_linewidth)
+%semilogy(xfit,yfit2,'-','color','black','linewidth',noise_linewidth)
 semilogy(x2,y2,'-','color','#999999','linewidth',signal_linewidth)
 plot([cut_limit cut_limit],[1e-9 1],'--','color','#444444','linewidth',signal_linewidth)
 axis([0 1 1e-7 1]);

### 2025-08-28 energy_distribution.m

@@ -4,11 +4,12 @@ home;
 fontsize = 16;
 markersize = 6;
 linewidth = 1.5;
-results = load('all_results.dat');
+results = load('all_results_2.dat');
 c = 0.3/1.78;
 sinC = sin(55.8*pi/180.0);
 dTheta = 5.77*pi/180.0;
 sigma = results(:,6);
+snr = results(:,7);
 cem = 0.825;
 log10E = (c*sigma./cem/dTheta/sinC).^2/log(10.0)+8.0;
 mean_log10E = mean(log10E);

### 2025-08-28 rho_vs_snr.m

@@ -6,7 +6,7 @@ fontsize = 16;
 markersize = 2;
 signal_linewidth = 4;
 noise_linewidth = 4;
-results = load('all_results.dat');
+results = load('all_results_2.dat');
 snr = results(:,7);
 rho = results(:,5);
 rho_noise = results(:,8);
@@ -19,8 +19,8 @@ y_bin_max = 1.0;
 xbins = x_bin_min:x_bin_delta:x_bin_max;
 ybins = y_bin_min:y_bin_delta:y_bin_max;
 contour_min = 0.0;
-contour_max = 0.003;
-contour_delta = 0.0006;
+contour_max = 0.002;
+contour_delta = 0.0004;
 contours = contour_min:contour_delta:contour_max;
 [h,c] = hist3([snr,rho],{xbins,ybins});
 [h2,c2] = hist3([snr,rho_noise],{xbins,ybins});
@@ -39,6 +39,6 @@ caxis([contour_min, contour_max]);
 %set(cb,'YTick',contours,'fontname','courier','fontsize',fontsize,'fontweight','bold');
 
 set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
-xlabel('SNR (dB)','fontname','courier','fontsize',fontsize,'position',[5 -0.15]);
+xlabel('SNR (dB)','fontname','courier','fontsize',fontsize,'position',[5 -0.18]);
 ylabel('Correlation Coefficient','fontname','courier','fontsize',fontsize,'position',[-8 0.5]);
 print('Aug15_plot2.pdf','-dpdf','-r300');

### 2025-08-28 sigmat_vs_rho.m

@@ -1,0 +1,38 @@
+clear;
+close;
+home;
+pkg load statistics
+fontsize = 16;
+markersize = 2;
+signal_linewidth = 4;
+noise_linewidth = 4;
+results = load('all_results_2.dat');
+rho = results(:,5);
+sigma = results(:,6);
+x_bin_delta = 0.25;
+x_bin_min = 0.0;
+x_bin_max = 5.0;
+y_bin_delta = 0.01;
+y_bin_min = 0.0;
+y_bin_max = 1.0;
+xbins = x_bin_min:x_bin_delta:x_bin_max;
+ybins = y_bin_min:y_bin_delta:y_bin_max;
+contour_min = 0.0;
+contour_max = 0.005;
+contour_delta = 0.001;
+contours = contour_min:contour_delta:contour_max;
+[h,c] = hist3([sigma,rho],{xbins,ybins});
+h/=sum(sum(h));
+
+figure(1);
+hold on;
+contour(c{1}, c{2}, h',contours,'linewidth',signal_linewidth);
+axis([0.0 5.0 0.0 1.0]);
+
+colormap('gray');
+caxis([contour_min, contour_max]);
+
+set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
+xlabel('\sigma_{t} (ns)','fontname','courier','fontsize',fontsize,'position',[2.5 -0.15]);
+ylabel('Correlation Coefficient','fontname','courier','fontsize',fontsize,'position',[-0.75 0.5]);
+print('Aug27_plot2.pdf','-dpdf','-r300');

### 2025-08-28 sigmat_vs_snr.m

@@ -1,0 +1,40 @@
+clear;
+close;
+home;
+pkg load statistics
+fontsize = 16;
+markersize = 2;
+signal_linewidth = 4;
+noise_linewidth = 4;
+results = load('all_results_2.dat');
+snr = results(:,7);
+sigma = results(:,6);
+x_bin_delta = 0.02;
+x_bin_min = 0.02;
+x_bin_max = 5.0;
+y_bin_delta = 0.25;
+y_bin_min = 0.0;
+y_bin_max = 5.0;
+xbins = x_bin_min:x_bin_delta:x_bin_max;
+ybins = y_bin_min:y_bin_delta:y_bin_max;
+contour_min = 0.0;
+contour_max = 0.005;
+contour_delta = 0.001;
+contours = contour_min:contour_delta:contour_max;
+[h,c] = hist3([snr,sigma],{xbins,ybins});
+h/=sum(sum(h));
+
+figure(1);
+hold on;
+contour(20*log10(c{1}), c{2}, h',contours,'linewidth',signal_linewidth);
+axis([-5 15 0.0 5.0]);
+
+colormap('gray');
+%cb = colorbar();
+caxis([contour_min, contour_max]);
+%set(cb,'YTick',contours,'fontname','courier','fontsize',fontsize,'fontweight','bold');
+
+set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
+xlabel('SNR (dB)','fontname','courier','fontsize',fontsize,'position',[5 -0.75]);
+ylabel('\sigma_{t} (ns)','fontname','courier','fontsize',fontsize,'position',[-6.75 2.5]);
+print('Aug27_plot1.pdf','-dpdf','-r300');

### 2025-08-28 viewing_angle.m

@@ -5,7 +5,7 @@ pkg load optim
 fontsize = 16;
 markersize = 6;
 linewidth = 1.5;
-results = load('all_results.dat');
+results = load('all_results_2.dat');
 theta = results(:,9)*180.0/pi;
 x_bin_delta = 2.0;
 x_bin_min = 0.0;

### 2025-08-29 template.tex
fixed a graph and some equations

@@
 From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$, and $dw(q)/dq = -2qw(q)+2j/\sqrt{\pi}$ \cite{NIST:DLMF}.
-The final result is left in terms of the real part of the Faddeeva function, which may be computed using the \textit{Voigt function} $U(x,t)$ \cite{NIST:DLMF,PhysRevD.105.123019}.
+The final result is left in terms of $\Re\lbrace w(q)\rbrace$ and $\Re\lbrace -jdw(q)/dq\rbrace$, which are proportional to the \textit{Voigt functions} \cite{NIST:DLMF,PhysRevD.105.123019}.
 \begin{multline}

### 2025-09-16 template.tex
new efficiency plot, it's wild

@@
 
-\item A Monte Carlo data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume with a depth of 0.65 km and a radius of 0.85 km.
-The UHE-$\nu$ energies ranged from 10-100 PeV, with roughly equal numbers of UHE-$\nu$ in each 10 PeV bin.
-The detector just a single string of 8 RF dipole antennas.
-Each RF channel had a filtered, amplified passpand of [80,1000] MHz, with 256 samples per channel at a 1 GHz sampling rate.
-The RF trigger responded when 3 of the 8 voltage traces exceeded $\pm 3$ times the $v_{\rm rms}$ of the thermal noise within 256 ns.
-For each signal, the Hilbert envelope of the coherently summed waveform (CSW) was calculated and correlated against Eqs.
+\item A data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume (see Tab.
+\ref{tab:1}).
+The 100 PeV interactions included charged and neutral electroweak currents, and the LPM effect.
+The detector was \textit{a single string} of 8 RF dipoles.
+The ice volume had a depth and radius of 0.65 km and 0.85 km, respectively, and the dielectric properties of the South Pole.
+Each RF channel had a filtered, amplified passband of [0.08-1] GHz, and 256 samples at a 1 GHz sampling rate.
+The RF trigger responded when any 3 of the 8 voltage traces exceeded $\pm 3 v_{\rm rms}$ of the thermal noise (233K) within a 256 ns window.
+The Hilbert envelope of the coherently summed waveform (CSW) was calculated from the traces and correlated against Eqs.
 \ref{eq:final}-\ref{eq:final2}.
-A quick optimization over the whole data set yielded 0.15 GHz and 0.025 GHz for the $f_0$ and $\gamma$ parameters, respectively.
-Each correlation was maximized by varying the just the $\sigma_t$ parameter, yielding an optimized analytical envelope for each event.
-A thermal noise waveform reflective of the channel properties was also generated for each event.
-The noise waveform was also correlated against the optimized analytical envelope.
-Both correlation distributions are shown in Fig.
+Each correlation was maximized by varying $\sigma_t$.
+A rough optimization over a noiseless data set yielded 0.15 GHz and 0.025 GHz for the $f_0$ and $\gamma$ parameters, respectively.
+For each signal, a separate thermal noise trace satisfying the RF trigger was generated and correlated against the best-fit analytic envelope.
+The results are shown in Fig.
 \ref{fig:fig3}.
@@
 
+\begin{table}
+\centering
+\begin{tabular}{| c | c | c |}
+\hline
+\textbf{Parameter} & \textbf{Value} & \textbf{Note} \\
+Ice Model & South Pole & 2015 measurements \\
+Signal Model & ARZ2020 & (see \cite{PhysRevD.101.083005}) \\
+Trigger & 3 of 8 channels & high-low trigger at $3v_{\rm rms}$ \\
+RF channels & 8 & RF bicone (in firn) \\
+Noise Temperature & 233K &  \\
+Sampling Rate & 1 GHz &  \\
+Samples per channel & 256 &  \\
+Channel depths & [-4,-6,-8,...-18] m & cable delays included \\
+RF cable type & LMR-400 & \\
+\hline
+\end{tabular}
+\caption{\label{tab:1}}
+\end{table}
+
 In Fig.
@@
 A fitting function of the form $x^2 \exp(-0.5 x^2)$ was fit to the noise distribution, and is represented by the gray dashed line.
-The solid gray line represents the signal distribution, which peaks at a correlation value of 0.96.
+The solid gray line represents the signal distribution, which peaks at a correlation value of 0.94.
 Lower signal correlation values correspond to lower SNR values (Fig.
 \ref{fig:fig4}).
-The vertical black dashed line represents a threshold of 0.386.
-For the simulated UHE-$\nu$, 97\% of correlations between CSWs and optimized analytic envelopes are greater than or equal to this threshold.
-Assuming the gray dashed line describes accurately the noise distribution tail, and assuming a thermal trigger rate of 1 Hz, the correlation threshold is equivalent to 0.88 noise events every 5 years.
+The vertical black dashed line represents a threshold of 0.4.
+For the simulated UHE-$\nu$, 99.99\% of correlations between CSWs and analytic envelopes are greater than or equal to this threshold.
+Assuming the gray dashed line describes accurately the noise distribution, and assuming a thermal trigger rate of 1 Hz, the correlation threshold is equivalent to 0.2 noise events every 5 years.
 

### 2025-09-16 efficiency.m

@@ -6,39 +6,39 @@ fontsize = 16;
 markersize = 8;
 signal_linewidth = 3.0;
 noise_linewidth = 1.5;
-results = load('all_results_2.dat');
+results = load('all_results.dat');
 bin_delta = 0.02;
 bin_min = 0.1;
 bin_max = 1.0;
 bins = bin_min:bin_delta:bin_max;
-n = length(bins);
+jj = find(results(:,6)<10.0);
 [y1,x1] = hist(results(:,8),bins,1);
 [y2,x2] = hist(results(:,5),bins,1);
 [~,pk_index] = max(y2);
 pk_corr = x2(pk_index);
 
-[~,exp_limit_index] = max(y1);
-exp_limit = x1(exp_limit_index)+5*bin_delta;
-exp_limit_index = find(x1>=exp_limit,1);
+%[~,exp_limit_index] = max(y1);
+%exp_limit = x1(exp_limit_index)+5*bin_delta;
+%exp_limit_index = find(x1>=exp_limit,1);
 p0 = [0.08,0.05,0.05];
-p1 = [exp_limit,0.012];
+%p1 = [exp_limit,0.012];
 [p2,~] = lsqcurvefit(@fit_function,p0,x1,y1);
-[p3,~] = lsqcurvefit(@fit_function_2,p1,x1(exp_limit_index:end),y1(exp_limit_index:end));
+%[p3,~] = lsqcurvefit(@fit_function_2,p1,x1(exp_limit_index:end),y1(exp_limit_index:end));
 xfit = linspace(bin_min,bin_max,length(bins)*100);
 yfit1 = fit_function(p2,xfit);
-yfit2 = fit_function_2(p3,xfit);
+%yfit2 = fit_function_2(p3,xfit);
 noise_events = 100;
 cut_limit = 0.25;
 signal_efficiency = 0;
 noise_rate = 1;
 while(noise_events>1)
-	cut_limit += 0.001;
+	cut_limit += 0.01;
 	sig_ll = find(x2>=cut_limit,1);
 	noise_ll = find(xfit>=cut_limit,1);
 	signal_efficiency = sum(y2(sig_ll:end));
 	noise_events = 5*365*24*60*60*noise_rate*sum(yfit1(noise_ll:end));
 endwhile
-display([exp_limit pk_corr cut_limit signal_efficiency noise_events])
+display([pk_corr cut_limit signal_efficiency noise_events])
 
 figure(1);
 hold on;

### 2025-09-18 template.tex
major update to graphs, involving 233K noise run

@@
 The 100 PeV interactions included charged and neutral electroweak currents, and the LPM effect.
+The Askaryan model used to generate the UHE-$\nu$ signals was ARZ2020 \cite{PhysRevD.101.083005}.
+ARZ2020 is a semi-analytic parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the charged particle cascade caused by the UHE-$\nu$ interaction.
+ARZ2020 accounts for sub-cascades and the LPM effect, and it has been validated against MC simulations \cite{zhs,10.1103/physrevd.84.103003}.
+The Askaryan signal model used in NuRadioMC for this analysis was \textit{not} HH2022 \cite{PhysRevD.105.123019}.
+Thus, the correlation between MC output (ARZ2020) and Eqs.
+\ref{eq:final}-\ref{eq:final2} (HH2022 and this work) is physical.
+
 The detector was \textit{a single string} of 8 RF dipoles.
@@
 \ref{fig:fig3}.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{Aug15_plot1.pdf}
-\caption{\label{fig:fig3} (Black circles) Noise distribution.
-(Gray dashed line) Fitting function to noise distribution.
-(Solid gray line) UHE-$\nu$ signal distribution.
-(Dashed black line) Optimized correlation coefficient threshold value.}
-\end{figure}
 
@@
 \end{tabular}
-\caption{\label{tab:1}}
+\caption{\label{tab:1} Important NuRadioMC parameters used in this analysis.}
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{Aug15_plot1.pdf}
+\caption{\label{fig:fig3} (Black circles) Noise distribution.
+(Gray dashed line) Fitting function to noise distribution.
+(Solid gray line) UHE-$\nu$ signal distribution.
+(Dashed black line) Optimized correlation coefficient threshold value.}
+\end{figure}
 
@@
 For the simulated UHE-$\nu$, 99.99\% of correlations between CSWs and analytic envelopes are greater than or equal to this threshold.
-Assuming the gray dashed line describes accurately the noise distribution, and assuming a thermal trigger rate of 1 Hz, the correlation threshold is equivalent to 0.2 noise events every 5 years.
+Assuming a thermal trigger rate of 1 Hz, integrating the PDF of the noise disteribution above the correlation threshold is equivalent to 0.2 noise events every 5 years.
 
@@
 The upper and lower distributions correspond to CSWs from UHE-$\nu$ events and thermal noise, respectively.
-A linear relationship between the correlation coefficient for UHE-$\nu$ events and SNR$_{\rm dB}$ is observed, while the correlation coefficient for thermal noise is independent of SNR$_{\rm dB}$.
+The correlation coefficient for UHE-$\nu$ events is proportional to SNR$_{\rm dB}$, while the correlation coefficient for thermal noise is independent of SNR$_{\rm dB}$.
 Note that the SNR of a CSW does not equal the SNR of the individual voltage traces.
@@
 For an event with 3 of 8 channels containing signal, $20\log_{10}(3)\approx 5$ dB, while $20\log_{10}(8)\approx 9$ dB.
-The exact increase in SNR from traces to CSW depends on how many RF channels contain significant signal.
+The exact increase depends on how many RF channels contain significant signal.
 
@@
 We will make the assumption that $\Delta\theta \approx \Delta\theta_{\rm rms}$.
-Relying on a single string of RF channels makes calculating $\Delta\theta$ difficult, and geometric event reconstruction usually requires interferometry with multiple strings (cite).
+Relying on a single string of RF channels makes calculating $\Delta\theta$ difficult.
 However, the assumption is justified since the $\Delta\theta$ distribution is Gaussian.
@@
 The rms and the $\sigma$ parameter are identical for Gaussian distributions, so we assume $\Delta\theta \approx 5.77$ deg.
-The fractional error $\sigma_{\Delta\theta}/\Delta\theta$ is then set to 1.0, reflecting our uncertainty in this parameter.
+The fractional error $\sigma_{\Delta\theta}/\Delta\theta$ is then set to 1.0, reflecting uncertainty in this parameter.
 Solving Eq.
@@
 
-The first term is small compared to the second, as it is limited by the scan resolution for $\sigma_t$ in the optimization of the analytic envelope and the number of samples per envelope.
-The scan resolution is set to 50 ps in the optimization, and there are typically $>10$ samples per envelope.
-Thus, the main source of error is $\sigma_{\Delta\theta}$, and
+The first term is small compared to the second, as it is limited by the scan resolution for $\sigma_t$ and the number of samples per analytic envelope.
+The scan resolution is set to 0.2 ns in the optimization, and there are typically $>10$ samples per envelope, or about 10 ns.
+Thus, $\left(\epsilon/\sigma_t\right)^2$ is two orders of magnitude smaller than $\left(\sigma_{\Delta\theta}/\Delta\theta\right)^2$, so
 
@@
 Using Eqs.
-10 and 12 from HH (\cite{PhysRevD.105.123019}), $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).
+10 and 12 from HH2022 (\cite{PhysRevD.105.123019}), $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).
 Using Eq.
-\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ CSWs may be used to deduce the UHE-$\nu$ energy distribution.
-Two modifications facilitate interpretation.
-First, converting to the base-10 logarithm is more convenient, and this introduces a factor of $\ln(10)$ in the denominator of Eq.
+\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ CSWs may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.
+First, converting to the base-10 logarithm introduces a factor of $\ln(10)$ in the denominator of Eq.
 \ref{eq:lnLambda}.
-Second, $\ln\Lambda = \ln(E_{\rm C}/E_{\rm crit})$, where $E_{\rm C}$ is the energy in the UHE-$\nu$ induced cascade, and $E_{\rm crit}\approx 10^8$ eV is known as the critical energy \cite{PhysRevD.105.123019}.
-Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio simply adds a constant to the right hand side of Eq.
+Second, $\ln\Lambda = \ln(E_{\rm C}/E_{\rm crit})$, where $E_{\rm C}$ is the cascade energy, and $E_{\rm crit}\approx 10^8$ eV is known as the critical energy \cite{PhysRevD.105.123019}.
+Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio adds a constant to the right hand side of Eq.
 \ref{eq:lnLambda}.

### 2025-09-18 efficiency.m

@@ -44,10 +44,9 @@ figure(1);
 hold on;
 semilogy(x1,y1,'o','color','black','markersize',markersize);
 semilogy(xfit,yfit1,'--','color','#999999','linewidth',noise_linewidth)
-%semilogy(xfit,yfit2,'-','color','black','linewidth',noise_linewidth)
 semilogy(x2,y2,'-','color','#999999','linewidth',signal_linewidth)
 plot([cut_limit cut_limit],[1e-9 1],'--','color','#444444','linewidth',signal_linewidth)
-axis([0 1 1e-7 1]);
+axis([0 1 1e-4 1]);
 set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
 xlabel('Correlation coefficient','fontname','courier','fontsize',fontsize);
 ylabel('Probability (Normalized)','fontname','courier','fontsize',fontsize);

### 2025-09-18 energy_distribution.m

@@ -4,24 +4,24 @@ home;
 fontsize = 16;
 markersize = 6;
 linewidth = 1.5;
-results = load('all_results_2.dat');
+results = load('all_results.dat');
 c = 0.3/1.78;
 sinC = sin(55.8*pi/180.0);
-dTheta = 5.77*pi/180.0;
-sigma = results(:,6);
-snr = results(:,7);
+dTheta = 4.3*pi/180.0;
+jj = find(results(:,6)<3);
+sigma = results(jj,6);
 cem = 0.825;
 log10E = (c*sigma./cem/dTheta/sinC).^2/log(10.0)+8.0;
 mean_log10E = mean(log10E);
 std_log10E = std(log10E);
 x_bin_delta = 1.0;
-x_bin_min = 8.0;
-x_bin_max = 30.0;
+x_bin_min = 10.0;
+x_bin_max = 40.0;
 xbins = x_bin_min:x_bin_delta:x_bin_max;
 [y,x] = hist(log10E,xbins,1);
 
-%Prediction from NuRadioMC, 10, 20, ..., 100 PeV
-m = mean(log10((10:10:100)*10^(15)));
+%Prediction from NuRadioMC, 100 PeV
+m = 17.0;
 s = 2;
 shade_delta = x_bin_delta/100.0;
 shade_bins = x_bin_min:shade_delta:x_bin_max;
@@ -31,7 +31,7 @@ region(find(and(shade_bins>=(m-s),shade_bins<=(m+s)))) = 1;
 figure(1);
 hold on;
 bar(x,y,'facecolor','white','edgecolor','black','linewidth',linewidth);
-axis([7 31 0.0 0.25]);
+axis([10 40 0.0 1]);
 h = area(shade_bins,region);
 set(h,'facecolor',[0.5 0.5 0.5]);
 set(h,'edgecolor',[0.5 0.5 0.5]);

### 2025-09-18 rho_vs_snr.m

@@ -4,9 +4,9 @@ home;
 pkg load statistics
 fontsize = 16;
 markersize = 2;
-signal_linewidth = 4;
-noise_linewidth = 4;
-results = load('all_results_2.dat');
+signal_linewidth = 2;
+noise_linewidth = 2;
+results = load('all_results.dat');
 snr = results(:,7);
 rho = results(:,5);
 rho_noise = results(:,8);
@@ -20,8 +20,8 @@ xbins = x_bin_min:x_bin_delta:x_bin_max;
 ybins = y_bin_min:y_bin_delta:y_bin_max;
 contour_min = 0.0;
 contour_max = 0.002;
-contour_delta = 0.0004;
-contours = contour_min:contour_delta:contour_max;
+contour_delta = 0.0005;
+contours = contour_min:contour_delta:contour_max
 [h,c] = hist3([snr,rho],{xbins,ybins});
 [h2,c2] = hist3([snr,rho_noise],{xbins,ybins});
 h/=sum(sum(h));
@@ -34,9 +34,7 @@ contour(20*log10(c2{1}), c2{2}, h2',contours,'linewidth',noise_linewidth);
 axis([-5 15 -0.05 1.05]);
 
 colormap('gray');
-%cb = colorbar();
 caxis([contour_min, contour_max]);
-%set(cb,'YTick',contours,'fontname','courier','fontsize',fontsize,'fontweight','bold');
 
 set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
 xlabel('SNR (dB)','fontname','courier','fontsize',fontsize,'position',[5 -0.18]);

### 2025-09-18 viewing_angle.m

@@ -5,15 +5,15 @@ pkg load optim
 fontsize = 16;
 markersize = 6;
 linewidth = 1.5;
-results = load('all_results_2.dat');
+results = load('all_results.dat');
 theta = results(:,9)*180.0/pi;
-x_bin_delta = 2.0;
+x_bin_delta = 2;
 x_bin_min = 0.0;
 x_bin_max = 90.0;
 xbins = x_bin_min:x_bin_delta:x_bin_max;
 [y1,x1] = hist(theta,xbins,1);
 
-p0 = [60,10,0.33];
+p0 = [55.8,10,0.33];
 [p1,~] = lsqcurvefit(@fit_function_3,p0,x1,y1);
 xfit = linspace(x_bin_min,x_bin_max,length(xbins)*100);
 yfit = fit_function_3(p1,xfit);
@@ -21,10 +21,10 @@ cAngle = acos(1.0/1.78)*180.0/pi;
 
 figure(1);
 hold on;
-plot(x1,y1,'o','color','black','markersize',markersize);
-plot(xfit,yfit,'-','color','black','linewidth',linewidth);
-axis([-10 90 0.0 0.25]);
-plot([cAngle cAngle],[0 1],'--','color','#444444','linewidth',linewidth)
+semilogy(x1,y1,'o','color','black','markersize',markersize);
+semilogy(xfit,yfit,'-','color','black','linewidth',linewidth);
+axis([0 90 1e-4 10]);
+plot([cAngle cAngle],[1e-4 10],'--','color','#444444','linewidth',linewidth)
 legendString = ['\mu: ' num2str(p1(1),3) ' \sigma: ' num2str(p1(2),3)];
 h = legend('NuRadioMC output',legendString,'Cherenkov Angle','location','northwest');
 set(h,'fontname','courier','fontsize',fontsize)

### 2025-09-18 template.tex
grinding towards the final results in Table III

@@
 Second, we match the analytic model to data computed for a detector with a single string of eight RF detection channels in NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
-For UHE-$\nu$ signals above RF thermal backgrounds, we find correlation coefficients in excess of $0.95$.
-Third, 96.9\% of UHE-$\nu$ signals pass a correlation threshold of 0.386, while all but 0.877 out of $1.57 \times 10^8$ RF thermal triggers are rejected.
-At a thermal trigger rate of 1 Hz, this corresponds to 5 years of continuous operation.
+For UHE-$\nu$ signals, we find correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of 0.4.
+Integrating the normalized PDF of the correlation distribution for RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years of continuous operation at a 1 Hz thermal trigger rate.
 Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy.
@@
 \end{tabular}
-\caption{\label{tab:param} things.}
+\caption{\label{tab:param} Parameters relevant for Eq. \ref{eq:s_full}.}
 \end{table*}
@@
 For the simulated UHE-$\nu$, 99.99\% of correlations between CSWs and analytic envelopes are greater than or equal to this threshold.
-Assuming a thermal trigger rate of 1 Hz, integrating the PDF of the noise disteribution above the correlation threshold is equivalent to 0.2 noise events every 5 years.
+Assuming a thermal trigger rate of 1 Hz, integrating the PDF of the noise distribution above the correlation threshold is equivalent to 0.2 noise events every 5 years.
 
@@
 \caption{\label{fig:fig5} (Black circles) Viewing angle from NuRadioMC.
-(Solid black line) Gaussian fit, with $\mu = 55.6$ deg, and $\sigma = 5.77$ deg.
+(Solid black line) Gaussian fit, with $\mu = 54.8$ deg, and $\sigma = 2.96$ deg.
 (Black dashed line) Cherenkov angle, $\theta_{\rm C}$.}
@@
 We will make the assumption that $\Delta\theta \approx \Delta\theta_{\rm rms}$.
-Relying on a single string of RF channels makes calculating $\Delta\theta$ difficult.
-However, the assumption is justified since the $\Delta\theta$ distribution is Gaussian.
+The assumption is justified since the $\Delta\theta$ distribution is Gaussian.
 The MC truth for $\Delta\theta$ in this analysis is shown in Fig.
-\ref{fig:fig5}, with a Gaussian fit ($\mu=55.6$ deg, $\sigma=5.77$ deg).
-The rms and the $\sigma$ parameter are identical for Gaussian distributions, so we assume $\Delta\theta \approx 5.77$ deg.
+\ref{fig:fig5}, with a Gaussian fit ($\mu=54.8$ deg, $\sigma=2.96$ deg).
+The rms and the $\sigma$ parameter are equal for Gaussian distributions with zero mean, so we let $\Delta\theta \to \Delta \theta_{\rm rms}$.
 The fractional error $\sigma_{\Delta\theta}/\Delta\theta$ is then set to 1.0, reflecting uncertainty in this parameter.
@@
 \begin{equation}
-\log_{10} E_{\rm C} = \frac{\left( \frac{c\sigma_t}{c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2}{\ln 10} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
+\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
 \end{equation}
 
-Figure \ref{fig:fig6} contains the $\sigma_t$ distribution, converted into $\log_{10} E_{\rm C}$.
-Note that when applying the change of base formula, factors of $\ln(10)$ cancel in the ratio of Eq.
-\ref{eq:a_err_2}.
-The histogram is spread out over a range much larger than the expected range from NuRadioMC.
-However, the average value of the histogram is $15.7 \pm 4.5$, in agreement with the prediction from NuRadioMC and Eq.
-\ref{eq:a_err_2}: $16.7 \pm 2.0$.
-Thus, the energy reconstruction produces the correct order of magnitude on average, if not the precise value.
+Table \ref{tab:2} contains the results for the energy reconstruction.
+Note that when applying the change of base formula, factors of $\ln(10)$ cancel in the error ratio of Eq.
+\ref{eq:a_err_2}, so the error in $\log_{10} E_{\rm C}$ remains $2.0$.
 
-\begin{figure}
+\begin{table}
 \centering
-\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 8.25cm,clip=true]{Aug19_plot1.pdf}
-\caption{\label{fig:fig6} Normalized distribution of $\sigma_t$ values, converted to $\log_{10}E_{\rm C}$ via Eq.
-\ref{eq:lnLambda_2}.
-The vertical black line represents the average $\log_{10}E_{\rm C}$ from the NuRadioMC energies, and the shaded region represnts the $1\sigma$ error range using Eq.
-\ref{eq:a_err_2}.}
-\end{figure}
+\begin{tabular}{| c | c |}
+\hline
+\textbf{MC Truth $\log_{10} E_{\rm C}$} & \textbf{Reconstructed $\log_{10} E_{\rm C}$} \\
+17.0 & $17.8 \pm 2.0$ \\
+\hline
+\end{tabular}
+\caption{\label{tab:2}}
+\end{table}
 

### 2025-09-18 energy_distribution.m

@@ -7,40 +7,8 @@ linewidth = 1.5;
 results = load('all_results.dat');
 c = 0.3/1.78;
 sinC = sin(55.8*pi/180.0);
-dTheta = 4.3*pi/180.0;
-jj = find(results(:,6)<3);
-sigma = results(jj,6);
-cem = 0.825;
-log10E = (c*sigma./cem/dTheta/sinC).^2/log(10.0)+8.0;
-mean_log10E = mean(log10E);
-std_log10E = std(log10E);
-x_bin_delta = 1.0;
-x_bin_min = 10.0;
-x_bin_max = 40.0;
-xbins = x_bin_min:x_bin_delta:x_bin_max;
-[y,x] = hist(log10E,xbins,1);
-
-%Prediction from NuRadioMC, 100 PeV
-m = 17.0;
-s = 2;
-shade_delta = x_bin_delta/100.0;
-shade_bins = x_bin_min:shade_delta:x_bin_max;
-region = zeros(size(shade_bins));
-region(find(and(shade_bins>=(m-s),shade_bins<=(m+s)))) = 1;
-
-figure(1);
-hold on;
-bar(x,y,'facecolor','white','edgecolor','black','linewidth',linewidth);
-axis([10 40 0.0 1]);
-h = area(shade_bins,region);
-set(h,'facecolor',[0.5 0.5 0.5]);
-set(h,'edgecolor',[0.5 0.5 0.5]);
-set(h,'facealpha',0.2);
-set(h,'edgealpha',0.9);
-plot([m m],[0 1],'-','color','black','linewidth',linewidth);
-labelString = ['mean: ',num2str(mean_log10E,3),' std: ',num2str(std_log10E,3)];
-text(16.0,0.26,labelString,'fontname','courier','fontsize',fontsize)
-set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
-xlabel('log_{10} E_{C}','fontname','courier','fontsize',fontsize);
-ylabel('Probability (Normalized)','fontname','courier','fontsize',fontsize);
-print('Aug19_plot1.pdf','-dpdf');
+jj = find(and(abs(results(:,9)*180/pi-55.8)>0,results(:,6)<3.0));
+sigma = mean(results(jj,6));
+dTheta = std(results(jj,9)-55.8*pi/180.0);
+cem = 0.8;
+log10E = (c*sigma./cem./dTheta/sinC).^2/log(10.0)+8.0

### 2025-09-18 viewing_angle.m

@@ -7,7 +7,7 @@ markersize = 6;
 linewidth = 1.5;
 results = load('all_results.dat');
 theta = results(:,9)*180.0/pi;
-x_bin_delta = 2;
+x_bin_delta = 2.5;
 x_bin_min = 0.0;
 x_bin_max = 90.0;
 xbins = x_bin_min:x_bin_delta:x_bin_max;
@@ -21,14 +21,13 @@ cAngle = acos(1.0/1.78)*180.0/pi;
 
 figure(1);
 hold on;
-semilogy(x1,y1,'o','color','black','markersize',markersize);
-semilogy(xfit,yfit,'-','color','black','linewidth',linewidth);
-axis([0 90 1e-4 10]);
-plot([cAngle cAngle],[1e-4 10],'--','color','#444444','linewidth',linewidth)
-legendString = ['\mu: ' num2str(p1(1),3) ' \sigma: ' num2str(p1(2),3)];
-h = legend('NuRadioMC output',legendString,'Cherenkov Angle','location','northwest');
+plot(x1-55.8,y1,'o','color','black','markersize',markersize);
+plot(xfit-55.8,yfit,'-','color','black','linewidth',linewidth);
+axis([-30 30 1e-4 0.75]);
+legendString = ['\mu: ' num2str(p1(1)-55.8,3) ' \sigma: ' num2str(p1(2),3)];
+h = legend('NuRadioMC output',legendString,'location','northwest');
 set(h,'fontname','courier','fontsize',fontsize)
 set(gca(),'fontname','courier','fontsize',fontsize,'box','on');
-xlabel('Viewing Angle (deg)','fontname','courier','fontsize',fontsize);
+xlabel('\Delta\theta (deg)','fontname','courier','fontsize',fontsize);
 ylabel('Probability (Normalized)','fontname','courier','fontsize',fontsize);
 print('Aug18_plot1.pdf','-dpdf');

### 2025-09-25 template.tex
finished 100 PeV energy recon table

@@
 Integrating the normalized PDF of the correlation distribution for RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years of continuous operation at a 1 Hz thermal trigger rate.
-Finally, we reconstruct the logarithm of the UHE-$\nu$ cascade energy.
+Finally, we present a preliminary reconstruction of the UHE-$\nu$ cascade energy.
 \end{abstract}
@@
 \caption{\label{fig:fig5} (Black circles) Viewing angle from NuRadioMC.
-(Solid black line) Gaussian fit, with $\mu = 54.8$ deg, and $\sigma = 2.96$ deg.
+(Solid black line) Gaussian fit, with $\mu = -1.05$ deg, and $\sigma = 3.02$ deg.
 (Black dashed line) Cherenkov angle, $\theta_{\rm C}$.}
@@
 The MC truth for $\Delta\theta$ in this analysis is shown in Fig.
-\ref{fig:fig5}, with a Gaussian fit ($\mu=54.8$ deg, $\sigma=2.96$ deg).
+\ref{fig:fig5}, with a Gaussian fit ($\mu=-1.05$ deg, $\sigma=3.02$ deg).
 The rms and the $\sigma$ parameter are equal for Gaussian distributions with zero mean, so we let $\Delta\theta \to \Delta \theta_{\rm rms}$.
@@
 Using Eq.
-\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ CSWs may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.
+\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ signal CSWs may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.
 First, converting to the base-10 logarithm introduces a factor of $\ln(10)$ in the denominator of Eq.
@@
 \ref{eq:lnLambda}.
+Third, let $c_{\rm ave}$ be the average of $c_{\rm em}$ and $c_{\rm had}$, reflecting the unknown hadronic or electromagnetic nature of the cascade.
 The modified form of Eq.
@@
 \begin{equation}
-\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
+\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(c_{\rm ave} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
 \end{equation}
 
-Table \ref{tab:2} contains the results for the energy reconstruction.
+Table \ref{tab:2} contains the preliminary results for the reconstruction of $\log_{10}E_{\rm C}$.
+The results are consistent with the MC truth.
 Note that when applying the change of base formula, factors of $\ln(10)$ cancel in the error ratio of Eq.
 \ref{eq:a_err_2}, so the error in $\log_{10} E_{\rm C}$ remains $2.0$.
+The $sigma_t$ result is the average value of 15133 optimized analytic envelopes fit to signal CSWs generated by 100 PeV UHE-$\nu$ events that triggered the detector.
+Note that the error in the \textit{average} $\sigma_t$ over all events fluctuates due to varying $\Delta\theta$, while the error in \textit{individual} $\sigma_t$ per CSW fit is negligible if the samples per CSW is much greater than 1.
+By far, the largest sources of systematic error are \textit{reflected signals} in the CSWs.
+
+Reflected signals are caused when more than one ray-tracing solution is available between the Askaryan radiation source and the detector.
+Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that first reflect at the snow-air interface, or in the glacial firn, are known as \textit{reflected signals} \cite{}.
+When \textit{direct} and \textit{reflected} signals arrive at the detector at similar times, and one or the other triggers the detector, the recorded waveforms contain direct and reflected signals.
 
@@
 \hline
-\textbf{MC Truth $\log_{10} E_{\rm C}$} & \textbf{Reconstructed $\log_{10} E_{\rm C}$} \\
-17.0 & $17.8 \pm 2.0$ \\
+\textbf{Parameter} & \textbf{Average Value} \\ \hline
+MC Truth, $E_{\rm C}$ [eV] & $10^{17}$ \\
+MC Truth, $\log_{10}E_{\rm C}$ & $17$ \\
+$\sigma_t$ & $1.2 \pm 0.4$ ns \\
+$c_{\rm em,had}$ & 0.86 m \\
+$\Delta\theta_{\rm rms}$ & 3.9 degrees \\
+$E_{\rm crit}$ & 100 MeV \\
+$c$ & $0.3/1.78$ m ns$^{-1}$ \\
+$\sin\theta_{\rm C}$ & 0.8271 \\ \hline
+\textbf{Reconstructed} $\mathbf{\log_{10}E_{\rm C}}$ & $16.5\pm 2.0$ \\
 \hline
 \end{tabular}
-\caption{\label{tab:2}}
+\caption{\label{tab:2} Energy reconstruction parameters used to calculate the logarithm of the UHE-$\nu$ cascade energy, $\log_{10}E_{\rm C}$.}
 \end{table}

### 2025-09-25 energy_distribution.m

@@ -1,14 +1,12 @@
 clear;
 close;
 home;
-fontsize = 16;
-markersize = 6;
-linewidth = 1.5;
-results = load('all_results.dat');
+results = load('all_results_100PeV.dat');
 c = 0.3/1.78;
 sinC = sin(55.8*pi/180.0);
 jj = find(and(abs(results(:,9)*180/pi-55.8)>0,results(:,6)<3.0));
 sigma = mean(results(jj,6));
+sigma_std = std(results(jj,6));
 dTheta = std(results(jj,9)-55.8*pi/180.0);
-cem = 0.8;
+cem = 0.86;
 log10E = (c*sigma./cem./dTheta/sinC).^2/log(10.0)+8.0

### 2025-09-25 viewing_angle.m

@@ -5,9 +5,9 @@ pkg load optim
 fontsize = 16;
 markersize = 6;
 linewidth = 1.5;
-results = load('all_results.dat');
+results = load('all_results_100PeV.dat');
 theta = results(:,9)*180.0/pi;
-x_bin_delta = 2.5;
+x_bin_delta = 2.0;
 x_bin_min = 0.0;
 x_bin_max = 90.0;
 xbins = x_bin_min:x_bin_delta:x_bin_max;
@@ -23,7 +23,7 @@ figure(1);
 hold on;
 plot(x1-55.8,y1,'o','color','black','markersize',markersize);
 plot(xfit-55.8,yfit,'-','color','black','linewidth',linewidth);
-axis([-30 30 1e-4 0.75]);
+axis([-30 30 1e-4 0.5]);
 legendString = ['\mu: ' num2str(p1(1)-55.8,3) ' \sigma: ' num2str(p1(2),3)];
 h = legend('NuRadioMC output',legendString,'location','northwest');
 set(h,'fontname','courier','fontsize',fontsize)

### 2025-09-26 template.tex
added analysis of logE fit, two plots of CSWs

@@
 \ref{eq:a_err_2}, so the error in $\log_{10} E_{\rm C}$ remains $2.0$.
-The $sigma_t$ result is the average value of 15133 optimized analytic envelopes fit to signal CSWs generated by 100 PeV UHE-$\nu$ events that triggered the detector.
+The $\sigma_t$ result is the average value of optimized analytic envelopes fit to signal CSWs generated by 15133 UHE-$\nu$ events that triggered the detector with $E_{\rm C} = 100$ PeV.
 Note that the error in the \textit{average} $\sigma_t$ over all events fluctuates due to varying $\Delta\theta$, while the error in \textit{individual} $\sigma_t$ per CSW fit is negligible if the samples per CSW is much greater than 1.
@@
 Reflected signals are caused when more than one ray-tracing solution is available between the Askaryan radiation source and the detector.
-Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that first reflect at the snow-air interface, or in the glacial firn, are known as \textit{reflected signals} \cite{}.
-When \textit{direct} and \textit{reflected} signals arrive at the detector at similar times, and one or the other triggers the detector, the recorded waveforms contain direct and reflected signals.
+Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that first reflect at the snow-air interface, or in the glacial firn, are known as \textit{reflected signals}.
+Complex RF signal propagation in polar ice has been studied, and even proposed as a UHE-$\nu$ energy reconstruction technique \cite{Barwick:2018497,anker2019neutrino-734}.
+When \textit{direct} and \textit{reflected} signals both arrive at the detector, recorded voltage traces contain both direct and reflected signals.
+The analytic envelope, however, assumes a single pulse.
+Thus, direct and reflected pulses that overlap, or are closely spaced, yield larger $\sigma_t$ values than the average quoted in Tab.
+\ref{tab:2}.
+This effect systematically overestimates the $\log_{10} E_{\rm C}$.
+Two examples are shown in Fig.
+\ref{fig:example_waveforms}: a single-pulse CSW and a CSW containing direct and reflected signals.
 
@@
 MC Truth, $\log_{10}E_{\rm C}$ & $17$ \\
-$\sigma_t$ & $1.2 \pm 0.4$ ns \\
-$c_{\rm em,had}$ & 0.86 m \\
-$\Delta\theta_{\rm rms}$ & 3.9 degrees \\
+$c$ & $0.3/1.78$ m ns$^{-1}$ \\
+$\overline{\sigma_t}$ & $1.229 \pm 0.004$ ns \\
+$c_{\rm ave}$ & 0.86 m \\
+$\Delta\theta_{\rm rms}$ & $3.78\pm0.04$ degrees \\
 $E_{\rm crit}$ & 100 MeV \\
-$c$ & $0.3/1.78$ m ns$^{-1}$ \\
 $\sin\theta_{\rm C}$ & 0.8271 \\ \hline
@@
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{Sept25_plot1.pdf}
+\includegraphics[width=0.5\textwidth]{Sept25_plot2.pdf}
+\caption{\label{fig:example_waveforms} (Top) A single-pulse CSW signal (black dots) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.951$.
+(Bottom) A direct and reflected CSW signal (black dots and thin black line) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.773$.}
+\end{figure}
 

### 2025-09-26 energy_distribution.m

@@ -6,7 +6,6 @@ c = 0.3/1.78;
 sinC = sin(55.8*pi/180.0);
 jj = find(and(abs(results(:,9)*180/pi-55.8)>0,results(:,6)<3.0));
 sigma = mean(results(jj,6));
-sigma_std = std(results(jj,6));
 dTheta = std(results(jj,9)-55.8*pi/180.0);
 cem = 0.86;
 log10E = (c*sigma./cem./dTheta/sinC).^2/log(10.0)+8.0

### 2025-09-26 plot_example_event.m

@@ -1,0 +1,18 @@
+clear;
+close;
+home;
+
+dt = 1; %ns
+
+results = load('example_event_bad.dat');
+[n m] = size(results);
+times = [0:1:n-1]*dt;
+csw = results(:,1);
+model = results(:,2);
+model = circshift(model,[44,0]);
+
+plot(csw)
+hold on
+plot(model)
+
+results = [times' csw model]

### 2025-09-30 template.tex
working on final draft

@@
 UHE-$\nu$ can induce such cascades that radiate in the RF bandwidth above thermal backgrounds.
-To identify UHE-$\nu$ signals in future data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.
-These models have correctly described the Askaryan electromagnetic field, while leaving the effect of the RF detection channels on the field to simulation packages.
-In this work, we present a fully analytic Askaryan model that accounts for the effect of an RF detection channel.
-First, we derive formulas for the observed voltage trace, and for the Hilbert envelope of the trace.
-Second, we match the analytic model to data computed for a detector with a single string of eight RF detection channels in NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
-For UHE-$\nu$ signals, we find correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of 0.4.
-Integrating the normalized PDF of the correlation distribution for RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years of continuous operation at a 1 Hz thermal trigger rate.
-Finally, we present a preliminary reconstruction of the UHE-$\nu$ cascade energy.
+To identify UHE-$\nu$ signals in data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and matched to simulations and laboratory measurements.
+These models have correctly described the Askaryan electromagnetic field, while leaving the effects of attenuation from polar ice propagation and RF detection channels to simulation packages.
+In this work, a fully analytic Askaryan model is that accounts for these effects is presented.
+First, formulas for the observed voltage trace and for the Hilbert envelope of the trace are calculated.
+Second, the analytic model is compared to UHE-$\nu$ signals at 100 PeV from NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
+For UHE-$\nu$ signals, correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of 0.4.
+Integrating the normalized PDF of the correlation distribution for RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years at a 1 Hz thermal trigger rate.
+Finally, we present a preliminary reconstruction of the UHE-$\nu$ cascade energy from a single string of RF channels.
 \end{abstract}
@@
 
-This work is the first application of the Hanson and Hartig (HH) model for the purposes of reconstruction.
+J.
+C.
+Hanson and R.
+Hartig presented the first fully analytic model of the Askaryan field in the time-domain (HH) \cite{PhysRevD.105.123019}.
+When correlated against semi-analytic parameterizations used in NuRadioMC, which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.105.123019}.
+This allows precise reconstruction of UHE-$\nu$ cascade parameters, but is limited to comparisons between the simulated and theoretical electromagnetic field, $\vec{E}$.
+Askaryan-class detectors actually observe voltage traces that represent the RF detection channel response, convolved with $\vec{E}$-fields that have propagated through kilometers of polar ice.
+NuRadioMC accounts for these effects by incorporating measurements from the lab and the field \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.
+
+In this work, we present the first fully analytic model in the time-domain that matches the observed voltage traces.
+In practice, it is common to compute the Hilbert envelope of voltage traces from RF channels before cross-correlating them.
+This is done to remove oscillations introduced by the RF antennas in the channels, which can confuse cross-channel timing and reconstruction.
+Our calculations include both the voltage trace, and the Hilbert envelope of the trace.
+In Sec.
+xxx, we introduce ...
+In Sec.
+yyy, we ...
 
@@
 Assuming a thermal trigger rate of 1 Hz, integrating the PDF of the noise distribution above the correlation threshold is equivalent to 0.2 noise events every 5 years.
+An example CSW fit by the analytic envelope is shown in Fig.
+\ref{fig:example_waveforms}.
 
@@
 Color scale: normalized histogram value, with five equally spaced contours between 0.0 and 0.002.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{Sept25_plot1.pdf}
+\caption{\label{fig:example_waveforms} A single-pulse CSW signal (black dots) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.951$.}
 \end{figure}
@@
 The upper and lower distributions correspond to CSWs from UHE-$\nu$ events and thermal noise, respectively.
+All RF thermal noise events satisfy the station trigger ($\pm 3v_{\rm rms}$ HL threshold).
 The correlation coefficient for UHE-$\nu$ events is proportional to SNR$_{\rm dB}$, while the correlation coefficient for thermal noise is independent of SNR$_{\rm dB}$.
@@
 For an event with 3 of 8 channels containing signal, $20\log_{10}(3)\approx 5$ dB, while $20\log_{10}(8)\approx 9$ dB.
-The exact increase depends on how many RF channels contain significant signal.
+The exact increase depends on how many RF channels contain signal.
 
@@
 This effect systematically overestimates the $\log_{10} E_{\rm C}$.
-Two examples are shown in Fig.
-\ref{fig:example_waveforms}: a single-pulse CSW and a CSW containing direct and reflected signals.
+An example of a CSW event with direct and reflected components fit by an analytic envelope is shown in Fig.
+\ref{fig:example_waveforms_2}.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Sept25_plot1.pdf}
 \includegraphics[width=0.5\textwidth]{Sept25_plot2.pdf}
-\caption{\label{fig:example_waveforms} (Top) A single-pulse CSW signal (black dots) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.951$.
-(Bottom) A direct and reflected CSW signal (black dots and thin black line) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.773$.}
+\caption{\label{fig:example_waveforms_2} A direct and reflected CSW signal (black dots and thin black line) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.773$.}
 \end{figure}

### 2025-10-03 template.tex
writing final draft for submission, start at Sec onc

@@
 To identify UHE-$\nu$ signals in data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and matched to simulations and laboratory measurements.
-These models have correctly described the Askaryan electromagnetic field, while leaving the effects of attenuation from polar ice propagation and RF detection channels to simulation packages.
-In this work, a fully analytic Askaryan model is that accounts for these effects is presented.
-First, formulas for the observed voltage trace and for the Hilbert envelope of the trace are calculated.
+These models have correctly described the Askaryan electromagnetic field, but leave the effects of attenuation from signal propagation through polar ice and RF channel response to simulation packages.
+In this work, a fully analytic Askaryan model that accounts for these effects is presented.
+First, formulas for the observed voltage trace and its Hilbert envelope are calculated.
 Second, the analytic model is compared to UHE-$\nu$ signals at 100 PeV from NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
-For UHE-$\nu$ signals, correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of 0.4.
-Integrating the normalized PDF of the correlation distribution for RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years at a 1 Hz thermal trigger rate.
-Finally, we present a preliminary reconstruction of the UHE-$\nu$ cascade energy from a single string of RF channels.
+Correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of 0.4.
+Analysis of RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years at a 1 Hz thermal trigger rate.
+Finally, we present a preliminary reconstruction of the logarithm of the UHE-$\nu$ cascade energy from a single string of RF channels.
 \end{abstract}
@@
 Cosmic neutrinos with energies up to 100 PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}.
-Previous analyses indicate that the discovery of neutrinos above 5 PeV to 20 EeV will  require large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.
-Neutrinos with energies in the EeV range could potentially reveal the source of ultra-high energy cosmic rays (see sections 3.1-3.3 of \cite{10.48550/arxiv.2008.04323}).
+Previous analyses indicate that the discovery of UHE-$\nu$ flux above 5 PeV requires large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.
+UHE-$\nu$ could reveal the source of ultra-high energy cosmic rays (see sections 3.1-3.3 of \cite{10.48550/arxiv.2008.04323}).
 Further, studying electroweak interactions at these energies is impossible on Earth, and Askaryan-class neutrino detectors provide new data (see section 3.4 of \cite{10.48550/arxiv.2008.04323}).
@@
 Hartig presented the first fully analytic model of the Askaryan field in the time-domain (HH) \cite{PhysRevD.105.123019}.
-When correlated against semi-analytic parameterizations used in NuRadioMC, which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.105.123019}.
-This allows precise reconstruction of UHE-$\nu$ cascade parameters, but is limited to comparisons between the simulated and theoretical electromagnetic field, $\vec{E}$.
+The model builds on earlier work from J.
+C.
+Hanson and A.
+L.
+Connolly (JCH+AC) for spectral filtering due to coherence effects and the form factor of the instantaneous charge distribution (ICD) \cite{10.1016/j.astropartphys.2017.03.008}.
+When correlated against semi-analytic parameterizations used in NuRadioMC (ARHZ2020), which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.101.083005,PhysRevD.105.123019}.
+This allows precise reconstruction of UHE-$\nu$ cascade parameters, but is limited to comparisons between the simulated and theoretical $\vec{E}$-fields.
+
 Askaryan-class detectors actually observe voltage traces that represent the RF detection channel response, convolved with $\vec{E}$-fields that have propagated through kilometers of polar ice.
-NuRadioMC accounts for these effects by incorporating measurements from the lab and the field \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.
-
-In this work, we present the first fully analytic model in the time-domain that matches the observed voltage traces.
+NuRadioMC accounts for these effects by incorporating measurements from years of lab field work \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.
+In this work, we present the first fully analytic Askaryan model in the time-domain that matches the observed voltage traces.
 In practice, it is common to compute the Hilbert envelope of voltage traces from RF channels before cross-correlating them.
@@
 Our calculations include both the voltage trace, and the Hilbert envelope of the trace.
+The work is organized as follows.
+Units, definitions, and notational conventions are given in Sec.
+\ref{sec:unit}.
 In Sec.
-xxx, we introduce ...
+\ref{sec:onc}, the calculations of the observed voltage trace and Hilbert envelope of the trace are given.
+These results are compared to NuRadioMC output in Sec.
+\ref{sec:sim}.
 In Sec.
-yyy, we ...
+\ref{sec:conc}, the key findings are summarized.
 
@@
 
-\begin{itemize}
-\item The result for $\mathcal{E}_{r*s}(t)$, Eqs.
-\ref{eq:final} and \ref{eq:final2}, depends on the model for $s(t)$, Eq.
-\ref{eq:s}.
-Equation \ref{eq:s} is a simplified version of Eq.
-28 in the analysis presented by Hanson and Hartig (HH) \cite{PhysRevD.105.123019}.
-The $E_0$ simply represents all time-independent amplitude factors.
-The full expression for $s(t)$ is
+The analysis is based on two analytic functions: the Askaryan signal, $s(t)$, and the RF channel response, $r(t)$.
+The observed voltage trace in an Askaryan-class detector is $r(t) * s(t)$, the convolution of $r(t)$ and $s(t)$.
+Let $\hat{s}(t)$ represent the Hilbert transform of $s(t)$, and let $j=\sqrt{-1}$.
+The \textit{analytic signal} and \textit{signal envelope} are defined by
+
+\begin{align}
+s_a(t) &= s(t) + j\hat{s}(t) \\
+\mathcal{E}_s(t) &= |s_a(t)|
+\end{align}
+
+The signal envelope actually observed by Askaryan-class detectors is the envelope of $r(t) * s(t)$, written as $\mathcal{E}_{r*s}(t)$.
+The result for $\mathcal{E}_{r*s}(t)$ depends on the model for $s(t)$, taken to be Eq.
+28 in (HH) \cite{PhysRevD.105.123019}:
 \begin{equation}
@@
 \end{equation}
-\begin{table*}
+\begin{table}
 \begin{tabular}{| c | c | c |} \hline
@@
 \caption{\label{tab:param} Parameters relevant for Eq. \ref{eq:s_full}.}
-\end{table*}
+\end{table}
 
@@
 
+The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}.
+The delayed time is $t_{\rm r} = t-r/c$.
+The speed $c$ is equal to the vacuum value, $c_0$, divided by the index of refraction $n$.
+For the RF bandwidth in solid ice, $n=1.78$ and $\theta_{\rm C} = 55.8$ degrees.
+The viewing angle $\theta$ is the zenith angle in spherical coordinates, if the cascade axis is taken to be the z-axis in Cartesian coordinates.
+The Cherenkov angle is a special zenith angle, $\cos\theta_{\rm C} = 1/n$ for relativistic cascade particles.
 The longitudinal cascade length, $a$, is set by the cascade physics.
@@
 In fact, the RB equations are valid when $\eta > 1$.
-Hanson and Connolly (JCH+AC) have shown that $\eta$ corresponds to low-pass filter with cutoff $\omega_{\rm C}$ that limits the RF emissions, $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
+JCH+AC have shown that $\eta$ corresponds to low-pass filter with cutoff $\omega_{\rm C}$ that limits the RF emissions, $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
 JCH+AC also studied $\omega_{\rm C}$ over the frequency and $a$ parameter space, because this parameter space is relevant for the LPM effect.
 
-The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}.
-The delayed time is $t_{\rm r} = t-r/c$.
-The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.
-The value for the RF bandwidth in solid ice ($n=1.78$) is 55.8 degrees.
-More detail on the index of refraction in polar ice is given in \cite{Barwick:2018497,ALLISON201963}.
-The viewing angle $\theta$ is measured relative to the cascade axis, and Askaryan radiation is concentrated for $\theta \approx \theta_{\rm C}$.
-The $n_{\rm max}$ parameter is the maximum excess negative cascade charge, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$.
-
-JCH+AC and Hanson and Hartig (HH) demonstrate how the cutoff frequency $\omega_{\rm 0}$ is related to the instantaneous charge distribution (ICD) and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
-Monte Carlo simulations have shown that the lateral dependence of the ICD is, to first order, exponentially distributed \cite{zhs,PhysRevD.105.123019}.
-In JCH+AC, characterizing the lateral component of the ICD as $\exp(-\sqrt{2\pi}\rho_0 \rho)$ led to an elegant expression for the ICD form factor, $\widetilde{F}(\omega)$.
-
-Hanson and Hartig (HH) have shown that the parameter $p$ is related to $\sigma_t$ \cite{PhysRevD.105.123019}:
+The $n_{\rm max}$ parameter is the maximum excess negative cascade charge, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.
+JCH+AC and HH demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the instantaneous charge distribution (ICD) and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
+Monte Carlo simulations have shown that the lateral dependence of the ICD is, to first order, exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.
+JCH+AC derived a closed form for the ICD form factor, $\widetilde{F}(\omega)$, by modeling the lateral component of the ICD as $\exp(-\sqrt{2\pi}\rho_0 \rho)$.
+Finally, HH have shown that the parameter $p$ is related to $\sigma_t$, the Gaussian pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
 
@@
 Let $E_{\rm C}/E_{\rm crit} = \Lambda$.
-Assuming the Greisen and Gaisser-Hillas parameterizaions for electromagnetic and hadronic cascades, respectively, HH found the relationship
+Assuming the Greisen and Gaisser-Hillas parameterizaions for electromagnetic and hadronic cascades, respectively, HH found the following relationships for the $a$-values from electromagentically dominated and hadronically dominated cascades:
 
 \begin{align}
-a &= c_{\rm em} \sqrt{\ln\Lambda} \label{eq:em} \\
-a &= c_{\rm had} \sqrt{\ln\Lambda} \label{eq:had}
+a_{\rm em} &= c_{\rm em} \sqrt{\ln\Lambda} \label{eq:em} \\
+a_{\rm had} &= c_{\rm had} \sqrt{\ln\Lambda} \label{eq:had}
 \end{align}
+
+From Eq. \ref{eq:uncert}, the fractional error in $\ln\Lambda$ is:
 
@@
 42 in \cite{PhysRevD.105.123019}, and has been corrected for units.
-Equations \ref{eq:pulse_width}-\ref{eq:a_err} imply measurements of $a$ and $\Delta\theta$ lead to a measurement of the logarithm of the cascade energy $\ln\Lambda$, and that the relative error in $\ln\Lambda$ is proportional to the relative error in $a$.
-\end{itemize}
+Equations \ref{eq:pulse_width}-\ref{eq:a_err} imply measurements of $a$ and $\Delta\theta$ yield $\ln\Lambda$, and that the relative error in $\ln\Lambda$ is proportional to the relative error in $a$.
 
@@
 
-Here is a list of the basic results and ideas for this paper.
-
-\begin{itemize}
-\item Let the signal model $s(t)$ be
+The parameters in Eq. \ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the essential time-dependence.  Let the signal model $s(t)$ be
 \begin{equation}
@@
 This is the off-cone field equation from \cite{PhysRevD.105.123019}.
-The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: the longitudinal length of the UHE-$\nu$-induced cascade, and the angle at which the cascade is observed relative to the Cherenkov angle.
-The parameter $E_0$ is the amplitude normalization, and it depends on two parameters: $\sigma_{\rm t}$, and $\omega_{\rm 0}$, the cutoff frequency from the cascade form factor.
-In Sec.
-\ref{sec:onc}, $E_0$ and $\sigma_t$ will be treated as constants, since neither depends on time.
-\item Let $\widehat{s}(t)$ represent the Hilbert transform of $s(t)$.  The \textit{analytic signal} of $s(t)$ is
+The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: $a$ and $\Delta\theta$.
+The parameter $E_0$ is the amplitude normalization, and the dependencies on other parameters can be determined from Eq.
+\ref{eq:s_full} and Tab.
+\ref{tab:param}.
+The \textit{analytic signal} of $s(t)$ is
 \begin{equation}
@@
 The Hilbert transform $\widehat{s}(t)$ is equivalent to the convolution of $s(t)$ and the tempered distribution $h(t) = 1/(\pi t)$.
-\item Let $S(f)$ be the Fourier transform of $s(t)$.  The Fourier transform of the analytic signal is
+ Let $S(f)$ be the Fourier transform of $s(t)$.  The Fourier transform of the analytic signal is
 \begin{equation}
@@
 The sign function, $\sgn$ gives $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$.
-\item Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
+ Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
 \begin{equation}
@@
 \end{equation}
-\item The Fourier transform of Eq. \ref{eq:s} is
+ The Fourier transform of Eq. \ref{eq:s} is
 \begin{equation}
@@
 \end{equation}
-\item Using the gaussian spectral width $\sigma_{\rm f}$ from \cite{10.1016/j.astropartphys.2017.03.008}, and the guassian width of $s(t)$ from \cite{PhysRevD.105.123019}, it was shown in \cite{PhysRevD.105.123019} that the uncertainty principle holds for off-cone signals:
+ Using the gaussian spectral width $\sigma_{\rm f}$ from \cite{10.1016/j.astropartphys.2017.03.008}, and the guassian width of $s(t)$ from \cite{PhysRevD.105.123019}, it was shown in \cite{PhysRevD.105.123019} that the uncertainty principle holds for off-cone signals:
 \begin{equation}
@@
 \end{equation}
-\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f\right)^2$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
+ Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f\right)^2$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
 \begin{align}
@@
 \end{equation}
-\item The overall analytic signal, $s_a(t)$, is
+ The overall analytic signal, $s_a(t)$, is
 \begin{equation}
@@
 Note that $s_a(0) \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.
-\item Signal data in detectors designed to observe Askaryan pulses is equivalent to the convolution of the signal and detector response functions.
+ Signal data in detectors designed to observe Askaryan pulses is equivalent to the convolution of the signal and detector response functions.
 Signal models are convolved with measured detector responses to create \textit{signal templates}.
@@
 The RLC damped oscillator is a standard circuit model for the RF dipole antennas used in RNO-G and the proposed IceCube Gen2 \cite{10.1103/PhysRevD.85.062004,10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
-\item There are two paths to calculating the final result.
+ There are two paths to calculating the final result.
 The first option involves three steps.
@@
 The second option involves computing the envelope of the convolution of $r(t)$ with $s(t)$ directly from $s_a(t)$ and $r_a(t)$.
-\item Let $s(t) * r(t)$ represent the convolution of $s(t)$ and $r(t)$.
-Let the envelope of the convolution be $\mathcal{E}_{s * r}(t)$.
-$\mathcal{E}_{s * r}(t)$, $s_a(t)$, and $r_a(t)$ are related by
+ Let $s(t) * r(t)$ represent the convolution of $s(t)$ and $r(t)$.  Let the envelope of the convolution be $\mathcal{E}_{s * r}(t)$.  $\mathcal{E}_{s * r}(t)$, $s_a(t)$, and $r_a(t)$ are related by
 \begin{equation}
@@
 \end{equation}
-\item Assume that a signal arrives in an RLC damped oscillator at $t=0$.  For $t\geq 0$, the impulse response and corresponding analytic signal are
+ Assume that a signal arrives in an RLC damped oscillator at $t=0$.  For $t\geq 0$, the impulse response and corresponding analytic signal are
 \begin{align}
@@
 (Check the sign of time here, to ensure that it is positive).
-\item The goal is now to apply Eq.
+ The goal is now to apply Eq.
 \ref{eq:awesome} by convolving $s_a(t)$ with $r_a(t)$.
@@
 \end{multline}
-\item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$,
+ Turning to the convolution of $r_a(t)$ with $\Im(s_a)$,
 \begin{multline}
@@
 Though a closed analytic form for $\mathcal{L}\lbrace D(u-x)\rbrace_k$ is elusive, finishing this calculation through numerical integration is straightforward.
-\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$, since
+ Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$, since
 \begin{equation}
@@
 \end{equation}
-\item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
+ It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
 \begin{equation}
@@
 \end{multline}
-\item To illustrate the accuracy of the model, Eqs. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
+ To illustrate the accuracy of the model, Eqs. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
 \begin{figure}[ht]
@@
 \end{figure}
-\item To demonstrate that \textit{numerical convolution} of $s(t)$ and $r(t)$ produces the same results as the \textit{mathematical convolution} of $s(t)$ and $r(t)$ (Eq.
+ To demonstrate that \textit{numerical convolution} of $s(t)$ and $r(t)$ produces the same results as the \textit{mathematical convolution} of $s(t)$ and $r(t)$ (Eq.
 \ref{eq:final3}), the corresponding waveforms are shown in Fig.
@@
 
+\section{Comparison between Analytic Calculations and NuRadioMC}
+\label{sec:sim}
+
+\begin{itemize}
 \item A data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume (see Tab.

### 2025-10-03 template.tex
continuing to write words

@@
 \ref{tab:param}.
-The \textit{analytic signal} of $s(t)$ is
-\begin{equation}
-s_{\rm a}(t) = s(t) + j \widehat{s}(t)
-\end{equation}
-The magnitude of the analytic signal, $|s_a(t)|$, is the \textit{envelope} of the signal.
 The Hilbert transform $\widehat{s}(t)$ is equivalent to the convolution of $s(t)$ and the tempered distribution $h(t) = 1/(\pi t)$.
- Let $S(f)$ be the Fourier transform of $s(t)$.  The Fourier transform of the analytic signal is
+The implication in the Fourier domain is that the negative frequencies in the spectrum of $\hat{s}(t)$ vanish, while the positive ones are doubled.
+Let the $\sgn(f)$ be $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$, and let $S(f)$ be the Fourier transform of $s(t)$.
+The Fourier transform $S_a(f)$ of the analytic signal $s_a(t)$ is
 \begin{equation}
@@
 \end{equation}
-The sign function, $\sgn$ gives $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$.
- Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
+Thus, if $f<0$, $S_a(f) = 0$, and $S_a(f) = 2S(f)$ if $f\geq 0$.  Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
 \begin{equation}
@@
 \end{equation}
-The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$} \cite{NIST:DLMF}:
+The imaginary part of $I$ is proportional to the \textit{Dawson function, $D(x)$} \cite{NIST:DLMF}:
 \begin{equation}
@@
 \end{equation}
-The signal envelope is $|s_a(t)|$.
-It is important to note that, though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.
-Note that $s_a(0) \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.
- Signal data in detectors designed to observe Askaryan pulses is equivalent to the convolution of the signal and detector response functions.
-Signal models are convolved with measured detector responses to create \textit{signal templates}.
+The envelope of the signal, $\mathcal{E}_s(t)$, is the magnitude of Eq.
+\ref{eq:sa_4}.
+Though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.
+As expected for $\mathcal{E}_s(t)$, $|s_a(0)| \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.
+Rather, $|s_a(0)| \propto \sigma_t$.
+
+Observed signals in Askaryan-class detectors is essentially the convolution of the signal and detector response functions.
+TO generate \textit{signal templates}, signal models are convolved with measured RF channel responses to create \textit{signal templates}.
+Signal templates are further refined by accounting for frequency-dependent attenuation due to propagation through polar ice \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214}.
 Signal templates are cross-correlated with observed data to identify UHE-$\nu$ signals.
-The oscillations of signal templates and observed data can introduce various uncertainties when cross-correlated.
+xxxyyyzzz
+
+Oscillations within signal templates and observed data are often introduced by the RF channel response, and can introduce various uncertainties when cross-correlated.
 This problem intensifies when the signal-to-noise ratio between Askaryan pulse data and thermal noise decreases.

### 2025-10-04 template.tex
worked on writing

@@
 
-Observed signals in Askaryan-class detectors is essentially the convolution of the signal and detector response functions.
-TO generate \textit{signal templates}, signal models are convolved with measured RF channel responses to create \textit{signal templates}.
-Signal templates are further refined by accounting for frequency-dependent attenuation due to propagation through polar ice \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214}.
+The observed data in Askaryan-class detectors is essentially the convolution of the UHE-$\nu$ signal from the ice and the detector response function.
+To generate \textit{signal templates}, Askaryan radiation signals are calculated for the UHE-$\nu$ interaction properties, modified by the frequency-dependent RF attenuation of polar ice, and convolved with the RF channel response \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214}.
 Signal templates are cross-correlated with observed data to identify UHE-$\nu$ signals.
-xxxyyyzzz
+RF detection channels based on RF dipole antennas, however, have resonance frequencies that introduce oscillations not present in the original signal.
+The oscillations can introduce timing uncertainties.
+The problem intensifies when the signal-to-noise ratio (SNR) relative to RF thermal noise decreases.
 
-Oscillations within signal templates and observed data are often introduced by the RF channel response, and can introduce various uncertainties when cross-correlated.
-This problem intensifies when the signal-to-noise ratio between Askaryan pulse data and thermal noise decreases.
-To reduce these uncertainties, the Hilbert envelope of observed signals is used in cross-correlations instead of the original signals.
-We seek an analytic equation for the Hilbert envelope of the data.
-That is, we seek the envelope of the convolution of the analytic signal model with a typical detector response.
-The RLC damped oscillator is a standard circuit model for the RF dipole antennas used in RNO-G and the proposed IceCube Gen2 \cite{10.1103/PhysRevD.85.062004,10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
- There are two paths to calculating the final result.
-The first option involves three steps.
+To reduce uncertainties, the Hilbert envelope of observed data is used in cross-correlations instead of the original signals.
+Thus, an analytic prediction for the Hilbert envelope of the observed data would an effective signal template.
+An assumption must be made, however, for the RF channel response.
+The RLC damped oscillator is a suitable circuit model for the RF dipole antennas used in RICE, RNO-G, and the proposed IceCube Gen2 \cite{10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
+In fact, an RLC response was first used by RICE at the South Pole a decade ago \cite{10.1103/PhysRevD.85.062004}.
+
+There are two paths to calculating the final result, $\mathcal{E}_{r*s}(t)$.
+The first involves three steps.
 First, the detector response, $r(t)$ is convolved with $s(t)$.
@@
 Third, the magnitude of the analytic signal is computed, which can be compared to envelopes of observed signals.
-The second option involves computing the envelope of the convolution of $r(t)$ with $s(t)$ directly from $s_a(t)$ and $r_a(t)$.
- Let $s(t) * r(t)$ represent the convolution of $s(t)$ and $r(t)$.  Let the envelope of the convolution be $\mathcal{E}_{s * r}(t)$.  $\mathcal{E}_{s * r}(t)$, $s_a(t)$, and $r_a(t)$ are related by
+The second path involves computing $\mathcal{E}_{r*s}(t)$ directly from $s_a(t)$ and $r_a(t)$.
+The second option is more straightforward, once a special theorem relating $r_a(t)$, $s_a(t)$, and $\mathcal{E}_{r*s}(t)$ is established.
+$\mathcal{E}_{s * r}(t)$, $s_a(t)$, and $r_a(t)$ are related by
 \begin{equation}
@@
 \end{equation}
+
 The proof of Eq.
@@
 \end{equation}
+
 Assume that a signal arrives in an RLC damped oscillator at $t=0$.  For $t\geq 0$, the impulse response and corresponding analytic signal are
 \begin{align}
-r(t) &= R_0 e^{-2 \pi \gamma_f t} \cos(2\pi f_0 t) \label{eq:r} \\
-r_a(t) &= R_0 e^{-2 \pi \gamma_f t} e^{2\pi j f_0 t} \label{eq:ra}
+r(t) &= R_0 e^{-2 \pi \gamma t} \cos(2\pi f_0 t) \label{eq:r} \\
+r_a(t) &= R_0 e^{-2 \pi \gamma t} e^{2\pi j f_0 t} \label{eq:ra}
 \end{align}
-The parameters $\gamma_f$ and $f_0$ are the \textit{decay constant} that corresponds to the \textit{fall time} of the output signal, and the resonance frequency.
-Note that the envelope of $r(t)$, $|r_a(t)|$, is $R_0 \exp(-2 \pi \gamma_f t)$, as expected.
+The parameters $\gamma$ and $f_0$ are the decay constant and the resonance frequency.
+Note that the envelope of $r(t)$, $|r_a(t)|$, is $R_0 \exp(-2 \pi \gamma t)$, as expected.
 To prove Eq.
@@
 R(f) &= \frac{R_0}{4\pi j} \left( \frac{1}{f - z_{+}} + \frac{1}{1- z_{-}} \right) \\
-z_{+} &= f_0 + j \gamma_f \\
-z_{-} &= -f_0 + j \gamma_f
+z_{+} &= f_0 + j \gamma \\
+z_{-} &= -f_0 + j \gamma
 \end{align}
 Given Eq.
-\ref{eq:sa_2}, the procedure to find $r_a(t)$ is to multiply the \textit{negative} frequency components by 0 and the \textit{positive} frequency components by 2, and take the inverse Fourier transform.
-The inverse Fourier transform may be completed by extension to the complex plane using the upper infinite semi-circle as a contour, and applying Jordan's lemma.
-The residue from the pole at $z_{+}$ drives the final result.
-(Check the sign of time here, to ensure that it is positive).
+\ref{eq:sa_2}, the procedure to find $r_a(t)$ is to multiply the \textit{negative} frequency component at $z_{-}$ by 0 and the \textit{positive} frequency component at $z_{+}$ by 2, and take the inverse Fourier transform.
+The inverse Fourier transform may be completed by applying Jordan's lemma in the complex plane frequency plane.
+The residue from the pole at $z_{+}$ yields the result.
+
 The goal is now to apply Eq.
@@
 \end{multline}
-Note that the units for the convolution of $r(t)$ and $s(t)$ correspond to $R_0 E_0 \sigma_t^2$.  Let $u = x-y$, so that $du = -dy$. The result is
+Note that the units for the convolution of $r(t)$ and $s(t)$ are $R_0 E_0 \sigma_t^2$.  Let $u = x-y$, so that $du = -dy$. The result is
 \begin{equation}
@@
 \end{multline}
+
 Turning to the convolution of $r_a(t)$ with $\Im(s_a)$,
@@
 \end{multline}
-Accounting for the step function in the convolution gives
+The convolution becomes
 \begin{multline}
@@
 \end{multline}
-Using the fundamental theorem of calculus, and the limiting cases of $D(x)$, 
+Using Leibniz rule for the fundamental theorem of calculus, and the limiting cases of $D(x)$, 
 \begin{multline}
@@
 The remaining integral is the Laplace transform of the shifted Dawson function, $\mathcal{L}\lbrace D(u-x)\rbrace_k$.  The final result is
-\begin{equation}
+\begin{multline}
 r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right) \label{eq:Im_result}
-\end{equation}
-Though a closed analytic form for $\mathcal{L}\lbrace D(u-x)\rbrace_k$ is elusive, finishing this calculation through numerical integration is straightforward.
- Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$, since
-\begin{equation}
-r_a(t) * s_a(t) = r_a(t) * \Re\lbrace s_a(t)\rbrace + j r_a(t) * \Im\lbrace s_a(t)\rbrace
-\end{equation}
-which yields
+\end{multline}
+Though a closed analytic form for $\mathcal{L}\lbrace D(u-x)\rbrace_k$ is elusive, evaluating $\mathcal{L}\lbrace D(u-x)\rbrace_k$ numerically is fast and precise.
+
+Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:
 \begin{multline}
@@
 \end{equation}
- It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
+
+xxyyzz It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
 \begin{equation}

### 2025-10-06 template.tex
further editing the text to make concise

@@
 The detection of ultra-high energy neutrinos (UHE-$\nu$), with enegies above 10 PeV, has been a long-time goal in astroparticle physics.
-Autonomous, radio-frequency (RF) UHE-$\nu$ detetectors have been deployed in polar regions.
-These detectors rely on the Askaryan effect in ice for the neutrino signal.
-The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.
-UHE-$\nu$ can induce such cascades that radiate in the RF bandwidth above thermal backgrounds.
+Autonomous, radio-frequency (RF) UHE-$\nu$ detetectors have been deployed in polar regions that rely on the Askaryan effect in ice for the neutrino signal.
+The Askaryan effect occurs when the excess negative charge within a UHE-$\nu$ cascade radiates in a dense medium.
+UHE-$\nu$ can induce cascades that radiate in the RF bandwidth above thermal backgrounds.
 To identify UHE-$\nu$ signals in data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and matched to simulations and laboratory measurements.
-These models have correctly described the Askaryan electromagnetic field, but leave the effects of attenuation from signal propagation through polar ice and RF channel response to simulation packages.
+These models describe the Askaryan electromagnetic field, but leave the effects of signal propagation through polar ice and RF channel response to simulations.
 In this work, a fully analytic Askaryan model that accounts for these effects is presented.
 First, formulas for the observed voltage trace and its Hilbert envelope are calculated.
-Second, the analytic model is compared to UHE-$\nu$ signals at 100 PeV from NuRadioMC, a key Monte Carlo toolset in UHE-$\nu$ detection.
-Correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of 0.4.
-Analysis of RF thermal noise reveals that just 0.2 thermal background events pass the correlation threshold in 5 years at a 1 Hz thermal trigger rate.
+Second, the analytic model is compared to UHE-$\nu$ signals at 100 PeV from NuRadioMC, a key Monte Carlo toolset in the field.
+Correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of $\rho=0.4$.
+Analysis of RF thermal noise reveals that just 0.2 background events have $\rho\geq 0.4$ in 5 years at a 1 Hz thermal trigger rate.
 Finally, we present a preliminary reconstruction of the logarithm of the UHE-$\nu$ cascade energy from a single string of RF channels.
@@
 \section{Introduction}
+\label{sec:int}
 
@@
 Hanson and R.
-Hartig presented the first fully analytic model of the Askaryan field in the time-domain (HH) \cite{PhysRevD.105.123019}.
+Hartig presented the first fully analytic model of the Askaryan field in the time-domain (HH2022) \cite{PhysRevD.105.123019}.
 The model builds on earlier work from J.
@@
 Connolly (JCH+AC) for spectral filtering due to coherence effects and the form factor of the instantaneous charge distribution (ICD) \cite{10.1016/j.astropartphys.2017.03.008}.
-When correlated against semi-analytic parameterizations used in NuRadioMC (ARHZ2020), which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.101.083005,PhysRevD.105.123019}.
+When correlated against semi-analytic parameterizations used in NuRadioMC (ARHZ2020), which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH2022 model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.101.083005,PhysRevD.105.123019}.
 This allows precise reconstruction of UHE-$\nu$ cascade parameters, but is limited to comparisons between the simulated and theoretical $\vec{E}$-fields.
@@
 The result for $\mathcal{E}_{r*s}(t)$ depends on the model for $s(t)$, taken to be Eq.
-28 in (HH) \cite{PhysRevD.105.123019}:
+28 in HH2022 \cite{PhysRevD.105.123019}:
 \begin{equation}
@@
 The delayed time is $t_{\rm r} = t-r/c$.
-The speed $c$ is equal to the vacuum value, $c_0$, divided by the index of refraction $n$.
-For the RF bandwidth in solid ice, $n=1.78$ and $\theta_{\rm C} = 55.8$ degrees.
-The viewing angle $\theta$ is the zenith angle in spherical coordinates, if the cascade axis is taken to be the z-axis in Cartesian coordinates.
-The Cherenkov angle is a special zenith angle, $\cos\theta_{\rm C} = 1/n$ for relativistic cascade particles.
+The speed $c$ is equal to the vacuum value, divided by the index of refraction $n$.
+For RF in ice, $n=1.78$ and $\theta_{\rm C} = 55.8$ degrees.
+The viewing angle $\theta$ is the zenith angle in spherical coordinates, if the cascade axis is the z-axis.
+The Cherenkov angle is $\cos\theta_{\rm C} = 1/n$ for relativistic cascades.
 The longitudinal cascade length, $a$, is set by the cascade physics.
-The ratio $\eta = (a/\Delta z_{\rm coh})^2$ corresponds to the far-field limit as $\eta \to 0$, but this is not a requirement of the RB model.
-In fact, the RB equations are valid when $\eta > 1$.
-JCH+AC have shown that $\eta$ corresponds to low-pass filter with cutoff $\omega_{\rm C}$ that limits the RF emissions, $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
-JCH+AC also studied $\omega_{\rm C}$ over the frequency and $a$ parameter space, because this parameter space is relevant for the LPM effect.
+The ratio $\eta = (a/\Delta z_{\rm coh})^2$ corresponds to the far-field limit as $\eta \to 0$, but $\eta \to 0$ is not a requirement.
+JCH+AC found that $\eta$ corresponds to a low-pass filter for the RF spectrum with cutoff frequency $\omega_{\rm C}$: $\eta = \omega/\omega_{\rm C}$ \cite{10.1016/j.astropartphys.2017.03.008}.
 
 The $n_{\rm max}$ parameter is the maximum excess negative cascade charge, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.
-JCH+AC and HH demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the instantaneous charge distribution (ICD) and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
-Monte Carlo simulations have shown that the lateral dependence of the ICD is, to first order, exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.
-JCH+AC derived a closed form for the ICD form factor, $\widetilde{F}(\omega)$, by modeling the lateral component of the ICD as $\exp(-\sqrt{2\pi}\rho_0 \rho)$.
-Finally, HH have shown that the parameter $p$ is related to $\sigma_t$, the Gaussian pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
+JCH+AC and HH2022 demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the instantaneous charge distribution (ICD) and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
+Monte Carlo simulations have shown that the lateral dependence of the ICD is exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.
+JCH+AC derived the ICD form factor, $\widetilde{F}(\omega)$, by modeling the lateral component of the ICD as an exponential distribution.
+Finally, the authors of HH2022 have shown that the parameter $p$ is related to $\sigma_t$, the Gaussian pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
 
@@
 
-The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta=(\theta-\theta_{\rm C})$, $p \propto \Delta\theta^2$ to second order, and
+The authors of HH2022 have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta=(\theta-\theta_{\rm C})$, $p \propto \Delta\theta^2$ to second order, and
 
@@
 III of \cite{10.1103/physrevd.65.016003}.
-HH analyzed the relationship between $a$, the cascade energy $E_{\rm C}$ and the critical energy $E_{\rm crit}$ for electromagnetic and hadronic cascades \cite{PhysRevD.105.123019}.
+The authors of HH2022 analyzed the relationship between $a$, the cascade energy $E_{\rm C}$ and the critical energy $E_{\rm crit}$ for electromagnetic and hadronic cascades \cite{PhysRevD.105.123019}.
 Let $E_{\rm C}/E_{\rm crit} = \Lambda$.
-Assuming the Greisen and Gaisser-Hillas parameterizaions for electromagnetic and hadronic cascades, respectively, HH found the following relationships for the $a$-values from electromagentically dominated and hadronically dominated cascades:
+Assuming the Greisen and Gaisser-Hillas parameterizaions for electromagnetic and hadronic cascades, respectively, the following relationships for the $a$-values from electromagentically dominated and hadronically dominated cascades were found:
 
@@
 \end{align}
-
-From Eq. \ref{eq:uncert}, the fractional error in $\ln\Lambda$ is:
+\noindent
+The values for $c_{\rm em}$ and $c_{\rm had}$ are calculated in Sec. \ref{sec:recon}. From Eq. \ref{eq:uncert}, the fractional error in $\ln\Lambda$ is:
 
@@
 \end{equation}
-
+\noindent
 Equation \ref{eq:a_err} corresponds to Eq.
@@
 
-\section{Collection of Main Results}
+\section{Calculation of the Main Results}
 \label{sec:onc}
 
-The parameters in Eq. \ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the essential time-dependence.  Let the signal model $s(t)$ be
+The parameters in Eq. \ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the time-dependence.  Let the signal model $s(t)$ be
 \begin{equation}
@@
 \end{equation}
-This is the off-cone field equation from \cite{PhysRevD.105.123019}.
+This is the \textit{off-cone} equation from \cite{PhysRevD.105.123019}.
 The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: $a$ and $\Delta\theta$.
@@
 Let the $\sgn(f)$ be $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$, and let $S(f)$ be the Fourier transform of $s(t)$.
-The Fourier transform $S_a(f)$ of the analytic signal $s_a(t)$ is
+The Fourier transform of the analytic signal $s_a(t)$ is
 \begin{equation}
@@
 Though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.
-As expected for $\mathcal{E}_s(t)$, $|s_a(0)| \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.
-Rather, $|s_a(0)| \propto \sigma_t$.
+As expected, $|s_a(0)| \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.
 
-The observed data in Askaryan-class detectors is essentially the convolution of the UHE-$\nu$ signal from the ice and the detector response function.
+The observed data in Askaryan-class detectors is the convolution of the UHE-$\nu$ signal from the ice and the detector response function.
 To generate \textit{signal templates}, Askaryan radiation signals are calculated for the UHE-$\nu$ interaction properties, modified by the frequency-dependent RF attenuation of polar ice, and convolved with the RF channel response \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214}.
@@
 
-xxyyzz It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
+To model the full time-dependent voltage trace from detection channels, and not merely the envelope, $s(t) * r(t)$ is required.
+The calculation may be done analytically, starting with the definition of convolution:
 \begin{equation}
-s * r = \int_{-\infty}^{\infty} s(t-\tau) r(\tau) d\tau 
+s(t) * r(t) = \int_{-\infty}^{\infty} s(t-\tau) r(\tau) d\tau 
 \end{equation}
-Inserting the definitions of $s(t)$ and $r(t)$,
+As in the calculation of $\mathcal{E}_{r*s}(t)$, the Heaviside step function, $u(t)$ is included to ensure causality.  Inserting the definitions of $s(t)$, $r(t)$, and $u(t)$ gives
 \begin{multline}
@@
 \end{equation}
-As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re\lbrace s_a(t)\rbrace$, the result for $I(x,z)$ is
+Let $b=x+\frac{1}{2}z$, and $b = j q$.  The calculation resembles that of $r_a(t) * \Re\lbrace s_a(t)\rbrace$.  The result for $I(x,z)$ is
 \begin{equation}
@@
 \end{equation}
-where $w(q)$ is the Faddeeva function.  Inserting this result into Eq. \ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives
+Inserting this result into Eq. \ref{eq:conv_sr}, gives
 \begin{multline}
@@
 \end{multline}
- To illustrate the accuracy of the model, Eqs. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
+
+To illustrate the accuracy of the model, the \textit{numerically-computed envelope} of Eq.
+\ref{eq:final3} is compared to Eqs.
+\ref{eq:final}-\ref{eq:final2} in Fig.
+\ref{fig:fig1}.
+The \textit{numerical convolution} of $s(t)$ and $r(t)$ is compared to Eq.
+\ref{eq:final3} in Fig.
+\ref{fig:fig2}.
 \begin{figure}[ht]
@@
 \end{figure}
- To demonstrate that \textit{numerical convolution} of $s(t)$ and $r(t)$ produces the same results as the \textit{mathematical convolution} of $s(t)$ and $r(t)$ (Eq.
-\ref{eq:final3}), the corresponding waveforms are shown in Fig.
-\ref{fig:fig2}.
 \begin{figure}[ht]
@@
 
-\begin{itemize}
-\item A data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume (see Tab.
+NuRadioMC was used to generate UHE-$\nu$ interactions in a cylindrical ice volume (see Tab.
 \ref{tab:1}).
 The 100 PeV interactions included charged and neutral electroweak currents, and the LPM effect.
-The Askaryan model used to generate the UHE-$\nu$ signals was ARZ2020 \cite{PhysRevD.101.083005}.
-ARZ2020 is a semi-analytic parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the charged particle cascade caused by the UHE-$\nu$ interaction.
+The Askaryan model used in NuRadioMC was ARZ2020 \cite{PhysRevD.101.083005}.
+ARZ2020 is a \textit{semi-analytic} parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the net charge in the UHE-$\nu$ cascade.
 ARZ2020 accounts for sub-cascades and the LPM effect, and it has been validated against MC simulations \cite{zhs,10.1103/physrevd.84.103003}.
@@
 Thus, the correlation between MC output (ARZ2020) and Eqs.
-\ref{eq:final}-\ref{eq:final2} (HH2022 and this work) is physical.
+\ref{eq:final}-\ref{eq:final2} (HH2022 and this work) is solely on physical grounds.
 
-The detector was \textit{a single string} of 8 RF dipoles.
-The ice volume had a depth and radius of 0.65 km and 0.85 km, respectively, and the dielectric properties of the South Pole.
-Each RF channel had a filtered, amplified passband of [0.08-1] GHz, and 256 samples at a 1 GHz sampling rate.
-The RF trigger responded when any 3 of the 8 voltage traces exceeded $\pm 3 v_{\rm rms}$ of the thermal noise (233K) within a 256 ns window.
-The Hilbert envelope of the coherently summed waveform (CSW) was calculated from the traces and correlated against Eqs.
+The detector was \textit{a single string} of 8 RF dipoles, each with the same (x,y)-coordinates and regularly-spaced z-coordinates.
+The ice had a depth and radius of 0.65 km and 0.85 km, respectively, and the dielectric properties of the South Pole.
+Each RF channel had a filtered, amplified passband of [0.08-1] GHz, 256 samples, and a 1 GHz sampling rate.
+The RF trigger responded when any 3 of the 8 voltage traces exceeded $\pm 3$ times the rms voltage ($v_{\rm rms}$) of the thermal noise (233K) within 256 ns.
+The Hilbert envelope of the coherently summed waveform (CSW) was calculated from the traces and cross-correlated with Eqs.
 \ref{eq:final}-\ref{eq:final2}.
 Each correlation was maximized by varying $\sigma_t$.
-A rough optimization over a noiseless data set yielded 0.15 GHz and 0.025 GHz for the $f_0$ and $\gamma$ parameters, respectively.
-For each signal, a separate thermal noise trace satisfying the RF trigger was generated and correlated against the best-fit analytic envelope.
+An optimization using noiseless data (3K) yielded 0.15 GHz and 0.025 GHz for $f_0$ and $\gamma$, respectively.
+For each signal, a thermal noise trace satisfying the RF trigger was generated and cross-correlated against the best-fit analytic envelope.
 The results are shown in Fig.
@@
 \begin{table}
+\small
 \centering
@@
 Signal Model & ARZ2020 & (see \cite{PhysRevD.101.083005}) \\
-Trigger & 3 of 8 channels & high-low trigger at $3v_{\rm rms}$ \\
+Trigger & 3 of 8 channels & high-low trigger, $3v_{\rm rms}$ \\
 RF channels & 8 & RF bicone (in firn) \\
-Noise Temperature & 233K &  \\
-Sampling Rate & 1 GHz &  \\
+Channel filters & [80-1000] MHz & Passband \\
+Noise Temperature & 233K & Sets $v_{\rm rms}$ \\
+Sampling Rate & 1 GHz & $f_{\rm c} = 500$ MHz \\
 Samples per channel & 256 &  \\
 Channel depths & [-4,-6,-8,...-18] m & cable delays included \\
-RF cable type & LMR-400 & \\
+RF cable type & LMR-400 & $<0.0886$ dB m$^{-1}$ \\
 \hline
@@
 (Solid gray line) UHE-$\nu$ signal distribution.
-(Dashed black line) Optimized correlation coefficient threshold value.}
+(Dashed black line) Correlation threshold.}
 \end{figure}
@@
 The vertical black dashed line represents a threshold of 0.4.
-For the simulated UHE-$\nu$, 99.99\% of correlations between CSWs and analytic envelopes are greater than or equal to this threshold.
+For the simulated UHE-$\nu$, 99.99\% of correlations exceed this threshold.
 Assuming a thermal trigger rate of 1 Hz, integrating the PDF of the noise distribution above the correlation threshold is equivalent to 0.2 noise events every 5 years.
@@
 The correlation between the optimized analytical envelope and UHE-$\nu$ signals depends on the signal to noise ratio (SNR).
-Let $v_{\rm pp}$ and $v_{\rm rms}$ represent the peak-to-peak and rms values a voltage traces, respectively.
-The SNR, in decibels, is defined as
+Let $v_{\rm pp}$ represent the peak-to-peak value in the voltage trace.
+The SNR (dB) is
 
@@
 The upper and lower distributions correspond to CSWs from UHE-$\nu$ events and thermal noise, respectively.
-All RF thermal noise events satisfy the station trigger ($\pm 3v_{\rm rms}$ HL threshold).
-The correlation coefficient for UHE-$\nu$ events is proportional to SNR$_{\rm dB}$, while the correlation coefficient for thermal noise is independent of SNR$_{\rm dB}$.
-Note that the SNR of a CSW does not equal the SNR of the individual voltage traces.
-Rather, the individual voltage traces will have SNR values approximately 5-10 dB \textit{lower} than the CSW SNR.
-If $N$ voltage traces contain signal, computing the CSW raises the linear SNR by a factor of $\sqrt{N}$, and adds to the SNR in dB a factor of $20\log_{10}(N)$.
-For an event with 3 of 8 channels containing signal, $20\log_{10}(3)\approx 5$ dB, while $20\log_{10}(8)\approx 9$ dB.
-The exact increase depends on how many RF channels contain signal.
+All RF thermal noise events satisfy the station trigger.
+Note that the correlation coefficient for UHE-$\nu$ events is proportional to SNR$_{\rm dB}$.
+The SNR of a CSW does not equal the SNR of the individual voltage traces.
+Rather, the voltage traces will have SNRs 5-9 dB \textit{lower} than the CSW.
+If $N$ voltage traces contain signal, computing the CSW raises the linear SNR by a factor of $\sqrt{N}$, and adds $10\log_{10}(N)$ to SNR$_{\rm dB}$.
+For an event with 3 of 8 channels containing signal, $10\log_{10}(3)\approx 5$ dB, while $10\log_{10}(8)\approx 9$ dB.
 
@@
 
-\item Equations \ref{eq:uncert}-\ref{eq:a_err} may be used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy, $\ln\Lambda$.
+\section{Reconstruction of $\log_{10}E_{\rm C}$}
+\label{sec:recon}
+
+Equations \ref{eq:uncert}-\ref{eq:a_err} may be used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy, $\ln\Lambda$.
 For Eq.
-\ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants, and an assumption must be made for $\Delta\theta$.
+\ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants.
+Without a separate fit for $\Delta\theta$ an assumption must be made.
 We will make the assumption that $\Delta\theta \approx \Delta\theta_{\rm rms}$.
@@
 The MC truth for $\Delta\theta$ in this analysis is shown in Fig.
-\ref{fig:fig5}, with a Gaussian fit ($\mu=-1.05$ deg, $\sigma=3.02$ deg).
-The rms and the $\sigma$ parameter are equal for Gaussian distributions with zero mean, so we let $\Delta\theta \to \Delta \theta_{\rm rms}$.
-The fractional error $\sigma_{\Delta\theta}/\Delta\theta$ is then set to 1.0, reflecting uncertainty in this parameter.
+\ref{fig:fig5}, with a Gaussian fit.
+The rms and $\sigma$ values are equal for normal distributions, so we let $\Delta\theta \approx \Delta \theta_{\rm rms}$ and set the fractional error $\sigma_{\Delta\theta}/\Delta\theta$ to 1.0.
 Solving Eq.
@@
 \begin{equation}
-\frac{\sigma_a}{a} = \left(\left(\frac{\epsilon}{\sigma_t}\right)^2 +  \left(\frac{\sigma_{\Delta\theta}}{\Delta\theta}\right)^2\right)^{1/2}
+\frac{\sigma_a}{a} = \left(\left(\frac{\epsilon}{\sigma_t}\right)^2 +  \left(\frac{\sigma_{\Delta\theta}}{\Delta\theta}\right)^2\right)^{1/2} \label{eq:err_prop}
 \end{equation}
@@
 
-Setting the ratio to 1 reflects the idea that the rms is equal to $\sigma$ for a normal distribution.  Inserting this assumption into Eq. \ref{eq:a_err} gives
+Setting the ratio to 1 is a conservative assumption for $\ln\Lambda$, for inserting it into Eq. \ref{eq:a_err} gives
 
@@
 Using Eq.
-\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ signal CSWs may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.
+\ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ signals may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.
 First, converting to the base-10 logarithm introduces a factor of $\ln(10)$ in the denominator of Eq.
@@
 Second, $\ln\Lambda = \ln(E_{\rm C}/E_{\rm crit})$, where $E_{\rm C}$ is the cascade energy, and $E_{\rm crit}\approx 10^8$ eV is known as the critical energy \cite{PhysRevD.105.123019}.
-Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio adds a constant to the right hand side of Eq.
+Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio adds $\log_{10} E_{\rm crit}$ to the right hand side of Eq.
 \ref{eq:lnLambda}.
@@
 
-Table \ref{tab:2} contains the preliminary results for the reconstruction of $\log_{10}E_{\rm C}$.
+Table \ref{tab:2} contains the results for the reconstruction of $\log_{10}E_{\rm C}$.
 The results are consistent with the MC truth.
@@
 \ref{eq:a_err_2}, so the error in $\log_{10} E_{\rm C}$ remains $2.0$.
-The $\sigma_t$ result is the average value of optimized analytic envelopes fit to signal CSWs generated by 15133 UHE-$\nu$ events that triggered the detector with $E_{\rm C} = 100$ PeV.
-Note that the error in the \textit{average} $\sigma_t$ over all events fluctuates due to varying $\Delta\theta$, while the error in \textit{individual} $\sigma_t$ per CSW fit is negligible if the samples per CSW is much greater than 1.
-By far, the largest sources of systematic error are \textit{reflected signals} in the CSWs.
+The $\sigma_t$ result is the average value derived from 15133 UHE-$\nu$ events that triggered the detector with $E_{\rm C} = 100$ PeV.
+Note that the error in the \textit{average} $\sigma_t$ over all events fluctuates due to varying $\Delta\theta$, while the error in \textit{individual} $\sigma_t$ per CSW is small if the samples per CSW is much greater than 1.
+By far, the largest source of systematic error is \textit{reflected signals}.
 
-Reflected signals are caused when more than one ray-tracing solution is available between the Askaryan radiation source and the detector.
-Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that first reflect at the snow-air interface, or in the glacial firn, are known as \textit{reflected signals}.
-Complex RF signal propagation in polar ice has been studied, and even proposed as a UHE-$\nu$ energy reconstruction technique \cite{Barwick:2018497,anker2019neutrino-734}.
-When \textit{direct} and \textit{reflected} signals both arrive at the detector, recorded voltage traces contain both direct and reflected signals.
-The analytic envelope, however, assumes a single pulse.
-Thus, direct and reflected pulses that overlap, or are closely spaced, yield larger $\sigma_t$ values than the average quoted in Tab.
+Multiple signals occur within traces either when signals from two ray-tracing paths are available, or when part of the signal reflects from the surface back to the channel.
+Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that reflect at the snow-air interface are known as \textit{reflected signals}.
+Complex RF signal propagation in polar ice has been studied, and even proposed as a UHE-$\nu$ energy reconstruction technique \cite{Barwick:2018497,anker2019neutrino-734,deaconu2018measurements-182}.
+When two signals are present in the voltage trace, the fitting algorithm favors $\sigma_t$ values that are unphysically larger than the average quoted in Tab.
 \ref{tab:2}.
-This effect systematically overestimates the $\log_{10} E_{\rm C}$.
+This systematically overestimates $\log_{10} E_{\rm C}$.
 An example of a CSW event with direct and reflected components fit by an analytic envelope is shown in Fig.
@@
 
-\begin{table}
+\begin{table}[hb]
 \centering
@@
 \includegraphics[width=0.5\textwidth]{Sept25_plot2.pdf}
-\caption{\label{fig:example_waveforms_2} A direct and reflected CSW signal (black dots and thin black line) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.773$.}
+\caption{\label{fig:example_waveforms_2} A CSW signal with a reflection (black dots and thin black line) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line), with $\rho = 0.773$.}
 \end{figure}
-
-\end{itemize}
 
@@
 
-The conclusion.
+In Secs.
+\ref{sec:int} and ref{sec:unit}, previous work in the utility of analytic Askaryan models was reviewed, and important parameters were defined.
+In Sec.
+\ref{sec:onc}, a fully analytic model for $\mathcal{E}_{\rm s*r}(t)$ and $s(t) * r(t)$ was presented and checked for accuracy.
+In Sec.
+\ref{sec:sim}, the analytic model was shown to reject all but 0.2 RF thermal triggers in a 5 year run at a 1 Hz thermal trigger rate using a correlation threshold of 0.4.
+That same threshold preserves 99.99\% of UHE-$\nu$ signals at 100 PeV.
+The correlation distribution for UHE-$\nu$ signals peaked at 0.94, and some values even exceed 0.94.
+Finally, in Sec.
+\ref{sec:recon}, a first attempt at using the CSW fit with data \textit{a single-string detector} to reconstruct $\log_{10}E_{\rm C}$ was presented.
+Though the error range for $\log_{10}E_{\rm C}$ is large, the average value is correct: $\log_{10}E_{\rm C} = 16.5 \pm 2.0$ for 100 PeV.
 
-\appendix
+There are three logical steps for this work in the future.
+First, we must account for multiple pulses in the algorithm used to fit the analytic envelope to CSWs from NuRadioMC.
+The authors of \cite{anker2019neutrino-734} have shown how direct and reflected (DnR) signals may be used to constrain the UHE-$\nu$ energy.
+This procedure should be combined with the analytic envelope fit to advance UHE-$\nu$ energy reconstruction.
+Though this is not difficult to implement in NuRadioMC, it was beyond the scope of this work.
 
-\section{Details}
-\label{app:a}
+Second, we should be able to incorporate a separate fit for $\Delta\theta$.
+This parameter may be constrained by using the spectral cutoff, which is inversely correlated to $\Delta\theta$ \cite{10.1016/j.astropartphys.2017.03.008}.
+With a separate fit for $\Delta\theta$, the $a$-value could be constrained without making any assumption about $\Delta\theta$.
+This step would improve the precision of the $a$-value by lowering the fractional error in $a$-values in Eq.
+\ref{eq:err_prop}.
 
-The details.
+Third, it is interesting to note that the entire model relies on the \textit{off-cone} ($\theta \neq \theta_{\rm C}$) version of $s(t)$.
+HH2022 also includes an \textit{on-cone} version of $s(t)$ that is used when $\Delta\theta \lesssim 1$ degree.
+The on-cone model could provide a better fit between $\mathcal{E}_{\rm s*r}(t)$ for events with $\Delta\theta \lesssim 1$ degree.
+
+We would like to thank Prof.
+Steve Barwick, and Prof.
+Mark Kozek for useful background discussions.
+We are grateful to the authors of RB, Prof.
+John Ralston and Roman Buniy, for inspiring us in this line of research \cite{10.1103/physrevd.65.016003}.
+We would like to thank Prof.
+Dave Besson for encouragement and wisdom while we continued to develop the model.
+Most of all, we would like to thank Prof.
+Amy Connolly for inspiring us and encouraging us to master more advanced applications of complex analysis to mathematical physics.
+It is our hope that the model will one day help to identify the first UHE-$\nu$ measured via the Askaryan effect.
 

### 2025-10-07 template.tex
minor changes ... time to print

@@
 The RLC damped oscillator is a suitable circuit model for the RF dipole antennas used in RICE, RNO-G, and the proposed IceCube Gen2 \cite{10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
-In fact, an RLC response was first used by RICE at the South Pole a decade ago \cite{10.1103/PhysRevD.85.062004}.
+In fact, an RLC response was first used by RICE at the South Pole \cite{10.1103/PhysRevD.85.062004}.
 
@@
 Each RF channel had a filtered, amplified passband of [0.08-1] GHz, 256 samples, and a 1 GHz sampling rate.
-The RF trigger responded when any 3 of the 8 voltage traces exceeded $\pm 3$ times the rms voltage ($v_{\rm rms}$) of the thermal noise (233K) within 256 ns.
+The RF trigger responded when any 3 of the 8 voltage traces exceeded $+3$ times \textit{and} $-3$ times the rms voltage ($v_{\rm rms}$) of the thermal noise ($T=233$ K) within 256 ns (256 samples).
 The Hilbert envelope of the coherently summed waveform (CSW) was calculated from the traces and cross-correlated with Eqs.
@@
 Signal Model & ARZ2020 & (see \cite{PhysRevD.101.083005}) \\
-Trigger & 3 of 8 channels & high-low trigger, $3v_{\rm rms}$ \\
+Trigger & 3 of 8 channels & $\pm 3v_{\rm rms}$ \\
 RF channels & 8 & RF bicone (in firn) \\
@@
 Sampling Rate & 1 GHz & $f_{\rm c} = 500$ MHz \\
-Samples per channel & 256 &  \\
+Samples per channel & 256 & total time, $256$ ns \\
 Channel depths & [-4,-6,-8,...-18] m & cable delays included \\
@@
 In Secs.
-\ref{sec:int} and ref{sec:unit}, previous work in the utility of analytic Askaryan models was reviewed, and important parameters were defined.
+\ref{sec:int} and \ref{sec:unit}, previous work in the utility of analytic Askaryan models was reviewed, and important parameters were defined.
 In Sec.
@@
 In Sec.
-\ref{sec:sim}, the analytic model was shown to reject all but 0.2 RF thermal triggers in a 5 year run at a 1 Hz thermal trigger rate using a correlation threshold of 0.4.
-That same threshold preserves 99.99\% of UHE-$\nu$ signals at 100 PeV.
+\ref{sec:sim}, the analytic model was shown to reject all but 0.2 RF thermal triggers in a 5 year run at a 1 Hz thermal trigger rate using a correlation threshold of $\rho\geq 0.4$.
+The threshold $\rho\geq 0.4$ preserves 99.99\% of UHE-$\nu$ signals at 100 PeV.
 The correlation distribution for UHE-$\nu$ signals peaked at 0.94, and some values even exceed 0.94.
@@
 \ref{sec:recon}, a first attempt at using the CSW fit with data \textit{a single-string detector} to reconstruct $\log_{10}E_{\rm C}$ was presented.
-Though the error range for $\log_{10}E_{\rm C}$ is large, the average value is correct: $\log_{10}E_{\rm C} = 16.5 \pm 2.0$ for 100 PeV.
+Though the error range for $\log_{10}E_{\rm C}$ was large, the average value was correct: $\log_{10}E_{\rm C} = 16.5 \pm 2.0$ for 100 PeV.
 
@@
 Amy Connolly for inspiring us and encouraging us to master more advanced applications of complex analysis to mathematical physics.
-It is our hope that the model will one day help to identify the first UHE-$\nu$ measured via the Askaryan effect.
+We hope the model will help identify the first UHE-$\nu$ via the Askaryan effect, especially in light of potential UHE-$\nu$ observations \cite{collaboration2025observation-22f}.
 

### 2025-10-09 template.tex
fine-tuning the writing ... not changing analysis

@@
 Second, the analytic model is compared to UHE-$\nu$ signals at 100 PeV from NuRadioMC, a key Monte Carlo toolset in the field.
-Correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of $\rho=0.4$.
+Correlation coefficients between the analytic signal envelope and MC data in excess of $0.94$ are found, and 99.99\% of UHE-$\nu$ signals pass a correlation threshold of $\rho\geq 0.4$.
 Analysis of RF thermal noise reveals that just 0.2 background events have $\rho\geq 0.4$ in 5 years at a 1 Hz thermal trigger rate.
@@
 L.
-Connolly (JCH+AC) for spectral filtering due to coherence effects and the form factor of the instantaneous charge distribution (ICD) \cite{10.1016/j.astropartphys.2017.03.008}.
+Connolly (JCH+AC), who developed an analytic form factor for the instantaneous charge distribution (ICD) that explains the low-pass filtering of the Askaryan spectrum, and cascade elongation from the LPM effect \cite{10.1016/j.astropartphys.2017.03.008}.
 When correlated against semi-analytic parameterizations used in NuRadioMC (ARHZ2020), which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH2022 model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.101.083005,PhysRevD.105.123019}.
@@
 Askaryan-class detectors actually observe voltage traces that represent the RF detection channel response, convolved with $\vec{E}$-fields that have propagated through kilometers of polar ice.
-NuRadioMC accounts for these effects by incorporating measurements from years of lab field work \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.
+NuRadioMC accounts for these effects by incorporating measurements from years of lab and field work \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.
 In this work, we present the first fully analytic Askaryan model in the time-domain that matches the observed voltage traces.
@@
 \ref{sec:unit}.
-In Sec.
-\ref{sec:onc}, the calculations of the observed voltage trace and Hilbert envelope of the trace are given.
+The calculations of the observed voltage trace and Hilbert envelope of the trace are given in Sec.
+\ref{sec:onc}.
 These results are compared to NuRadioMC output in Sec.
@@
 The analysis is based on two analytic functions: the Askaryan signal, $s(t)$, and the RF channel response, $r(t)$.
-The observed voltage trace in an Askaryan-class detector is $r(t) * s(t)$, the convolution of $r(t)$ and $s(t)$.
+The RF detection channel is a linear, time-invariant DSP system.
+Thus, the observed voltage trace in an Askaryan-class detector is the convolution of $r(t)$ and $s(t)$, $r(t) * s(t)$.
 Let $\hat{s}(t)$ represent the Hilbert transform of $s(t)$, and let $j=\sqrt{-1}$.
@@
 The speed $c$ is equal to the vacuum value, divided by the index of refraction $n$.
-For RF in ice, $n=1.78$ and $\theta_{\rm C} = 55.8$ degrees.
+For RF in ice, $n=1.78$.
 The viewing angle $\theta$ is the zenith angle in spherical coordinates, if the cascade axis is the z-axis.
-The Cherenkov angle is $\cos\theta_{\rm C} = 1/n$ for relativistic cascades.
+The Cherenkov angle is $\cos\theta_{\rm C} = 1/n$ for relativistic cascades, and for the RF bandwidth in ice, $\theta_{\rm C} = 55.8$ degrees.
 The longitudinal cascade length, $a$, is set by the cascade physics.
@@
 
-The $n_{\rm max}$ parameter is the maximum excess negative cascade charge, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.
-JCH+AC and HH2022 demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the instantaneous charge distribution (ICD) and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
+The $n_{\rm max}$ parameter is the maximum number of excess negative cascade charges, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.
+JCH+AC and HH2022 demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the ICD and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
 Monte Carlo simulations have shown that the lateral dependence of the ICD is exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.
-JCH+AC derived the ICD form factor, $\widetilde{F}(\omega)$, by modeling the lateral component of the ICD as an exponential distribution.
-Finally, the authors of HH2022 have shown that the parameter $p$ is related to $\sigma_t$, the Gaussian pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
+JCH+AC derived the form factor by modeling the lateral component of the ICD as an exponential distribution.
+Finally, the authors of HH2022 have shown that the parameter $p$ is related to $\sigma_t$, the pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
 
@@
 \begin{align}
-a_{\rm em} &= c_{\rm em} \sqrt{\ln\Lambda} \label{eq:em} \\
-a_{\rm had} &= c_{\rm had} \sqrt{\ln\Lambda} \label{eq:had}
+a_{\rm em} &= x_{\rm em} \sqrt{\ln\Lambda} \label{eq:em} \\
+a_{\rm had} &= x_{\rm had} \sqrt{\ln\Lambda} \label{eq:had}
 \end{align}
 \noindent
-The values for $c_{\rm em}$ and $c_{\rm had}$ are calculated in Sec. \ref{sec:recon}. From Eq. \ref{eq:uncert}, the fractional error in $\ln\Lambda$ is:
+The values for $x_{\rm em}$ and $x_{\rm had}$ are calculated in Sec. \ref{sec:recon}. From Eq. \ref{eq:uncert}, the fractional error in $\ln\Lambda$ is:
 
@@
 
-The parameters in Eq. \ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the time-dependence.  Let the signal model $s(t)$ be
+The parameters in Eq.
+\ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the time-dependence.
+From now on, let $t$ refer to $t_{\rm r}$, without the subscript.
+The signal model $s(t)$ is
 \begin{equation}
@@
 This is the \textit{off-cone} equation from \cite{PhysRevD.105.123019}.
-The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: $a$ and $\Delta\theta$.
+The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: $a$ and $\Delta\theta$ (Eq.
+\ref{eq:uncert}).
 The parameter $E_0$ is the amplitude normalization, and the dependencies on other parameters can be determined from Eq.
@@
 \ref{tab:param}.
+To achieve the goal of $\mathcal{E}_{\rm r * s}(t)$, the Hilbert transform and analytic signal of $s(t)$ are required.
 The Hilbert transform $\widehat{s}(t)$ is equivalent to the convolution of $s(t)$ and the tempered distribution $h(t) = 1/(\pi t)$.
@@
 Thus, an analytic prediction for the Hilbert envelope of the observed data would an effective signal template.
-An assumption must be made, however, for the RF channel response.
-The RLC damped oscillator is a suitable circuit model for the RF dipole antennas used in RICE, RNO-G, and the proposed IceCube Gen2 \cite{10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
-In fact, an RLC response was first used by RICE at the South Pole \cite{10.1103/PhysRevD.85.062004}.
+An assumption must be made, however, for the RF channel response, $r(t)$.
+The RLC impulse response was first used by RICE at the South Pole at a model for RF dipole channels \cite{10.1103/PhysRevD.85.062004}.
+The RLC damped oscillator is a suitable circuit model for the RF dipole channels for two reasons.
+First, dipoles respond within a bandwidth centered around a resonance frequency, just as RLC circuits do.
+Second, RF dipole  channels are used in RICE, RNO-G, and the proposed IceCube Gen2 because these channels must fit inside cylindrical ice boreholes \cite{10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
+Thus, the model chosen for $r(t)$ is the damped oscillation of an RLC circuit.
 
@@
 \ref{eq:awesome} is based on two ideas.
-First, the Hilbert transform of a function $s(t)$ is equivalent to convolving it with the ``tempered distribution'' $h(t) = 1/(\pi t)$.
-Second, computing the Hilbert transform twice yields the original function, multiplied by $-1$: $h * h * s = -s$.
-Given the definitions of the analytic signal and the Hilbert transform,
+First, the Hilbert transform of a function $s(t)$ is equivalent to convolving it with $h(t) = 1/(\pi t)$.
+Second, the Hilbert transform is an \textit{anti-involution}, meaning acting it twice on a function $f(t)$ yields $-f(t)$: $h * h * f = -f$.
+Given the definitions of $s_a(t)$ and $\hat{s}(t)$,
 \begin{align}
@@
 \end{multline}
-Using Leibniz rule for the fundamental theorem of calculus, and the limiting cases of $D(x)$, 
+Using Leibniz rule for the fundamental theorem of calculus, and the limiting cases of $D(x)$, xxyyzz
 \begin{multline}
@@
 
+\appendix
+
+\section{Python3 Example Code for $\mathcal{E}_{\rm s * r}(t)$}
+\label{sec:appA}
+
+\begin{verbatim}
+things
+\end{verbatim}
+
+\section{Python3 Example Code for $s(t) * r(t)$}
+\label{sec:appA}
+
+\begin{verbatim}
+things
+\end{verbatim}
+
 \bibliography{apssamp}

### 2025-10-09 template.tex
added code to paper in appendix

@@
 Connolly (JCH+AC), who developed an analytic form factor for the instantaneous charge distribution (ICD) that explains the low-pass filtering of the Askaryan spectrum, and cascade elongation from the LPM effect \cite{10.1016/j.astropartphys.2017.03.008}.
-When correlated against semi-analytic parameterizations used in NuRadioMC (ARHZ2020), which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH2022 model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.101.083005,PhysRevD.105.123019}.
+When correlated against semi-analytic parameterizations used in NuRadioMC (AHRZ2020), which involve numeric convolution of UHE-$\nu$ cascade data with an analytic vector potential, the HH2022 model yields correlation coefficients in excess of 0.95 \cite{PhysRevD.101.083005,PhysRevD.105.123019}.
 This allows precise reconstruction of UHE-$\nu$ cascade parameters, but is limited to comparisons between the simulated and theoretical $\vec{E}$-fields.
@@
 \end{multline}
-Using Leibniz rule for the fundamental theorem of calculus, and the limiting cases of $D(x)$, xxyyzz
+Using Leibniz rule for the fundamental theorem of calculus, and the limiting cases of $D(x)$,
 \begin{multline}
@@
 Though a closed analytic form for $\mathcal{L}\lbrace D(u-x)\rbrace_k$ is elusive, evaluating $\mathcal{L}\lbrace D(u-x)\rbrace_k$ numerically is fast and precise.
+A short code that demonstrates how this Laplace transform is computed is given in Appendix \ref{sec:appA}.
 
@@
 \includegraphics[width=0.5\textwidth]{July3rd_plot2.pdf}
-\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.
-The light gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 SciPy function scipy.special.hilbert.
-The dark gray envelope represents Eq.
+\caption{\label{fig:fig1} (Top) The thin black line represents Eq.
+\ref{eq:final3}.
+The light gray envelope represents the envelope of Eq.
+\ref{eq:final3} computed with the Python3 SciPy function scipy.special.hilbert.
+The black envelope represents Eq.
 \ref{eq:final}-\ref{eq:final2}.
@@
 \includegraphics[width=0.5\textwidth]{July7th_plot2.pdf}
-\caption{\label{fig:fig2} (Top) The thin black line represents $s(t) * r(t)$, produced using the Python3 SciPy function scipy.signal.convolve.
-The dark gray line represents Eq.
+\caption{\label{fig:fig2} (Top) The thin black line represents Eq.
+\ref{eq:s} convolved with Eq.
+\ref{eq:r}, produced using the Python3 SciPy function scipy.signal.convolve.
+The gray line represents Eq.
 \ref{eq:final3}.
@@
 The 100 PeV interactions included charged and neutral electroweak currents, and the LPM effect.
-The Askaryan model used in NuRadioMC was ARZ2020 \cite{PhysRevD.101.083005}.
-ARZ2020 is a \textit{semi-analytic} parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the net charge in the UHE-$\nu$ cascade.
-ARZ2020 accounts for sub-cascades and the LPM effect, and it has been validated against MC simulations \cite{zhs,10.1103/physrevd.84.103003}.
-The Askaryan signal model used in NuRadioMC for this analysis was \textit{not} HH2022 \cite{PhysRevD.105.123019}.
-Thus, the correlation between MC output (ARZ2020) and Eqs.
-\ref{eq:final}-\ref{eq:final2} (HH2022 and this work) is solely on physical grounds.
+The Askaryan model used in NuRadioMC was AHRZ2020 \cite{PhysRevD.101.083005}.
+AHRZ2020 is a \textit{semi-analytic} parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the net charge in the UHE-$\nu$ cascade.
+AHRZ2020 accounts for sub-cascades and the LPM effect, and it has been validated against MC simulations \cite{zhs,10.1103/physrevd.84.103003}.
+The Askaryan model used in NuRadioMC for this analysis was \textit{not} HH2022, so correlations between MC output and Eqs.
+\ref{eq:final}-\ref{eq:final2} is solely on physical grounds.
 
@@
 Ice Model & South Pole & 2015 measurements \\
-Signal Model & ARZ2020 & (see \cite{PhysRevD.101.083005}) \\
+Signal Model & AHRZ2020 & (see \cite{PhysRevD.101.083005}) \\
 Trigger & 3 of 8 channels & $\pm 3v_{\rm rms}$ \\
@@
 Channel depths & [-4,-6,-8,...-18] m & cable delays included \\
-RF cable type & LMR-400 & $<0.0886$ dB m$^{-1}$ \\
+RF cable type & LMR-400 & $\approx -1$ dB at 20 m  \\
 \hline
 \end{tabular}
-\caption{\label{tab:1} Important NuRadioMC parameters used in this analysis.}
+\caption{\label{tab:1} Important NuRadioMC parameters.}
 \end{table}
@@
 In Fig.
-\ref{fig:fig3}, the circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and thermal noise.
+\ref{fig:fig3}, the circles represent the normalized histogram of the correlation coefficient between the optimized analytic envelope and thermal noise.
 A fitting function of the form $x^2 \exp(-0.5 x^2)$ was fit to the noise distribution, and is represented by the gray dashed line.
@@
 \ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants.
-Without a separate fit for $\Delta\theta$ an assumption must be made.
+Without a separate fit for $\Delta\theta$, an assumption must be made.
 We will make the assumption that $\Delta\theta \approx \Delta\theta_{\rm rms}$.
-The assumption is justified since the $\Delta\theta$ distribution is Gaussian.
 The MC truth for $\Delta\theta$ in this analysis is shown in Fig.
 \ref{fig:fig5}, with a Gaussian fit.
-The rms and $\sigma$ values are equal for normal distributions, so we let $\Delta\theta \approx \Delta \theta_{\rm rms}$ and set the fractional error $\sigma_{\Delta\theta}/\Delta\theta$ to 1.0.
+The rms and $\sigma$ values are equal for normal distributions with zero mean.
+As a rough approximation, we let $\Delta\theta \approx \Delta \theta_{\rm rms}$ and set the fractional error $\sigma_{\Delta\theta}/\Delta\theta$ to 1.0.
 Solving Eq.
@@
 \ref{eq:lnLambda}.
-Third, let $c_{\rm ave}$ be the average of $c_{\rm em}$ and $c_{\rm had}$, reflecting the unknown hadronic or electromagnetic nature of the cascade.
+Third, let $c_{\rm ave}$ be the average of $c_{\rm em}$ and $c_{\rm had}$, accurate to 0.05 m.
+The average reflects the unknown hadronic or electromagnetic nature of the cascade.
 The modified form of Eq.
@@
 This systematically overestimates $\log_{10} E_{\rm C}$.
+Though it is straightforward to add a second analytic envelope to the fit algorithm to account for multiple pulses, this was beyond the scope of this work.
 An example of a CSW event with direct and reflected components fit by an analytic envelope is shown in Fig.
@@
 $\overline{\sigma_t}$ & $1.229 \pm 0.004$ ns \\
-$c_{\rm ave}$ & 0.86 m \\
-$\Delta\theta_{\rm rms}$ & $3.78\pm0.04$ degrees \\
+$c_{\rm ave}$ & 0.85 m \\
+$\Delta\theta_{\rm rms}$ & $3.78$ degrees \\
 $E_{\rm crit}$ & 100 MeV \\
 $\sin\theta_{\rm C}$ & 0.8271 \\ \hline
-\textbf{Reconstructed} $\mathbf{\log_{10}E_{\rm C}}$ & $16.5\pm 2.0$ \\
+\textbf{Reconstructed} $\mathbf{\log_{10}E_{\rm C}}$ & $16.7\pm 2.0$ \\
 \hline
@@
 Finally, in Sec.
-\ref{sec:recon}, a first attempt at using the CSW fit with data \textit{a single-string detector} to reconstruct $\log_{10}E_{\rm C}$ was presented.
+\ref{sec:recon}, a first attempt to reconstruct $\log_{10}E_{\rm C}$ using the CSW fit with data from a \textit{a single-string detector} was presented.
 Though the error range for $\log_{10}E_{\rm C}$ was large, the average value was correct: $\log_{10}E_{\rm C} = 16.5 \pm 2.0$ for 100 PeV.
@@
 \ref{eq:err_prop}.
+This procedure was completed in HH2022, but it is restricted to comparisons between $\vec{E}$-fields and not observed CSWs.
 
-Third, it is interesting to note that the entire model relies on the \textit{off-cone} ($\theta \neq \theta_{\rm C}$) version of $s(t)$.
-HH2022 also includes an \textit{on-cone} version of $s(t)$ that is used when $\Delta\theta \lesssim 1$ degree.
+Third, it is interesting to note that the model in this work relies on the \textit{off-cone} ($\theta \neq \theta_{\rm C}$) version of $s(t)$.
+HH2022 also includes an \textit{on-cone} version of $s(t)$ that is used when $\Delta\theta = 0$, and can be used as $\Delta\theta\to 0$.
 The on-cone model could provide a better fit between $\mathcal{E}_{\rm s*r}(t)$ for events with $\Delta\theta \lesssim 1$ degree.
+Further, the on-cone model is defined in a piecewise fashion by rising and falling exponential functions, making the convolution with Eq.
+\ref{eq:r} easier than the procedure used to arrive at Eqs.
+\ref{eq:final}-\ref{eq:final2}.
 
@@
 
-\section{Python3 Example Code for $\mathcal{E}_{\rm s * r}(t)$}
+\section{Python3 Code for $\mathcal{L}\lbrace D(u-x)\rbrace_k$}
 \label{sec:appA}
 
+The code in this section computes the Laplace transform of the shifted Dawson function, $\mathcal{L}\lbrace D(u-x)\rbrace_k$.
+The syntax has been adjusted to fit in two-column format, so please check the alignment.
+
+\small
 \begin{verbatim}
-things
+import numpy as np
+from scipy.integrate import quad
+from scipy.special import dawsn as D
+...
+def shifted_laplace_transform(self,f,s,t0,t_max=1000):
+    x = s.real
+    y = s.imag
+    re_int = quad(lambda t: 
+        np.exp(-x*t)*np.cos(y*t)*f(t-t0),0,t_max)[0]
+    im_int = quad(lambda t: 
+        np.exp(-x*t)*np.sin(y*t)*f(t-t0),0,t_max)[0]
+    return complex(re_int,-im_int)
+...
+x = t/(sigma_t*np.sqrt(2))
+z = (2*np.pi*J*f0-2*np.pi*gamma)*np.sqrt(2)*sigma_t
+k=-z
+... + k*self.shifted_laplace_transform(D,k,x))
+\end{verbatim}
+
+\section{Python3 Example Code for $\mathcal{E}_{\rm s * r}(t)$}
+\label{sec:appB}
+
+The code in this section computes $\mathcal{E}_{\rm s * r}(t)$.  The syntax has been adjusted to fit in two-column format, so please check the alignment.
+
+\small
+\begin{verbatim}
+import numpy as np
+from scipy.integrate import quad
+from scipy.special import dawsn as D
+...
+def shifted_laplace_transform(...):
+...
+def math_env(self,t,E0,R0,sigma_t,f0,gamma):
+    units = R0*E0*sigma_t*sigma_t
+    J = complex(0,1)
+    x = t/(sigma_t*np.sqrt(2))
+    z = (2*np.pi*J*f0-2*np.pi*gamma)
+    z *= np.sqrt(2)*sigma_t
+    k=-z
+    q = -J*(x+z/2)
+    first = -np.sqrt(np.pi)*(x*np.exp(-x*x)*w(q)
+        +0.5*J*np.exp(-x*x)*self.dwdq(q))
+    second = 2/np.sqrt(np.pi)*(D(x)
+        +k*self.shifted_laplace_transform(D,k,x))
+    if(np.isinf(first) or np.isinf(second) 
+        or np.isnan(first) or np.isnan(second)):
+        return 0.0
+    else:
+        result = units*(first+J*second)
+    return 0.5*np.abs(result)
 \end{verbatim}
@@
 \section{Python3 Example Code for $s(t) * r(t)$}
-\label{sec:appA}
+\label{sec:appC}
 
+The code in this section contains the definitions of $s(t)$ and $r(t)$, and computes $s(t) * r(t)$.  The syntax has been adjusted to fit in two-column format, so please check the alignment.
+
+\small
 \begin{verbatim}
-things
+import numpy as np
+from scipy.special import wofz as w
+...
+def dwdq(q):
+    J = complex(0,1)
+    return 2*J/np.sqrt(np.pi)-2*q*w(q)
+def s(t,E0,sigma_t):
+    return -E0*t*np.exp(-0.5*t*t/sigma_t/sigma_t)
+def r(t,R0,f0,gamma):
+    if(t>=0):
+        result = R0*np.cos(2*np.pi*f0*t)
+        result *= np.exp(-2*np.pi*gamma*t)
+        return result
+    else:
+        return 0
+...
+def math_conv(t,E0,R0,sigma_t,f0,gamma):
+    J = complex(0,1)
+    units = R0*E0*sigma_t*sigma_t
+    x = t/(sigma_t*np.sqrt(2))
+    z = (2*np.pi*J*f0-2*np.pi*gamma)
+    z *= np.sqrt(2)*sigma_t
+    q = -J*(x+0.5*z)
+    Re_wq = np.real(w(q))
+    Re_dwdx = np.real(-J*dwdq(q))
+    result = x*np.exp(-x*x)*Re_wq
+    result -= 0.5*np.exp(-x*x)*Re_dwdx)
+    if(np.isinf(result) or np.isnan(result)):
+        return 0.0
+    else:
+        return -np.sqrt(np.pi)*units*result
 \end{verbatim}

### 2025-10-09 energy_distribution.m

@@ -4,8 +4,8 @@ home;
 results = load('all_results_100PeV.dat');
 c = 0.3/1.78;
 sinC = sin(55.8*pi/180.0);
-jj = find(and(abs(results(:,9)*180/pi-55.8)>0,results(:,6)<3.0));
+jj = find(and(abs(results(:,9)*180/pi-55.8)>0.0,results(:,6)<3.0));
 sigma = mean(results(jj,6));
 dTheta = std(results(jj,9)-55.8*pi/180.0);
-cem = 0.86;
+cem = 0.85;
 log10E = (c*sigma./cem./dTheta/sinC).^2/log(10.0)+8.0

### 2025-10-12 template.tex
last commit

@@
 
-\title{Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction via the Hilbert Envelope of Observed Signals}
+\title{Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction using the Hilbert Envelope of Observed Signals}
 
@@
 UHE-$\nu$ could reveal the source of ultra-high energy cosmic rays (see sections 3.1-3.3 of \cite{10.48550/arxiv.2008.04323}).
-Further, studying electroweak interactions at these energies is impossible on Earth, and Askaryan-class neutrino detectors provide new data (see section 3.4 of \cite{10.48550/arxiv.2008.04323}).
+Further, studying electroweak interactions at these energies is impossible on Earth, and Askaryan-class neutrino detectors will provide new data (see section 3.4 of \cite{10.48550/arxiv.2008.04323}).
 
@@
 In Sec.
-\ref{sec:conc}, the key findings are summarized.
+\ref{sec:recon}, a preliminary reconstruction of the logarithm of the cascade energy from the UHE-$\nu$ interaction is given.
+The key findings are summarized in Sec.
+\ref{sec:conc}.
 
@@
 Let $\hat{s}(t)$ represent the Hilbert transform of $s(t)$, and let $j=\sqrt{-1}$.
-The \textit{analytic signal} and \textit{signal envelope} are defined by
+The \textit{analytic signal}, $s_a(t)$, and \textit{signal envelope}, $\mathcal{E}_s(t)$, are defined by
 
@@
 The $n_{\rm max}$ parameter is the maximum number of excess negative cascade charges, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.
-JCH+AC and HH2022 demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the ICD and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
+JCH+AC and HH2022 demonstrated that the frequency $\omega_{\rm 0}$ is related to the ICD and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.
 Monte Carlo simulations have shown that the lateral dependence of the ICD is exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.
-JCH+AC derived the form factor by modeling the lateral component of the ICD as an exponential distribution.
-Finally, the authors of HH2022 have shown that the parameter $p$ is related to $\sigma_t$, the pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
+JCH+AC derived the form factor by modeling the lateral component of the ICD as an exponential distribution, which in turn makes the form factor act as a low-pass filter with cutoff $\omega_0$.
+Finally, the authors of HH2022 showed that $p$ in Tab.
+\ref{tab:param} is related to $\sigma_t$, the pulse width of $s(t)$ \cite{PhysRevD.105.123019}:
 
@@
 \ref{tab:param}.
+The most important of these is the $1/r$ dependence (Eq.
+\ref{eq:s_full}).
 To achieve the goal of $\mathcal{E}_{\rm r * s}(t)$, the Hilbert transform and analytic signal of $s(t)$ are required.
@@
 First, dipoles respond within a bandwidth centered around a resonance frequency, just as RLC circuits do.
-Second, RF dipole  channels are used in RICE, RNO-G, and the proposed IceCube Gen2 because these channels must fit inside cylindrical ice boreholes \cite{10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
+Second, RF dipole channels are used in RICE, ARA, RNO-G, and the proposed IceCube Gen2 because these channels must fit inside cylindrical ice boreholes \cite{10.1103/PhysRevD.85.062004,10.1103/physrevd.102.043021,10.1016/j.astropartphys.2011.11.010,10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.
 Thus, the model chosen for $r(t)$ is the damped oscillation of an RLC circuit.
@@
 The Askaryan model used in NuRadioMC for this analysis was \textit{not} HH2022, so correlations between MC output and Eqs.
-\ref{eq:final}-\ref{eq:final2} is solely on physical grounds.
+\ref{eq:final}-\ref{eq:final2} are solely on physical grounds.
 
@@
 \begin{equation}
-\ln\Lambda = \left( \frac{c\sigma_t}{c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2 \label{eq:lnLambda}
+\ln\Lambda = \left( \frac{c\sigma_t}{x_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2 \label{eq:lnLambda}
 \end{equation}
@@
 Using Eqs.
-10 and 12 from HH2022 (\cite{PhysRevD.105.123019}), $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).
+10 and 12 from HH2022 (\cite{PhysRevD.105.123019}), $x_{\rm em}$ and $x_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).
 Using Eq.
@@
 \ref{eq:lnLambda}.
-Third, let $c_{\rm ave}$ be the average of $c_{\rm em}$ and $c_{\rm had}$, accurate to 0.05 m.
+Third, let $x_{\rm ave}$ be the average of $x_{\rm em}$ and $x_{\rm had}$, accurate to 0.05 m.
 The average reflects the unknown hadronic or electromagnetic nature of the cascade.
@@
 \begin{equation}
-\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(c_{\rm ave} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
+\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(x_{\rm ave} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
 \end{equation}
@@
 This systematically overestimates $\log_{10} E_{\rm C}$.
-Though it is straightforward to add a second analytic envelope to the fit algorithm to account for multiple pulses, this was beyond the scope of this work.
-An example of a CSW event with direct and reflected components fit by an analytic envelope is shown in Fig.
+Though adding a second analytic envelope to the fit algorithm to account for pulse reflection is straightforward, this added complexity was beyond the scope of this work.
+An example CSW event with direct and reflected signals fit by an analytic envelope is shown in Fig.
 \ref{fig:example_waveforms_2}.
@@
 \ref{sec:recon}, a first attempt to reconstruct $\log_{10}E_{\rm C}$ using the CSW fit with data from a \textit{a single-string detector} was presented.
-Though the error range for $\log_{10}E_{\rm C}$ was large, the average value was correct: $\log_{10}E_{\rm C} = 16.5 \pm 2.0$ for 100 PeV.
+Though the error range for $\log_{10}E_{\rm C}$ was large, the average value was correct: $\log_{10}E_{\rm C} = 16.7 \pm 2.0$ for 100 PeV.
 
@@
 This procedure should be combined with the analytic envelope fit to advance UHE-$\nu$ energy reconstruction.
-Though this is not difficult to implement in NuRadioMC, it was beyond the scope of this work.
+Though this is not difficult to implement, it was beyond the scope of this work.
 
@@
 HH2022 also includes an \textit{on-cone} version of $s(t)$ that is used when $\Delta\theta = 0$, and can be used as $\Delta\theta\to 0$.
-The on-cone model could provide a better fit between $\mathcal{E}_{\rm s*r}(t)$ for events with $\Delta\theta \lesssim 1$ degree.
+The on-cone model could provide a better fit between $\mathcal{E}_{\rm s*r}(t)$ for events with $\Delta\theta \lesssim 1$ degree \cite{PhysRevD.105.123019}.
 Further, the on-cone model is defined in a piecewise fashion by rising and falling exponential functions, making the convolution with Eq.
@@
 Mark Kozek for useful background discussions.
-We are grateful to the authors of RB, Prof.
+We are grateful to the authors of RB, Profs.
 John Ralston and Roman Buniy, for inspiring us in this line of research \cite{10.1103/physrevd.65.016003}.
@@
 from scipy.integrate import quad
+from scipy.special import wofz as w
 from scipy.special import dawsn as D
@@
 ...
+def dwdq(q):
+    J = complex(0,1)
+    return 2*J/np.sqrt(np.pi)-2*q*w(q)
 def math_env(self,t,E0,R0,sigma_t,f0,gamma):
@@
 ...
-def dwdq(q):
-    J = complex(0,1)
-    return 2*J/np.sqrt(np.pi)-2*q*w(q)
+def dwdq(...):
+...
 def s(t,E0,sigma_t):
@@
         return 0
-...
 def math_conv(t,E0,R0,sigma_t,f0,gamma):

### 2025-11-09 ARAFit/pres/JCHanson_Nov11_2025_ARAAnalysis.tex
started ARA presentation

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{graphicx}
\usepackage{hyperref}
\title{Complex analysis of Askaryan Radiation: UHECR and UHE-$\nu$ Reconstruction with Analytic Signals}
\author{Jordan Hanson}
\institute{Whittier College Department of Physics and Astronomy}
\bibliographystyle{abbrv}

\begin{document}
\maketitle

\section{Summary}

\begin{frame}{UHECR and UHE-$\nu$ Reconstruction with Analytic Signals}
\footnotesize
\begin{enumerate}
\footnotesize
\item \alert{\textbf{Introduction}}: 
\footnotesize
\begin{itemize}
\footnotesize
\item \textbf{A fully analytic Askaryan E-field} model in the time-domain \cite{hanson2022complex-5f5}
\item Based on work begun with Prof. Amy Connolly \cite{hanson2017complex-037}
\item Based on work begun by J. Ralston and R. Buniy \cite{buniy2001radio-221}
\item Advantages: (i) extract UHE-$\nu$ cascade parameters by fitting model to raw voltage traces, (ii) fast and simple, (iii) analytic equations may be embedded as event filter
\end{itemize}
\item \alert{\textbf{UHECR and UHE-$\nu$ identification}}:
\begin{itemize}
\footnotesize
\item \textbf{A fully analytic Askaryan voltage} model, time-domain [this work]
\item Equations for both voltage trace, and envelope of voltage trace
\item Verification with NuRadioMC: strong thermal background rejection, signal identification, and (rough) $\log_{\rm 10}(E_{\rm \nu})$ estimate
\end{itemize}
\item \alert{\textbf{Correlation with Recent ARA observations of UHECR}}
\end{enumerate}
\end{frame}

\section{Bibliography}

\begin{frame}{Bibliography}
\bibliography{references}
\end{frame}

\end{document}

### 2025-11-10 ARAFit/pres/JCHanson_Nov11_2025_ARAAnalysis.tex
started ARA analysis call presentation

@@
 \usepackage{hyperref}
+\usepackage{tcolorbox}
+\DeclareMathOperator\erfc{erfc}
+\DeclareMathOperator\erf{erf}
+\DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\snr}{SNR}
+\definecolor{box_background}{RGB}{240,240,240}
+\definecolor{box_frame}{RGB}{40,40,40}
 \title{Complex analysis of Askaryan Radiation: UHECR and UHE-$\nu$ Reconstruction with Analytic Signals}
@@
 \footnotesize
-\item \textbf{A fully analytic Askaryan E-field} model in the time-domain \cite{hanson2022complex-5f5}
-\item Based on work begun with Prof. Amy Connolly \cite{hanson2017complex-037}
-\item Based on work begun by J. Ralston and R. Buniy \cite{buniy2001radio-221}
+\item \textbf{A fully analytic Askaryan E-field} model in the time-domain \cite{hh2022}
+\item Based on work begun with Prof. Amy Connolly \cite{jchac2017}
+\item Based on work begun by J. Ralston and R. Buniy \cite{rb}
 \item Advantages: (i) extract UHE-$\nu$ cascade parameters by fitting model to raw voltage traces, (ii) fast and simple, (iii) analytic equations may be embedded as event filter
@@
 
+\section{UHECR Event Geometry for in the ARA Detector}
+
+\begin{frame}{UHECR Event Geometry for in the ARA Detector}
+\begin{columns}
+\begin{column}{0.6\textwidth}
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/ara.png}
+\caption{\label{fig:1} (Top right) UHECR cascade core interacting in ice. (Bottom left) ARA RF detection channels (Vpol and Hpol).}
+\end{figure}
+\end{column}
+\begin{column}{0.5\textwidth}
+\alert{\textbf{ARA detector schematic}}
+\begin{itemize}
+\item Askaryan component of the radiation
+\item Vpol and Hpol channels are dipole antennas
+\item E-field components are radial to the cascade axis
+\item Reference: \url{https://arxiv.org/pdf/2510.21104}
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\section{Notations and Definitions}
+
+\begin{frame}{Notations and Definitions}
+\footnotesize
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Askaryan electric field, $\vec{E}(r,t)$, [V m$^{-1}$]}]
+\begin{equation}
+r \vec{E}(t,\theta) = -\frac{E_0 \omega_0 \sin(\theta)}{8 \pi p} t_r e^{-\frac{t_r^2}{4p} + p \omega_0^2}\erfc(\sqrt{p}\omega_0)
+\end{equation}
+\end{tcolorbox}
+\begin{table}
+\scriptsize
+\begin{tabular}{| c | c | c |} \hline
+\textbf{Variable} & \textbf{Definition} & \textbf{Units}\\ \hline
+$c$ & speed of light in medium & m ns$^{-1}$ \\ 
+$r$ & distance to cascade peak & m \\
+$t_{\rm r}$ & $t-r/c$ & ns \\
+$\theta_{\rm C}$ & Cherenkov angle & radians \\ 
+$\theta$ & viewing angle from cascade axis & radians \\ 
+$a$ & longitudinal cascade length (see \cite{rb,jchac2017,hh2022}) & m \\ 
+$n_{max}$ & max excess cascade particles (see \cite{rb,jchac2017,hh2022})  & none \\
+$E_{\rm 0}$ & $\propto n_{\rm max}a$ (see \cite{rb,jchac2017,hh2022}) & V GHz$^{-2}$ \\
+$p$ & $\frac{1}{2}(a/c)^2 \left(\cos\theta - \cos\theta_C\right)^2$ (see \cite{hh2022}) & ns$^2$ \\ 
+$\omega_{\rm 0}$ & $\sqrt{\frac{2}{3}} (c\sqrt{2\pi}\rho_{\rm 0})/(\sin\theta)$ (see \cite{jchac2017,hh2022}) & GHz \\
+$\sqrt{2\pi}\rho_{\rm 0}$ & lateral ICD width (see \cite{jchac2017,hh2022}) & m$^{-1}$ \\ \hline
+\end{tabular}
+\caption{\label{tab:param} Parameters relevant for $E(t)$.}
+\end{table}
+\end{frame}
+
+\begin{frame}{Notations and Definitions}
+\footnotesize
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Askaryan \textit{signal}, $\vec{s}(t)$, [V m$^{-1}$]}]
+\begin{equation}
+s(t) = -E_0 t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2}
+\end{equation}
+\end{tcolorbox}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Detector \textit{response}, $\vec{r}(t)$, [m ns$^{-1}$]}]
+\begin{equation}
+r(t) = R_0 e^{-2 \pi \gamma t} \cos(2\pi f_0 t)
+\end{equation}
+\end{tcolorbox}
+\end{frame}
+
 \section{Bibliography}
 
-\begin{frame}{Bibliography}
+\begin{frame}[allowframebreaks]{Bibliography}
 \bibliography{references}

### 2025-11-11 ARAFit/pres/JCHanson_Nov11_2025_ARAAnalysis.tex
finished ARA analysis call talk

@@
 \definecolor{box_background}{RGB}{240,240,240}
-\definecolor{box_frame}{RGB}{40,40,40}
+\definecolor{box_frame}{RGB}{50,50,50}
 \title{Complex analysis of Askaryan Radiation: UHECR and UHE-$\nu$ Reconstruction with Analytic Signals}
@@
 
-\section{Notations and Definitions}
+\section{Notations, Definitions, and Analytic Signals}
 
-\begin{frame}{Notations and Definitions}
+\begin{frame}{Notations, Definitions, and Analytic Signals}
 \footnotesize
@@
 
-\begin{frame}{Notations and Definitions}
+\begin{frame}{Notations, Definitions, and Analytic Signals}
 \footnotesize
 \begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Askaryan \textit{signal}, $\vec{s}(t)$, [V m$^{-1}$]}]
+Let $E_0$ represent all amplitude factors not dependent on time.  Further, let $\sigma_{\rm t} = \sqrt{2p}$.  The Askaryan E-field is
 \begin{equation}
@@
 \end{tcolorbox}
+\begin{itemize}
+\item Impulse response of a causal ($t\geq 0$) damped, driven RLC circuit
+\item First used by the RICE collaboration \cite{10.1103/PhysRevD.85.062004}
+\item RF dipole channels are used in RICE, ARA, RNO-G, and the proposed IceCube Gen2 (radio) \cite{10.1103/PhysRevD.85.062004,10.1103/physrevd.102.043021,10.1016/j.astropartphys.2011.11.010,10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}
+\item RF channels must fit inside cylindrical ice boreholes
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Notations, Definitions, and Analytic Signals}
+\footnotesize
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Analytic signal, $s_a(t)$, of $s(t)$.}]
+Let $s_a(t)$ be the \textit{analytic signal} of the signal $s(t)$.  Further, let $\hat{s}(t)$ be the Hilbert transform of $s(t)$.  Finally, let $\mathcal{E}_s(t)$ be the \textit{envelope} of $s(t)$.
+\begin{align}
+s_a(t) &= s(t) + j\hat{s}(t) \\
+\mathcal{E}_s(t) &= |s_a(t)|
+\end{align}
+\end{tcolorbox}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Analytic signals, $s_a(t)$, and $r_a(t)$.}]
+Let $x = t/(\sqrt{2}\sigma_{\rm t})$, and let $D(x)$ be the \textit{Dawson function.}  The analytic signals for $s(t)$ (V m$^{-1}$) and $r(t)$ (m ns$^{-1}$) are
+\begin{align}
+s_a(t) &= -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{2 j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right)  \\
+r_a(t) &= R_0 e^{-2 \pi \gamma t} e^{2\pi j f_0 t}
+\end{align}
+\end{tcolorbox}
+\end{frame}
+
+\begin{frame}{Notations, Definitions, and Analytic Signals}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title={Detected signals, $r(t) * s(t)$, [V]}]
+\begin{equation}
+r(t) * s(t) = \int_{-\infty}^{\infty} r(\tau) s(t-\tau) d\tau
+\end{equation}
+\end{tcolorbox}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title=Theorem: the envelope of detected signal]
+Let $\mathcal{E}_{r * s}(t)$ represent the \textit{envelope} of the convolution of $r(t)$ and $s(t)$.  If $s_a(t)$ and $r_a(t)$ are the analytic signals of $s(t)$ and $r(t)$, respectively, then
+\begin{equation}
+\mathcal{E}_{r*s}(t) = \frac{1}{2}|r_a(t) * s_a(t)|
+\end{equation}
+\end{tcolorbox}
+\end{frame}
+
+\begin{frame}{Notations, Definitions, and Analytic Signals}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title=$\mathcal{E}_{r*s}(t)$: part I]
+Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z = (2\pi j f_0 - 2\pi\gamma)\sqrt{2}\sigma_t$.
+Let $w(q)$ be the \textit{Faddeeva function,} with $b = jq$, $b = x+\frac{1}{2} z$.
+The convolution of $r_a(t)$ with $\Re\lbrace s_a(t)\rbrace$ is
+\begin{multline}
+r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ -\sqrt{\pi} R_0 E_0 \sigma_t^2 \left(x e^{-x^2} w(q) + \left(\frac{j}{2}\right) e^{-x^2} \frac{dw(q)}{dq} \right)
+\end{multline}
+\end{tcolorbox}
+\end{frame}
+
+\begin{frame}{Notations, Definitions, and Analytic Signals}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title=$\mathcal{E}_{r*s}(t)$: part II]
+Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z = (2\pi j f_0 - 2\pi\gamma)\sqrt{2}\sigma_t$.
+Let $u = x-y$, $z=-k$, and let $\mathcal{L}\lbrace D(u-x)\rbrace_k$ be the Laplace transform of the shifted Dawson function.
+The convolution of $r_a(t)$ with $\Im\lbrace s_a(t)\rbrace$ is
+\begin{multline}
+r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right) \label{eq:Im_result}
+\end{multline}
+\end{tcolorbox}
+\end{frame}
+
+\begin{frame}{Notations, Definitions, and Analytic Signals}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title=$\mathcal{E}_{r*s}(t)$: part III]
+\begin{align}
+\mathcal{E}_{r*s}(t) &= \frac{1}{2}| r_a * s_a| = \frac{1}{2}\left| r_a * \left( \Re\lbrace s_a\rbrace + j\Im\lbrace r_a\rbrace\right)\right| \\
+\mathcal{E}_{r*s}(t) &= \frac{1}{2}\left| r_a * \Re\lbrace s_a\rbrace + j r_a * \Im\lbrace r_a\rbrace \right|
+\end{align}
+\end{tcolorbox}
+\begin{itemize}
+\item We have calculated $r_a(t) * \Re\lbrace s_a(t)\rbrace$ and $r_a(t) * \Im\lbrace s_a(t)\rbrace$
+\item Combine to form the final result
+\item This result is used to predict the \textit{envelope} of the voltage traces and CSWs
+\item Python3 code provided in the paper
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Notations, Definitions, and Analytic Signals}
+\begin{tcolorbox}[colback=box_background,colframe=box_frame,title=$\mathcal{E}_{r*s}(t)$: part IV]
+Using prior definitions, it turns out that $s * r$ is
+\begin{multline}
+s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \Re\left\lbrace xe^{-x^2} w(q) - \frac{1}{2}e^{-x^2} \frac{d w(q)}{dx} \right\rbrace
+\end{multline}
+\end{tcolorbox}
+\begin{itemize}
+\item This result is used to predict the voltage traces and CSWs
+\item Python3 code provided in the paper
+\end{itemize}
+\end{frame}
+
+\section{Results: Voltage Traces and Envelopes}
+
+\begin{frame}{Results: Voltage Traces and Envelopes}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.49\textwidth]{figures/July3rd_plot1.pdf}
+\includegraphics[width=0.49\textwidth]{figures/July3rd_plot2.pdf}
+\caption{\label{fig:fig1} (Left) The thin black line represents $s*r$.
+The light gray envelope represents the envelope of $s*r$ computed with the Python3 SciPy function scipy.special.hilbert.
+The black envelope represents $\mathcal{E}_{r*s}(t)$.
+(Right) Same as left, for different parameter values.}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Results: Voltage Traces and Envelopes}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.49\textwidth]{figures/July7th_plot1.pdf}
+\includegraphics[width=0.49\textwidth]{figures/July7th_plot2.pdf}
+\caption{\label{fig:fig2} (Left) The thin black line represents $s$ convolved with $r$ using the Python3 SciPy function scipy.signal.convolve.
+The gray line represents $s*r$.
+(Right) Same as left, for different parameter values.}
+\end{figure}
+\end{frame}
+
+\section{Results: Comparisons to NuRadioMC}
+
+\begin{frame}{Results: Comparisons to NuRadioMC}
+\begin{table}
+\small
+\centering
+\begin{tabular}{| c | c | c |}
+\hline
+\textbf{Parameter} & \textbf{Value} & \textbf{Note} \\
+Ice Model & South Pole & 2015 measurements \\
+Signal Model & AHRZ2020 & (see \cite{PhysRevD.101.083005}) \\
+Trigger & 3 of 8 channels & $\pm 3v_{\rm rms}$ \\
+RF channels & 8 & RF bicone (in firn) \\
+Channel filters & [80-1000] MHz & Passband \\
+Noise Temperature & 233K & Sets $v_{\rm rms}$ \\
+Sampling Rate & 1 GHz & $f_{\rm c} = 500$ MHz \\
+Samples per channel & 256 & total time, $256$ ns \\
+Channel depths & [-4,-6,-8,...-18] m & cable delays included \\
+RF cable type & LMR-400 & $\approx -1$ dB at 20 m  \\
+\hline
+\end{tabular}
+\caption{\label{tab:1} Important NuRadioMC parameters.}
+\end{table}
+NuRadioMC was used to generate 15133 UHE-$\nu$ events that triggered the detector with $E_{\rm C} = 100$ PeV.
+\end{frame}
+
+\begin{frame}{Results: Comparisons to NuRadioMC}
+\small
+\alert{\textbf{Bottom line:}} 0.2 noise events pass correlation threshold in 5 years.
+\begin{figure}
+\centering
+\includegraphics[width=0.49\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{figures/Aug15_plot1.pdf}
+\includegraphics[width=0.49\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{figures/Aug15_plot2.pdf}
+\caption{\small \label{fig:fig3} (Left) The black circles represent the noise distribution.
+The gray dashed line is a fitting function to noise distribution.
+The solid gray line represents the correlation distribution for mathematical envelope to envelope of UHE-$\nu$ signals.
+The dashed black line is the correlation threshold.
+(Right) The correlation coefficient versus SNR.}
+\end{figure}
+\end{frame}
+
+\section{Results: ARA5 UHECR Results}
+
+\begin{frame}{Results: ARA5 UHECR Results}
+\small
+\alert{\textbf{Correlation coefficient}} for ARA5 UHECR candidate and model: \textbf{0.853}.
+\begin{figure}
+\centering
+\includegraphics[width=0.75\textwidth]{figures/November2nd_plot1.pdf}
+\caption{\small \label{fig:fig4} Fit for analytic $s*r$ to an ARA5 UHECR candidate 1915-26288.}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Results: ARA5 UHECR Results}
+\small
+\begin{figure}
+\centering
+\includegraphics[width=0.75\textwidth]{figures/November10th_plot1.pdf}
+\caption{\small \label{fig:fig5} Fit for analytic $s*r$ to an ARA5 UHECR candidate 1957-13330.}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Results: ARA5 UHECR Results}
+\small
+\begin{figure}
+\centering
+\includegraphics[width=0.75\textwidth]{figures/November10th_plot2.pdf}
+\caption{\small \label{fig:fig6} Fit for analytic $s*r$ to an ARA5 UHECR candidate 2171-31805.}
+\end{figure}
+\end{frame}
+
+\section{Conclusion}
+
+\begin{frame}{UHECR and UHE-$\nu$ Reconstruction with Analytic Signals}
+\footnotesize
+\begin{enumerate}
+\footnotesize
+\item \alert{\textbf{Introduction}}: 
+\footnotesize
+\begin{itemize}
+\footnotesize
+\item \textbf{A fully analytic Askaryan E-field} model in the time-domain \cite{hh2022}
+\item Based on work begun with Prof. Amy Connolly \cite{jchac2017}
+\item Based on work begun by J. Ralston and R. Buniy \cite{rb}
+\end{itemize}
+\item \alert{\textbf{UHECR and UHE-$\nu$ identification}}:
+\begin{itemize}
+\footnotesize
+\item \textbf{A fully analytic Askaryan voltage} model, time-domain [this work]
+\item Equations for both voltage trace, and envelope of voltage trace
+\item Verification with NuRadioMC: strong thermal background rejection, signal identification, and (rough) $\log_{\rm 10}(E_{\rm \nu})$ estimate
+\end{itemize}
+\item \alert{\textbf{Correlation with Recent ARA observations of UHECR}}
+\begin{itemize}
+\item Three events reconstructed, with ten more to come
+\item Improvements: noise filter, channel selection
+\item \textbf{Proposal:} short manuscript with equations and fits
+\item Mathematical physics and NuRadioMC comparison has been submitted to \textbf{PRD}
+\end{itemize}
+\end{enumerate}
 \end{frame}

### 2025-11-11 ARAFit/fit_data.py

@@ -75,25 +75,20 @@ i=0
 n = 512
 data = np.zeros((7,n))
 times = np.arange(0,n)/fs
-good_channels = [0,1,2,3,4,6,7]
+#good_channels = [0,1,2,3,4,6,7] for event starting with 1915
 
 with open(args.filename, newline='') as csvfile:
 	reader = csv.reader(csvfile, delimiter=',')
 	for row in reader:
-		if(i in good_channels):
-			data[i] = list(map(float,row))
-		if(i==6):
-			break
-		else:
-			i+=1
+		data[i] = list(map(float,row))
+		i+=1
 
-csw = get_csw(data,6)
+csw = -1.0*get_csw(data,6)
 model = np.zeros(n)
-env_model = np.zeros(n)
 rho_max = 0
-f0s = [0.170,0.175,0.180,0.185,0.190]
-gammas = [0.011,0.012,0.013,0.014,0.015]
-sigmas = [0.425,0.45,0.475,0.5,0.525,0.55]
+f0s = [0.150,0.155,0.160,0.165,0.170,0.175,0.180,0.185,0.190,0.195,0.200,0.205,0.210]
+gammas = [0.010,0.011,0.012,0.013,0.0135,0.014,0.0145,0.015,0.016,0.017,0.018,0.019,0.020,0.021,0.022]
+sigmas = [0.325,0.35,0.4,0.425,0.45,0.475,0.5,0.525,0.550]
 best_sigma = 0
 best_gamma = 0
 best_f0 = 0
@@ -109,15 +104,11 @@ for f0 in f0s:
 				best_gamma=gamma
 				best_sigma=sigma
 				rho_max = rho
-print("Best fit values")
-print(best_sigma,best_f0,best_gamma,rho_max)
+'''print("Best fit values")
+print(best_sigma,best_f0,best_gamma,rho_max)'''
 print("Data:")
 for i in range(n):
-	model[i] = math_conv(times[i]-154,1,1,best_sigma,best_f0,best_gamma)
-	env_model[i] = math_env(times[i]-154,1,1,best_sigma,best_f0,best_gamma)
+	model[i] = math_conv(times[i]-156.5,1,1,best_sigma,best_f0,best_gamma)
 model = model/np.sqrt(np.inner(model,model))
-env_model = env_model/np.sqrt(np.inner(env_model,env_model))
-csw_env = np.abs(hilbert(np.real(csw)))
[…]
